\documentclass[11pt,a5paper]{article}

\usepackage[
  paperwidth=5in,
  paperheight=8.375in,
  top=0.6in,
  bottom=0.65in,
  left=0.5in,
  right=0.5in
]{geometry}

\usepackage[scaled=0.9]{overlock} % Provides sans-serif typeface.
\usepackage[lining]{ebgaramond}
\usepackage{epigraph}
\usepackage{lettrine}
\newcommand{\alet}[1]{\textit{#1}\vspace{1em}}

\sloppy

\renewcommand\thepart{\arabic{part}}

\usepackage{titlesec}

\titleformat{\section}
  {\Large\normalfont} % format
  {Chapter~\thesection:}       % label
  {1em}               % spacing
  {}                  % before-code

\begin{document}

\part{The Deep White Forest}

\newpage

\section{Fury Follows the Hare}

\alet{A Meadow, Early Morning}

\noindent {\sc Fury} loved a Hare, and before you judge her, consider whom you love and what it might take to dissuade you. She was a mounted archer, he was a wandering musician. He couldn't be bothered, and she couldn't help herself. As he wandered round the Forest and through the meadows, strumming his guitar, thinking up songs, she tagged along, frustrated, often hung over, swatting tall blossoms into soft, inconsequential explosions of petals. He didn't seem to pay her much attention, and I think it's safe to say she didn't see him the way we do.

She talked and talked, and he only listened and strummed his guitar. Songs never issued forth from his mouth but that they were entirely written; she never heard him crafting, arranging the fragments, mumbling placeholder syllables, or however one writes a song. When she talked to him, maybe she hoped that some of what she said made it into his songs, but in truth she feared it. In his presence she spoke nothing but inanities and felt befuddlement in her tenderhearted awe at shape of his ears, the music in his heart, the genius of his songs, and how unaccountably soft were the white soles of his black feet on the rough Forest floor.

She was never comfortable on the meadows, and certainly not with him. She felt exposed, and found herself looking skyward fearful of she didn't know what. She would urge the Hare back into the Forest, suggesting the blossom-pocked glade abraded the eye and offered his songs nothing but clichés. She'd urge they rejoin his animal friends, the Otter, the Hedgehog, the Badger, the Fox, and her archer friends, Hemlock, Hobby, and Christoffel. At her barracks, a maple chalet in the woods, together, they would make music.

It's important to note how uncharacteristic of Fury was her foolishness over the Hare. Her friends would describe her as the most intelligent of them, and the kindest. While not the Squad's leader--that  was Hobby--Fury was certainly the most capable in combat, in diplomacy, in all their duties. They all looked, each in their own ways, for her approval. And her praise literally brightened them: it was her magic.

But in romantic love, and for the first time, she was anything but fearless, so unaccustomed to the feeling was the poor archer. No younger than thirty, she didn't know her own age, anymore than she knew the age of the Forest itself, but her love for her comrades had been the chief love of her life, however endless or brief. She loved her Mother in the complicated way of many daughters. Her love for her Father, God and King and Lord of all the Forest, was axiomatic. And she and her friends all loved Spring, who flirted with them unmercifully when they met him at functions, as they tended to, and who was as beautiful as a man could be.

But the Hare thing was different, for it stirred a dread, like an anchor dragging in silt, and the murky spirals that eddied up from the lengthening trench of her infatuation had begun to coalesce into shapes and faces: terrible shapes, horrible faces. Love was meant to ennoble, to encourage, not to encloud one in fear. Fury didn't know why love and fear, which she knew to be opposites, were now conjoined in her. She only knew she loved the Hare. Tears came to her eyes when she spoke this truth silently to herself. There was no one else to tell, least of all him.

The meadow was exposure.

``Please let's go back into the Forest,'' she would say to him. When at last he headed that way, she would follow, knowing that he in turn followed only his own fancy.

\newpage

\section{Thomas \& Asa Arrive}

\alet{A Meadow, Afternoon}

\noindent {\sc Not long} after Fury and the Hare left the meadow, two naval officers from the Kingdom of Newfoundland \& Labrador came to a halt in the centre of another.

``I think this is the right meadow,'' grunted Asa, the slightly older, rather shorter, much blonder of the two men, as he set down the rucksack he'd hauled for his friend and subordinate, Thomas, who stood sweating in the sun bearing yet two more. ``So I'll leave you to it,'' Asa said, turned, and walked back the way they had come.

``Wait! Asa.'' Thomas laughed imploringly.

The blonde man turned around. ``Conduct you here,'' he said, the flatness of his voice and curt horizontal motion of his hand indicating verbatim. ``Those were my orders.''

Thomas smiled at his friend and boss, who was pale and Scandinavian, and who was sweating more than Thomas. Thomas had the dark Inuk hair and eyes of his mother, the stature of his Flemish father, a deep sensitivity, and a disarming cheer when necessary. Both men wore their pressed khaki uniforms and black shoes, unsuited for hiking in a forest, but required by uniform regulations for late Summer visits to ``Other.''

Asa stalked back to him. ``Look, Thomas,'' he said, ``I don't know what you're doing here.''

``Me neither,'' said Thomas, shrugging affably.

``I have tried to reach them for weeks.''

``I know.''

``The boss has tried to reach them for weeks.''

``It's okay, Asa.'' Thomas reached out and put his hand on his friend's shoulder.

``Why we, why he---'' Asa sputtered.

``This is a nice meadow.''

Asa shook his head. Thomas knew it had been a frustrating few weeks for his friend, with nothing heard from the other side. In the end, Asa's boss's boss, the Commander's own Stargazer, as he was nicknamed, had made the call: send the uniquely game and qualified Lieutenant Thomas Shattering, Newfoundland \& Labrador Navy, to the Deep White Forest. You know, if they could find it. Equip him with such intelligence as they had gathered from...

``...two years of scant, incomplete, confusing, occasionally contradictory communications,'' Asa was saying, incredulous, ``but mostly, you know: just let's see what happens. I don't know what we hope to gain from this.''

Still smiling, and still burdened with one rucksack on his back and another in his arms, Thomas shrugged again. ``Me neither. Some drawings of Fairy archers, I suppose.''

Asa smiled. ``Though it possess neither mast nor helm,'' he said, ``he is determined this fellowship shall sail.''

Thomas knew his friend, like everyone else, assessed his character as game, loyal, a little naive. He sometimes wished he had a secret part that wasn't covered by that description.

``I guess.''

``It could all be lies.''

``Maybe.''

As Asa stared at him, Thomas marked the concern on his friend's face. For two years they'd manned adjacent desks in International Plans \& Policy, and together they had navigated challenging negotiations in more than a few cultures and languages, opposite some challenging personalities. And they'd had some successes, closing the deal on a number of important letters of request. But this Forest stuff was another thing entirely, connected as it was to the ascendancy of both Newfoundland \& Labrador and her greatest rival, the Republic of Iceland. Few understood what the Deep White Forest was, where it was, who lived there, how they operated, what they wanted. But everyone knew that for a hundred years, the interests of the Forest had been aligned with those of St John's, and in that time, Newfoundland \& Labrador had become the greatest maritime power, the largest supplier of arms, and so the wealthiest nation, on Earth.

Now someone in that Forest and someone in some secret part of the N\&L military and, one presumed, the Royal Family, had decided to appoint the first ever military liaison, for certainly none had ever come from the Forest to St John's. One presumed Iceland had been making inroads, gaining influence. They were crafty, those Icelanders.

It had taken two ships, three airplanes, another ship, and a three day hike to deliver Thomas and Asa to this meadow. There had been secrecy all the way, even blindfolds at one point, codewords, and men and women whose unit insignia and warfare specialties Thomas hadn't recognised.

And it \emph{was} a nice meadow. There were tall colourful blossoms, some of which Thomas had never seen. Honey bees. The grass was deep green, soft and welcoming; the sky deep blue, clear and comforting. It was Spring here, it seemed, wherever here was. Asa had a compass, but it had stopped being usable the first day of their hike, fixing only when held vertical, the needle hanging straight down in defeat.

Asa handed him an envelope sealed with the King's own stamp. ``She's called \emph{Fawn} or \emph{Fille} or something like that. Your contact.''

Thomas looked from the envelope to Asa's bemused face and said: ``I hate this spy shit.''

``Me too,'' said Asa, walking away. ``Send reports.''

Thomas laughed. ``How?''

``As many as you can.''

``No, \emph{how?}''

Asa shrugged.

Thomas called after him. ``I'll be fine!''

\vspace{1em}

\noindent {\sc Thomas} sat atop his stuffed rucksack and drew in his notebook, enjoying the sunshine. His black patent leather shoes shone in the long green meadow blades like eels snuggling in sea grass. There was, from time to time, a light breeze from the direction of the deepest woods. Though he faced into the Earth's turn, Thomas thought how alike were a soft meadow before a wood and a calm sea before a sunset, how one was drawn into the darkness by forest trees that seemed to beckon, as by a sinking ocean sun that asked to be followed. But inside the wood the trees were xenophobic, and over the advancing horizon was only night, solitude, and terrible islands jutting up from Hell.

Thomas had gone to sea as a youth, less following his father and grandfather, more seeking the source of a loneliness he'd felt while surrounded by friends and family on land in St John's. Something else tugged at his heart from within the nascent consciousness of a little boy, in a snowy wilderness he'd glimpsed only once, on his single visit to his mother's homeland in the far north of Labrador. Something in a blizzard. A face. Three stars suspended in an arc.

Strange to think of oceans and blizzards on this sunny meadow.

``\emph{To think there was a life I had,}'' he sang absently, ``\emph{a life before she came.}'' A sailor on {\sc heart of autumn} had sung it and played the concertina. ``\emph{To think there was a time before I knew her name.}''

\newpage

\section{Fury Observes Thomas}

\alet{A Meadow, Late Afternoon}

\noindent {\sc The man} was singing.

Fury watched him from the woods and felt a kind of exhaustion. These were the kinds of orders no one wanted, babysitting an attaché, and this time it was to be for an entire year. That year would start today. Fury, who never put anything off, ran her fingers along the grooved bark of the log she sat upon, feeling the softness of the moss, sinking her nails into the fissures, risking splinters, drumming her fingers, pressing her palm down like pitch to receive the bark's repoussé.

The man looked tall and slim, though Fury would be taller and slimmer. He did not, she thought, look like an outdoorsman. He looked like a rich boy. Fury had known many, had helped to seat some on their thrones, had helped to unseat others. This one looked unaware of the half-dozen immediate threats to his life---one bear, two kinds of insect that carried parasites, two bucks in rut, Fury herself---in the meadow and surrounding woods.

But he didn't necessarily look vulnerable.

Not \emph{in}vulnerable.

Charmed, maybe.

She'd bid the Hare farewell by the brambly entrance of the Fox's redoubt, odd companions that those two were. Both played guitars; guess that made them friends. ``See you later,'' was always her farewell to him, and she hoped it did not sound to those enormous and perceptive ears like a prayer. She'd gone back to work. She'd inspected the room at the Chanticleer Hotel in Three Nations, the Icelandic village nearest the Lodge. The little maid who'd let her in had kept her eyes down on the jangling keyring she gripped with not-quite trembling fists. ``Thank you,'' Fury had said in Icelandic. She'd nodded at the hotel manager as she passed through the lobby, empty of guests. He'd nodded back, warily, a bit unhappily.

``Don't worry,'' Fury had thought, swiping a sugar cube from a bar table, ``you won't see me again until he checks out.''

Looking at Thomas now, she had the feeling he'd set the hotel staff at ease, become quite popular with them, charm the little maids. That he'd been chosen for such reasons.

She'd gone back to the Lodge. No one had been around. Hobby and Hemlock were on short patrols. Christoffel was probably upriver hunting eels. In the darkness of the large common room, the late afternoon sun had rendered in blinding amber the polished maple face of the Hedgehog's double bass, resting in the corner next to the Badger's drum kit. It had stamped a dark hourglass shape onto Fury's vision for several minutes, requiring that she obliquely reread her obliquely written orders, behind His own seal.

One man, one year, one objective.

In the tack room she'd hung up her bow and quiver beside her saddle; the other three bays had been empty. In his stall she'd given Ontario the sugar cube and grabbed his mane and shook his head roughly to acknowledge that he was lonesome, and she promised him that someone would take him down to the river  later when it was cooler.

She'd trotted herself south to the little bridge over the waterfall, a two hour run. No horse. No weapons. That wasn't in her orders, but these things had a feel to them. Thomas here looked about as unthreatening a thing as Fury had ever seen, save that he represented a year of her life she anticipated being uncomfortable, annoyed, and courteous at the expense of her own energy.

``What else are you going to do, Fury.'' she asked herself aloud. Silently she answered with a sarcastic: ``Marry the Hare?'' At this she snorted, a sudden, out-of-place, surprisingly loud noise from the wood to which Thomas was oblivious.

She stood.

Fury was very tall.

\newpage

\section{Thomas Sees Fury}

\alet{A Meadow, Late Afternoon}

\noindent {\sc The sun} was getting low, and Thomas had to admit to himself that despite having been a naval officer for nearly a decade, he now had no confident sense of which direction he and Asa had come and Asa had set off. That this was the sort of meadow in which one might happily spend the rest of one's life was the kind of thought he'd spent the decade suppressing in order to live up to the meagrest of his family's expectations. Nevertheless, if his anxiety was at all eased in this strange place, it was by such a thought. Nor was it the first time Thomas had acknowledged the curious fusion of unease and comfort by which he processed the alien and uncanny. Or perhaps the uncanny created the feeling. Isn't it what the word meant?

Looking round the perimeter, he saw there was a small region, an acute arc of the surrounding wood darker than the rest, more forbidding. His father's kind voice told him, as always, that was the direction he ought to go, on a trajectory parallel to the one that had led the older Shattering to Tom's mother in the far north of Labrador, that had led that man's father to an ancient oceanic civilisation and a bride, Tom's grandmother, who some had whispered was not Dutch at all, but was in fact a mermaid. Sailors and their gossip.

Tom's orders told him to stay put and wait for his contact.

It was from that dark region she emerged, lean and very tall, in her striking headdress. A thing anticipated and now arrived, with less waiting than one might have expected for such a life-changing moment, she strode out into the sunshine with an athletic grace obvious to Thomas, to whom such things weren't always obvious.

He stood, and as she approached the details of her uniform struck him, the enormous red fur headdress with its tall tufted ears and the matching tall boots. Her spurs. They were obscured by the meadow grass, but Thomas heard them now. The black bodice and copper-embroidered braces and chased brooches over the crisp white cotton shirt, sleeves rolled up above the elbows. Suspended between the brooches were three polished copper five-pointed stars on a chain. The tan pleated skirt cut just above the knee, its yoke yet more red fur, its hem embroidered in black crenellations matching the copper pattern on her braces and bodice. In the sun, on the green, before the forest, all that glinting copper and red fur and polished black hide leather was something to behold. She had long bright white tufts of hair growing from her ears. And was she--? She was. She was wearing glasses, copper rimmed, oblate octagons. Her skin was pale; not as pale as Asa's. Her broad face was framed by the red fur headdress and its black leather chinstrap. Her hair was bobbed, with brown bangs that hung in her bright blue eyes. She looked a little pissed off.

Thomas, agape, a Catholic, and having nothing else to say, whispered: ``Jesus Christ.''

\newpage

\section{Fury Greets Thomas}

\alet{A Meadow, Late Afternoon}

\noindent {\sc The man}, whose face was a boy's really, uttered something as she approached him. Something inconsequential. Some foreign epithet she pretended not to hear. He looked stupefied. He looked kind of stupid. She resisted rolling her eyes, inhaled, and said:

``I'm called Fury.''

``Why?'' said the idiot before he could stop himself.

She ignored it.

He tried to recover. ``I'm sorry, I'm Thomas,'' he said, reaching out a hand.

She stared at it. He pulled it back.

``I'm sorry,'' he repeated.

A year of this.

He tried again: ``Do I---? I don't know your rank. Do I salute you?''

She looked at his bewildered face. She was taller than he, a couple inches.

``I serve Lord Ekkor,'' she announced, and in the mantra genuinely felt her annoyance recede. She meant those four words, the first she'd ever spoken, and this hapless tourist was her charge now. She looked at him.

``No, Thomas,'' she said, ``you don't salute us. We don't salute.''

She walked past him and picked up a rucksack.

He pivoted to watch her. ``You're, um---shit!---'' He stumbled on the pack he'd been sitting on. ``Ha ha. You're my, my contact.''

She shouldered the rucksack. ``Yes.''

``You're an archer.''

``Yes.'' He'd come at least a little prepared.

``And a horsema---a horsewoman. A horseperson.''

She pitied him now.

``Horseman is fine,'' she said. ``A mounted archer, yes.'' She smiled, her impatience fled, and she resolved herself to bringing the poor guy up to speed.

``Okay then,'' he said, ``well I am Lieutenant Thomas Shattering, Newfoundland and Labrador Navy, and you speak English, so that's good.''

``I do,'' she said.

``Good. Good.'' God, he seemed confused. ``And I've been assigned to your squad as a liaison officer.''

``For one year,'' she said.

``Yes, one year.''

``You pack light,'' she said glancing at the three rucksacks.

``Well...''

``No, that's good,'' she reassured him. ``That's good here.''

``I don't need much,'' he claimed.

She doubted that.

``Sure,'' she said. What residue of ambivalence still clung to her good manners, the visitor now detected it.

``I've been a liaison before,'' he said a little indignantly.

``Oh? Where.''

``Arabia.''

``I see,'' she said, nodding.

``It's not just palaces, there.''

``Sure.''

She walked off toward the wood; he hurriedly hefted the other two rucksacks and followed. They crossed the buzzing meadow as the sun began to set. Their shadows stretched across the grass. Birds piped a noisy chorus from the wood.

``It's mostly palaces,'' he said.

\newpage

\section{Thomas Follows Fury to the Forest}

\alet{A Woods, Early Evening}

\noindent {\sc Thomas} had never been so disarmed. In diplomacy, deference was a grammar, and it might camouflage weakness, but he could not have felt more naked before Fury had he been literally naked. Tripping over his words and his own feet. His addled mind reassessed everything now as he followed her into the Forest: the year ahead, his career, his future.

His ideas of beauty.

Tall and boyish, wide jawed, with white-whiskered ears, these were not feminine ideals in St John's at the time. But he found Fury a beautiful creature. She was a creature, wasn't she? Apart from the overwhelming sense of longness her frame gave, there was nothing manifestly inhuman about her.

The ear hair was weird.

His preparation for this mission had somewhat introduced Thomas to the notion that the reality of the Deep White Forest offered more than he could imagine. In a dingy shop deep in the basement of Fleet Headquarters, the civilian Ted Bradfield, whose own past was a mystery, whose security clearance was rumoured to be higher than that of the Fleet Commander's, hadn't said much that was useful for Thomas. One meeting, half an hour. ``Otherworldly,'' had been the word Mr Bradfield had used to describe the archers. They were legion, millions upon millions of them, clad in red fur. ``I look forward to seeing your drawings,'' he'd told Thomas. But the philosophical old man had said this about entering the Forest: ``Only through the varied manifolds describing the extremes of our ecstasy, our mastery, our depravity, may we enter that woodland realm, and the immigrant projects the features of the frontier through the trespassed border. If you arrive through ecstasy, you can expect ecstasy to describe the colours of the sunset and the shapes of the mountains. If you arrive through mastery, the clouds and foothills will undulate with your satisfaction. If it be depravity, the Forest will be all corruption,'' he'd paused and looked at Thomas for a few pregnant seconds, ``and you slithering among it.''

During the voyage here, Thomas had made a drawing, a sort of Vitruvian Man surrounded by these intersecting, overlapping envelopes. How the boundaries of man's experience or nature might be labeled, how they might nest or overlap, he couldn't guess. If Mr Bradfield had parsed his own scholarship in these areas to such a diagram, he hadn't shared the details with Thomas. Maybe that's what the old guy had been doing down in his basement shop for a quarter century.

``He had a lot of books,'' Thomas said to Asa a week ago in a wardroom on a classified vessel crossing a classified body of water.

``I hope you've been disabused of any belief in expertise,'' Asa had said over his coffee as Thomas sketched Mr Bradfield's bearded face from memory. ``No one can prepare you for that place.''

``If it exists,'' Thomas had said.

``Right,'' his friend had agreed. ``If it exists.''

Fury was real.

And watching her walk in front of him as they approached the woods, Thomas began to feel a pull inside himself, something he couldn't define.

``Is this the Deep White Forest.'' he asked her.

``There is a bridge over a little waterfall we'll come to,'' she replied over her shoulder, her breathy voice stirring him. ``I don't think I'd call anything this side of that bridge home.''

``I figured it'd be white,'' he said, a bit out of breath. He wasn't yet struggling to keep up with her, but he thought he would be soon.

``It is in winter. It's always deep.''

``How big is it?''

She stopped and turned to him. She looked thoughtful and said with a cheerful sincerity: ``Imagine death, or some graver threat, or some sweeter promise were to drive you across and through. And now imagine fair skies favoured that you ride one hundred days without losing time to aught but to sleep on moss and feed on game, and your horse is very fast, and your eyes are clear.''

``Alright,'' said Thomas. He put on a skeptical tone, the appropriate response, he felt, to her suddenly poetic evocation, but over its course the pull he had been feeling had deepened and become more urgent. It was connected to him at a trunk whence diverged the branches of gut, heart, and mind, a now so obvious junction he'd neglected in his little Vitruvian diagram.

``Now you've arrived not at the opposite side, but at the centre of the Wood.''

His realisation of the scale of her Forest broke his reverie, and he looked past her into the wood. Two hundred days' gallop across, what was that, six thousand kilometres? Seven thousand? ``It's vast,'' he said.

``Aye.''

``We'll cross the footbridge tomorrow,'' she said, turning to resume the hike.

``How long is the walk.''

``A few hours. More in the dark. We'll camp this side of the waterfall.''

They entered the trees in the last direct rays of the sun. The birdsong peaked in intensity, swallows and starlings, robins and blackbirds, all darting about the foliage.

``It feels like Summer here,'' said Thomas.

``It's a warm Spring.'' confirmed Fury. She glanced back at him momentarily and asked: ``Is that your regular uniform.''

``The khakis,'' he laughed, ``yeah, they're not ideal. We put them on this morning---''

``We?''

``My friend, my boss, my friend Asa. Lieutenant Commander Roos. He accompanied me on the journey. Anyway, I have better clothes for hiking.''

``Good.''

``I put this on to meet you. Is that your uniform of the day.''

``We only have the one.''

The woods grew denser and darker as they walked, and fireflies emerged to give the darkness dimension. There was no path, but Fury picked out the route with ease, and she seemed mindful that Thomas was carrying bags and wearing shoes designed for sailing. He was transfixed by her gait as she became a silhouette wading through a sea of bluebells, all now closing up for the evening; her straight brown hair emerging from her headdress, brushing the crisp white collar of her shirt; her broad shoulders rocking back and forth as that white shirt became the last visible feature of her form in the darkness; the sleigh bell rhythm of her spurs guiding him as sight became useless.

\newpage

\section{Christoffel Writes to Arthur}

\alet{A Forest Lodge, Evening}

\noindent {\sc By the light} of oil lamps, with a copper hatchet, smiling Christoffel chopped the head off a shiny black eel, who also seemed to smile, even upon finding itself now only a head and now rolling off the wooden table and landing with a rubbery slap upon the stone floor of the barracks kitchen. Three other eel heads who had not made such a bid for freedom huddled in a group on the tabletop and looked on as Christoffel laid out and flayed open each of the four shimmering black bodies. She pulled out the intestines and threw them in the sink. She rubbed the bodies in salt and pepper and oil, and gathering them up by their narrow tails hefted the heavy lot triumphantly before her. Pushing open the bottom half of the stabled outside door with her own bottom, she stepped out into the warm evening, heading for the smoker which fumed away under the maples at the edge of the barracks yard.

The eels hung, she walked back to the barracks. From the darkened stables to her left she heard Cheops snort with a tone she recognised as horsey dreaming. She softened her footfalls so as not to stir him.

Hobby and Hemlock had not yet returned from their patrol out past the reservoir. Fury wouldn't be back until the following night, bringing with her the liaison officer from Newfoundland \& Labrador. Christoffel---the others called her ``Toffy''---was excited to meet this person, whomever he or she might be. There was no way to tell any details about the visitor by the typically terse and oblique message from His Central Force: ``{\sc n\&l} $\triangle$ {\sc lno} $\odot$.'' That is ``Newfoundland \& Labrador sending naval liaison officer to the Forest for one year.'' The archers knew they'd be hosting this officer, or they wouldn't have received the message. Hobby had chosen Fury for the duty of the visitor's sponsorship, which was the obvious choice. Fury was the smartest, kindest, and bravest of them. Toffy knew Fury wasn't enthusiastic about the duty, but she wasn't sure why.

Toffy was not the sort to wonder long about things she didn't understand. Harmony and duty were her chief interests, and she was a loving friend and a fierce fighter in accordance with this philosophy.

She pulled her Serafini pocket watch from her skirt pocket and saw that it was only nine. Hobby and Hemlock would be another hour. The creatures wouldn't come until midnight. Her chores were done. The fire and the lamps were lit, filling the common room and kitchen with a warm amber glow. The eels were smoking.

She decided she would write to Arthur in Firenze.

Everyone, the archers, the creatures if they could talk, would say Fury was the kindest and most clever. They'd say Hobby was the toughest and the quietest. Everyone would say Hemlock was the prettiest, and also the biggest clown. Toffy knew they all would say she herself was the most sentimental, the most given to nostalgia, and if that aspect of her character bore faults, one would have to count among them a tendency to reminisce about the sunshine she'd felt on her face, the poetry she'd heard, the music she'd played, and the friends she'd made during the year she'd spent on assignment in Italy.

``Who could have helped themselves?'' was Toffy's thought. Her Squad had fought all over the world---all over \emph{other} worlds---and could confirm firsthand the singular magic of that peninsula. Arthur, who was from Germany, agreed, and also understood Toffy herself in a way she'd never been understood, nor had known she'd wanted to be understood. Italy had not seemed to value Arthur's impressions of it, but Toffy, for whom self-understanding had never been a preoccupation until her Italian experience had unlocked the urge and Arthur had suggested their correspondence as a way forward, found his observations intriguing.

For Toffy---and for Fury and Hemlock and Hobby and all the other million millions of Ekkor's daughters---an understanding of the world was prescribed, and circumscribed, by \emph{Ekkorbok}. The bookshelves of the barracks were populated by thousands of hidebound volumes of the sacred text, the reading of which was a lifetime pursuit for the immortal. Hemlock could be seen to read Ekkorbok every day. Hobby could be imagined to have already finished reading all of it, impossible though that was in finite time. Fury, more than anyone their Father might have hoped to sire, was possessed of a spirit in whose essential makeup the instructions of \emph{Ekkorbok}, or any other book of virtues, might be said to be redundant. Even wanting, thought Toffy, a thought no less blasphemous than the act of hiding her draft letters to Arthur in a volume of \emph{Ekkorbok} that sat in a shelf next to the fireplace, and whose volume subtitle struck her as unlikely. She retrieved and unfolded the latest draft now and sat on a stool at the kitchen table with pen and ink. Arthur had mentioned in a previous reply that he enjoyed the stains and smells her letters carried to him from the barracks kitchen.

Her last paragraph had been:

``I hope it is useful to you, Artur, to have these more deliberate and thoughtful descriptions to connect desultory details I sputtered in Pisa. To review in brief: Hobby is the silent boss, Hemlock is the pretty clown, and Fury is the kindest, warmest, gentlest soul ever to smile at a fellow being.''

Toffy thought about trying to assign helpful German epithets to each of her friends for Arthur, but found she had exhausted her German with ``Liebe Artur'' at the beginning of the letter.

``Tomorrow we are expecting an envoy from Newfoundland \& Labrador,'' the letter continued. ``Fury has gone to greet this person. Hobby expects it will be a soldier, probably an officer, and that he or she will stay for one year. I suppose he or she will accompany us on patrols, which is all we do these days. We have not been in combat for some time, Artur, nor have we travelled---in fact, I think Fury's little excursion to retrieve our N\&F liaison is the first time any of us has been outside the Forest in a few years. I have done some long patrols, many hundreds of kilometres, and as I have told you again and again, perhaps self-consciously, the Forest provides a variety of landscapes and features: it's not just big trees, Artur! There are mountains and glaciers, lakes and farms. Nevertheless, I hunger for alien corn (I know you will get the reference), despite having only just now butchered eels from the river and reminded myself how delicious they are.''

She heard Hemlock's and Hobby's spurs before they reached the river, then blonde Cheops', blue Mercury's, and unburdened brown Ontario's hooves upon the red maple bridge. Unhurriedly, she blew gently on the drying ink, refolded the letter, slipped it between its familiar pages of the holy volume, and replaced the book in its home by the fireplace. When green-eyed Hemlock, covered in patches and flecks of drying mud, burst cheerfully into the barracks, she found Christoffel stoking the fire.

\newpage

\section{Hemlock \& Hobby Return from Patrol}

\alet{A Forest Lodge, Late Evening}

\noindent {\sc Toffy} looked guilty. Hemlock perceived it without understanding it and dismissed it in her love for her brown-haired sister, whose cheer and musicality were a gift from God, and who was hideously vicious in---and especially after---battle. Nevertheless, as she strode into the barracks, Hemlock grinned at her, only a moment overlong, before announcing: ``We saw them in silhouette coming over the hill.'' Toffy's expression of guilt phased through a brief pleading defensiveness before emerging into reassured delight. She clearly knew Hemlock kept her faith and that she was talking about the musician creatures.

``Every night is sort of too good to be true,'' said Toffy. Hemlock held out her stiff, achy, muddy arms to embrace her friend, who parried her advance with the fire poker. Hemlock giggled mischievously. Toffy hung the poker on its hook on the hearth, freed her hair from its ponytail, and asked: ``Anything exciting out there.''

``Not a thing,'' said Hemlock. ``Nice ride though. Dark and silent and fast from the Waterfall, through Three Nations--I think Hobby thought Fury might be back.''

``I think it'll be in the morning,'' said Toffy.

Hemlock's stomach tightened at the thought of Fury camping in the woods with the stranger from Newfoundland \& Labrador. When she wasn't nearby, thoughts of her closest friend had been having that effect on Hemlock for some time now. When had this seam opened up? Hemlock, so talented at discovering hidden seams and fissures and frontiers, couldn't quite identify the start of the tear in a fabric she'd understood to be as finely knit as Fury's own exquisite arrow-motif quilt, the one her friend surely slept on tonight, somewhere west, opposite the campfire from their imminent houseguest. She realised she was channeling Hobby's subtle distaste for the idea of the visitor, and she shook it away. Not her style. Actually, Hemlock remembered, Fury would be sleeping in the grass. She'd set out on foot three days ago, asking Hemlock to exercise Ontario, and taking nothing with her. No horse, no suitcase, no weapons, no quilt.

``What.'' Toffy inquired about Hemlock's evolving expression.

``No, I agree. Tomorrow.'' She paused. ``Tonight,'' she grinned another muddy grin at Toffy, ``we make music.''

Toffy grinned back. ``You saw the fox.''

``Oh yes. All of them.'' They all liked the fox. Toffy felt a special kinship since they both played stringed instruments: she balalaika, he guitar. Hemlock thought him capable of some real understanding. But the little hedgehog, who played the enormous double bass, and who never sang, was, she thought, the most deeply intelligent. Hemlock looked into the fire thinking about their creature friends and knew Toffy was doing the same.

Hobby, tall and also muddy, strode in the open door holding her saddle before her, already saying ``Toffy...''.

``She broke a strap,'' said Hemlock.

``I'll fix it now,'' said Toffy. ``Put it in the kitchen.''

``I wiped it down,'' said Hobby, carrying the saddle into the kitchen. ``There's eel guts here,'' she called back.

``Ooh, nice,'' said Hemlock, still looking into the fire.

``Put it by the door. I'll take care of it,'' Toffy called back to Hobby, then said to Hemlock: ``Is she worried.''

``About Fury.'' asked Hemlock, now turning her head to look at Toffy. She thought, then looked back at the fire. ``Maybe.''

They all were. If she had to describe the change in Fury in a single word, Hemlock would have used ``absen.''--about a woman who could never have been described as inattentive. Her duties--such as they were these days--hadn't been impacted. But everyone felt the absence, because the presence had been so fructifying. No one who knew Fury had ever, as far as Hemlock could imagine, taken her for granted, because Fury herself never took anyone for granted. Hemlock would not go so far as to say that was what was happening now, but the faraway look, the long walks alone. And the dreams. Hemlock, whose rack was next to Fury's upstairs, had heard her cry out more than once.

Standing here staring at the fire with Toffy, both of them having the same unspoken thoughts, was the sort of thing that pissed Hemlock off, that made her act out. She thought about trying to hug Toffy again, but she'd used up that joke.

``It's getting too warm,'' she said instead. ``We should play outside.'' That she'd retreated into banality pissed her off even more, and now she felt a debt to Christoffel. To actually embrace her, to cheer her up, to give of herself to the splendid archer beside her.

``We should play outside,'' said Hobby emerging from the kitchen. Toffy and Hemlock looked at each other. Hemlock raised her eyebrows.

``Back in a flash, I'll help you set up,'' she said, still in the other's debt. She followed Hobby out the door, past the stables and the smoker, now emitting an eely hickory, through the crescent of wood bound by the road and the river, down to the riverbank, and into the cool, dark water where the horses were already swimming.

CHAPTER: Hobby \& Hemlock Bathe in the River

A River, Evening



Hobby's long blonde braided ponytail drifted round to encircle her pale upturned face on the calm obsidian surface of the river. Through her overlong bangs, the ink of night spilled into her bright blue eyes bearing silver flecks of a million stars, each one settling inverted on the polished bowls of her retinae, sliding in spherical unison as she shifted her gaze. She felt the cool water working its way down into her boots, up under her headdress, anywhere it hadn't already gotten to. She felt the minnows, numerous as the stars, cleaning every inch of her.

When she and Hemlock emerged they were spotlessly clean. They sat drying together on the grassy bank watching Mercury, Puer, and Ontario wade in the shallows and drink. Mercury's roan coat caught the moon, an artificial blue there among tan and blonde Puer and deep brown Ontario.

The night, a beautiful one, what might be the last warm night of Summer, had settled on their country with a purpose. From sundown up on the plateau mad with birds, through twilight across the farms filled with Settlers busily reaping, and down, as evening fell, along the winding wooded road crisscrossed by unhurried harts and gravid hinds, the ride back to the barracks lodge had been a glimpse at Autumn's battle plans.

When they'd ridden through Three Nations, Hobby had looked up at the ever dark windows of the Chanticleer and wondered that one might be lit for an entire year. ``Keep him alive for one year,'' she reminded herself. This was the extent of her remit. Whatever His Central Force had in mind, whatever they hoped to gain from this arrangement, she didn't know nor care. Apart from their standing orders, they hadn't in years been given a mission with any hope of completion, and she had felt relief that the four archers and their horses here at the bottom edge of His Forest hadn't been forgotten. But this was not the sort of assignment she'd expected. She had thought more likely some disciplinary measures for carrying on with the Forest Animals, a circumstance for which Hobby took full responsibility, though it had been Fury who had brought the Animals into their lives. She looked up at the ferocious band of centaurs mounting the northern dome of the sky. The Animals. The envoy. Hobby couldn't help imagining this strange conjunction was the source of Autumn's anticipation.

``Toffy went to market,'' said Hemlock in a quiet voice. Hobby didn't have to turn around to know she was also revering the stars.

``And to the river,'' confirmed Hobby.

Hemlock hummed. They all liked eel.

They both wore smiles now, Hobby certain that Hemlock was also thinking about Christoffel splashing round the river catching eels by hand and the brown-haired archer's oblivious but effective haggling with nervous and unfriendly Icelandic settlers in the market, also unable to decide which image was funnier.

Above the two drying fairies and three wading horses, the climbing centaurs dug galactic hooves into the velvet of evening, wrinkling the smooth dome of the sky into umbral folds, long, dim compressions subtending uncountable stars. Hobby's knowledge of the stars was prodigious, like her knowledge of scripture.

CHAPTER: Fury \& Thomas Camp Outside the Forest

A Clearing in the Woods, Late Evening



There would be music tonight at the Lodge without her, thought Fury. He--the hare--won't wonder where she is. He will have new songs. The otter will already know the tunes and will have fashioned lovely and intricate harmonies. The fox will have invented some ingenious decorations on his guitar. The little hedgehog on his big double bass and the hard-drinking badger on his drum kit will be working it out as they go. Without Fury there, Hemlock will be the first to come in on her pipes, then Christoffel on her balalaika, then, maybe Hobby on her horn. Dear, dear Hobby, who was accountable for everything that went on at the Lodge, who had thrice written to His Central Force asking permission for the creatures to come in to play music in the evenings, and who, after having heard nothing back for a year, had made the call on her own authority.

Thomas had gone to pee. Fury stoked the campfire, which threw an oversized shadow of her tufted-eared headdress up against the trees surrounding their little clearing. Skewers of mushrooms were suspended on a makeshift trellis just above the licking flames, and Fury occasionally dribbled eel oil on and rotated them. A small flask of the oil, five copper arrowheads, and a sealed letter from the King promising a mighty reward to anyone who helped His devoted archer escape from enemy territory - these were the perennial contents of the small pocket of Fury's skirt.

Thomas peed rather loudly, traipsed back to the campfire loudly, and greeted her sheepishly, and loudly, but Fury had given up being frustrated by his inexperience with life on the trail. So she smiled, returned his greeting, and indicated the meal now near ready to eat.

``Mushrooms,'' he said, pleased, then made a face. ``What's that you're putting on them.''

They ate, not in the most nor the least awkward of silences. His preparations for sleep were more involved than hers, which in this weather involved only lying down. She poked absently at the campfire, confident she'd be asleep before him, equally confident she'd remain more alert while asleep than he was while awake. She had become aware that he was finding it difficult to meet her gaze, looking rather into his little notebook, but she didn't think much about it. She detected nothing in him that piqued her interest, and she had never once underestimated a man.

Her thoughts, as the embers died and the stars re-emerged, were with the hare and with her friends. When had that become the order, first he then they? The singing, the drinking and smoking, the carrying on and laughing--the Creatures didn't seem to laugh, but Hemlock laughed constantly, and Toffy could easily be made to pee herself, and Hobby, once drunk or high, would eventually squint so hard and grin so wide her face threatened to separate into thirds--would go on until dawn. Other creatures occasionally showed up: a marten that played a cello, a skunk with a copper horn like Hobby's, the stag, whom they adored, who played stringed instruments in the most peculiar way with his hooves. What tableaux they presented in the early morning hours of their hootenannies, archers and creatures dancing and singing and drinking by a roaring fire, to alien artists like this Thomas here, outside in the snow, painting them from different angles through different window frames, confounded by what they might be carrying on about, what language they might share, what brush-stroked glances, touches, or whispers might elucidate the discrete binary acquaintances. Soon Thomas, as ignorant of the Forest as any Newfy was bound to be, would be privy to their day-to-day, with more access than any Icelandic settler from Three Nations or another village near their barracks. It occurred to Fury that among all their reviews of protocols and operational security regarding Thomas--they hadn't known his name then--they'd never discussed whether he'd be invited to the singalongs.

``They call it the Great In-Between,'' said Thomas, actually startling her.

CHAPTER: Thomas Falls in Love with Fury by the Campfire

A Clearing in the Woods, Late Evening



Other than noting how delicious the eel oil had indeed made the mushrooms, a distant and inspired loon, and a starry sky that appeared endlessly to populate as night deepened, Thomas' attention that evening was framed by Fury's brown bangs, the pair of long locks that hung down her cheeks, and her black leather chinstrap. Her face, that fair lantern bearing the deep blue gems of her eyes in their twin octagonal copper settings, which had so ignited his fancy by the late afternoon sun of the meadow, visited by campfire light an apocalypse upon his heart. He watched the flickering play across her features as much as propriety allowed, as much as he dared, ashamed and fearful of what a battle it already was to look away. She ate like an animal, in a kneel, licking her hands sometimes. When at last she stretched out on the grass beside the fire, her length and slenderness took his breath away, and her knees shone prominently between her skirt and boots. Laid out in that glow, her polished bodice was ablaze, the stars and chased brooches a blinding display. Her spurs--cruelly sharp--glinted. Her pelt headdress and boots roared more red. Fireflies had begun to gather round her. She was, before that cool dark green Forest of incalculable scale, a city of warm amber light. Camouflage was not fundamental to these beings' tactics, thought Thomas.

She looked at him from time time, but seemed lost in thoughts of other things, and it maddened him how long, how many weeks, he would have to wait to ask to sketch her not to be plain rude. Now would have been perfect. They hadn't spoken since he'd sat to eat, with the Forest providing as much to listen to as anyone could want. Some sounds were ominous, but he looked to her, confident that he now travelled with one of this country's most formidable warriors. Arabia had given him experience in trusting the host in a dangerous place, and Thomas was not a spy and not suspicious. His bosses counted on that. Anyway, in the Forest's music, all was orchestra to Fury's loveliness.

They'd not yet crossed, according to her, properly into her homeland. Thomas took out his notebook and read a list of terms he'd copied down from Mr Bradfield's own notes. Names of the Forest. ``The Great In-Betwee.'' had been uttered by a castaway picked up by a frigate in the 30s, and ``The Gi.'' with a hard ``.'' had stuck among some parts of the Navy, though Thomas had never used that term. His Father and Mother had called the Deep White Forest the Deep White Forest, and they'd called fireflies fireflies, and anything else sounded wrong. But the speculation, the jokes, the navigational theories on just what that sailor had meant, exactly what two things the Great In-Between was in-between--Thomas had at hand now someone who might address questions, and better before entering any sanctum where blunder might become blasphemy. So he blurted, without even clearing his throat: ``They call it the Great In-Between,'' and he marked her start.

He saw those blue eyes looking at him sideways.

``Who are they.'' she asked. ``What do they call that.'' Fury's voice was a soft and breathy one, and it seemed to carry some low frequencies along with its gentle alto, frequencies that Thomas could feel in his skeleton sitting this near to her in the stillness of the woods.

``They are sailors in my Navy,'' he said. ``It's what they call the Deep White Forest.''

She considered, her eyes momentarily tracking a firefly who seemed to think the better of landing on her nose. Finally she said: ``Don't say that in the Forest.''

``Aye,'' said Thomas, nodding, ``I thought I'd get a few questions out. An assignment like this, I mean, traditionally there are months or even years of meetings before...'' He trailed off, because from across the campfire that fantastic woodland elf warrior woman stared at him, and he was revealing himself to have somehow in the past ten years evolved from adventuresome mariner to irritating bureaucrat. He closed his notebook with a gentle snap, chuckled to himself, shrugged, and made a show of preparing to sleep while she stared at him a bit longer before returning to gazing into the campfire, which was mostly what she'd been doing this evening.

Settling into his bedroll, Thomas had nowhere to look but up. Some thin white clouds and fireflies notwithstanding, here was a blackness that rivalled the ocean sky, and from which the brightest stars leaned forward in their lantern oranges and greens, while the dimmer ones behind them, so dense and scarce to be distinguished from one another, smeared the firmament in pale tendrils. Once he found Arcturus, the map of the Heavens spread out readily across Thomas' seafaring mind, but rarely had he found it so colourful. The Herdsman himself blushed an uncharacteristic red among a school of indistinct mermaids Thomas had never seen, and blonde-breasted Cygnus led her own phantom squadron described by troughs in a turbulent background of unfamiliar nebulae. Looking at Thomas' warfare pin, emblem of astral literacy, Mr Bradfield had warned the sky would be ``unfamilia.'' in the Deep White Forest, and that the Forest itself was landlocked, both of which were likely to unsettle Thomas. It had sounded like experience talking.

Thomas chanced a look over at Fury. She was still staring into the flames. She hadn't brought any provisions as far as he could tell, and he supposed she intended to sleep in the position she'd lain down in, without removing the enormous headdress, nor the boots with their spurs. Her stillness was surreal in the flickering campfire, her shadow on the woods behind her comically active.

Her eyes met his. He looked away, then looked back. She still stared at him. It was with great relief that he saw her face prepare to form speech.

``I don't mind questions,'' she said.





CHAPTER: Fury Breaks Camp

A Clearing in the Woods, Evening



Inscrutable to Hobby, three five-pointed copper stars hung between the chased brooches suspending Fury's bodice. The stars were connected by a copper chain and hung like bunting in a shallow arc before her heart. Hobby wore triangles. Hemlock squares. Christoffel's were spiral whorls. All were copper, the only metal whose refinement, possession, or use were permitted in the Forest, all polished daily like their spurs. Fury noted that Thomas' rank insignia, warfare pin, and belt buckle all were copper, she assumed substituted for gold and silver, and she judged his interest in the Forest to be sincere for a diplomat. So when he asked her, at her regrettable invitation, question after question, stirring up some matters she'd have rather thought about in daylight, she did her best to give him useful answers.

``How long have you been here.''

``The Forest? Forever. This post? Years. It's a very remote post: it's not easy to fill.''

``Far from HCF.''

``You've heard that acronym? Yes, about as far as you can get. We are not, as you would say, promotable.''

``Why not.''

``It's a rule.'' Fury paused, then added: ``It's for appearances. Because we are His daughters.''

``I see,'' said the gentle envoy. This charitable pair of words--in her native tongue the first was just this side of the midpoint from ``mil.''--had taken up a place in her mind as caption beneath the figure of Thomas.

He continued: ``How many of you are there? Is this a rude question? It's unclear, um, both the answer and whether it's impolite to ask the question.''

She took a bite of mushroom and said through a mouthful: ``Can't be counted. Not with your number system.'' She had a dozen oblique answers to this question. This was the most honest one. She detected relief in his eyes, utterly inexplicable, so she ignored it. With as gentle a shift in weight as was needed to steer Ontario away from a hornet's nest, she steered the Newfy: ``I've had your job, you know.''

His eyebrows went up. ``You have.''

``All of us,'' she said. ``Separately, together, Brávellir, Teutoburg, Meriton, on the trail with Chimopteryx, on the trail against Chimopteryx.'' She smiled. ``You don't know some of those names,'' she teased him.

``No.''

``Toffy--that's Christoffel--has a book for you. It has information.''

``That will be useful,'' he said earnestly, but should have said pointedly. He really was gentle.

She hadn't brought it. She hadn't brought anything, not a blanket, not food nor water. Fury could live off the trail forever if she had to. And she was forced to acknowledge a region of her heart that considered leaving the Forest forever, and that walking out un-provisioned to meet Thomas was an expression of that notion. Hemlock, Hobby, and Toffy would all be uneasy, she knew, but they wouldn't know precisely why. It was not very strange to walk a long distance, unarmed, for a mission like this. But it was a little bit strange.

Maybe she had been acting a little strange in general. She'd awakened from fitful dreams--their contents were, variably, too horrible to think about--and she'd suspected from an imperceptible nuance in the attitude of Hemlock's back and shoulders in the adjacent bunk that whatever involuntary somatic manifestations attended Fury's nocturnal psychic drama, her best friend was taking them all in. Had Fury cried out? Growled? She'd wet the bed on one occasion.

``I saw you sketching on the meadow,'' she announced. He blushed, she thought, and she asked if she could look at his drawings. ``Is that impolite.'' she asked.

``No no,'' he replied immediately and was forthcoming with the sketchbook. Lifting her glasses, she observed he was an excellent draughtsman. She was familiar enough with that aspect of the Forest he'd enjoyed from his seat on the meadow to appreciate how artfully he'd rendered, in only ink, the inexplicable darkness in that direction. She knew foreigners and the settlers called it darkness, what the archers called the way home.

She lifted the corner of the previous page and dropped her glasses to look up at him. After a moment he said: ``Go ahead.''

The drawings were a naturalist tour of other meadows and woods. Soft deer, ancient maples, a trout in a stream, all in black ink. Here was another officer reclining by a fallen tree. ``That's Commander Roos. Asa. My boss. My friend.'' After a dozen pages of meadows and woods there was an older man's face, tired, disillusioned, beneath an odd diagram of a human male, one of which she could make no sense. Abruptly she was in St Johns, on a wharf, then in a cafe, then a park with some bathing birds.

``I didn't sketch during the voyage,'' he explained.

``Operational security,'' she said.

``Yes.''

``Is this why they chose you? Because you can draw? Because cameras aren't allowed.''

``It's what I've got.''

No one had yet figured out how to make a camera that used only copper, but Fury knew one day someone would, and they'd all have to reckon with the true nature of the prohibition. She detected some authentic humility in Thomas' self-mocking reply, which was thin enough to betray the angular edges of the indignation over which it had been hurriedly draped.

She knew he'd sketch her right there and then if she asked. She had no intention of ever being sketched, even if that were permitted. Something, probably Fury herself, probably this restlessness that had become an unwelcome part of her personality, had unsettled the evening, and when Thomas, after a long gaze up at the crystallising zodiac, said he feared not being able to sleep for his eagerness to reach the ``true Forest,'' it was all the excuse she needed.

``We could go now,'' she said.

CHAPTER: Thomas Falls in Love with Fury

The Edge of a Forest, Night



He had only meant to excuse his inquisitive prattling. Now he hid his dejection, packing up his things as Fury kicked dirt over the campfire. But his restlessness was authentic. When she'd lifted her glasses to look at his drawings, then dropped them again onto her pug nose to look, vaguely impressed, up at him, he was lost in love with her forever. Henceforth, never would he prefer any geometries over such planes as constituted her expression in that moment, nor any colours over those provided by her pale skin in the firelight, the rust-red of her shaggy headdress, the woody brown of her bangs, the twinkling copper of her glasses, and the deep, fearsome blue of her eyes.



CHAPTER: The Satyr Meets with Kimberly

A Lecture Theatre, Late Morning



``So by the time they cross that little wooden bridge over the waterfall that marks the edge of the 'true Forest,' he is smitten with her. Now, it has been argued that whomever had gone out to meet him, that is with whom he would have fallen in love, and that this predisposition, not any artistic ability, certainly not any martial acumen, was why Lieutenant Shattering had been chosen for the mission. And, as he guessed--and we see from the diagram in his sketchbook that he unwittingly came closer than Ted Bradfield to understanding this--breaching that frontier in the state of being in love meant that love would shape, or reshape, the Forest for Tom Shattering and also for those who follow him in. So: how does the topography of the Forest map to such an obsession, and what are the consequences? That is, in part, what we intend to cover in this course, which is for the most part at the unclassified level, though there are some secret-level documents reserved in the Shaffley Library, with apologies to our foreign students.''

There was light laughter from the front rows, which were always filled with partner-nation students in a kaleidoscope of foreign uniforms. He knew each of their own intelligence services had those documents, and the students knew it, too. Smiling, he backed his wheelchair up, rolled to the podium where he'd stashed his briefcase, and placed it on his lap. By the clocks over each door, he had five minutes left, but instead of taking questions he dismissed the students and made his way back to Chao Hall--everyone called it ``the mes.''--greeting students and faculty as he pushed himself along the red granite walks. Thin columns of white smoke rose from the greens in the cool, still late morning air as gardeners in black jumpsuits burned piles of orange and yellow maple leaves under a deep blue Newfoundland autumn sky.

He heard hurried footsteps behind him before he heard ``Professor.'' and stopped and turned to greet a young lieutenant junior grade in khakis with a rucksack and an armful of textbooks. Her name tag read ``JAC.''. ``I don't want to hold you up, Professor.''

``It's okay,'' he said.

``I'm in your lecture.''

``How do like it so far.''

She laughed. ``Yes, so far so good. I'm training for foreign service.''

He waited. She wanted into his research group. His reputation and especially his budget attracted a lot of students eager to write an award-winning thesis, and to log a lot of travel on the Navy's dime. He already had a stack of unsolicited letters on his desk, which his current team would sift through hopefully before Christmas.

``I'm in my first year,'' she continued.

She was, he was sure, the daughter of the Chief of Naval Operations, Admiral Jack. He tried not to let that influence his inflection as he said:

``Do I have a letter from you.''

``No,'' she said, tucking some fallen white blonde hair back into her garrison cover. ``I thought I'd ambush you.''

``You're Kimberly Jack.''

She nodded, and in the next moment they exchanged by means of glances a succession of weighty, but ultimately obvious and banal, inquiries and confirmations that they were both too intelligent and too interested in the sublime to articulate. Acknowledging the instant connection with young Kimberly, he knew he'd likely be inviting her to join his team. Glancing again at her name tag, he also acknowledged what would likely be a lifelong failure to fully trust why he had done so.

``Do you always begin at the beginning.'' she asked. ``When he meets Fury in the meadow.''

They had resumed movement towards Chao Hall. The frenzied red squirrels of Autumn were the spectacle as they talked.

``I've tried it a couple different ways over the years,'' he replied. Again he was struck by the efficiency of communicating with someone for whom much of the connective tissue of conversation was taken as read. If platitudes like ``well, insofar as the story has a beginnin.'' and certainly ``do you have a better place to start.'', as well as her attendant rejoinders, and his rejoinders to her rejoinders, occurred to him, they had been skipped over, and he knew that the more they talked, the less space and time any such trivialities would occupy.

``The readings are impossible to organise,'' she offered. He nodded in emphatic agreement. She'd read them already. All of them. There was one obvious question. So obvious that their rapport could have easily elided its expression, save that she would want to demonstrate that she'd arrived at it on her own. If she asked it, she was in.

``And Ekkorbok.''

He stopped his wheelchair and looked up at her.

``Not a page,'' he said, smiling. ``Not a word.''



CHAPTER: Hemlock Worries About Fury

A Forest Lodge, Night



Toffy sat on the rug before the fire mending Hobby's saddle strap. In exchange, Hobby had cleaned up the eel guts and was in the kitchen mixing a pail of copper polish as Hemlock--four pairs of spurs, an array of kitchen utensils, a spade, and her bagpipes all laid out before her on the coffee table--scraped out the dregs of the vinegary white paste from another. All the doors and windows were open in an attempt to justify the fire that no one wished to extinguish despite the dying Summer having reasserted itself with such a warm evening. A bit of breeze was making it bearable.

Candles and lanterns extended the fireplace's glow in satellite spheres of amber throughout the large hall, including seven large candles high in the copper chandelier and a helix of small lanterns attached to the tall spiral staircase in the corner beside the fireplace. Diagonally across the hall the badger's drum kit and the hedgehog's bass completed a generous circle of chairs and more candles on copper stands.

The hall had once been filled with maple dining tables and chairs, just as the dormitory upstairs had once been filled with maple racks. Now there were only four racks upstairs, though oddly scattered being situated in their original assigned locations, and the archers dined in the kitchen, or at the picnic table outside, or on the settee by the fire.

``Oh that smells so good,'' said Hemlock, meaning the eels, whose meaty smoke rode the breeze into the hall.

Toffy tried not to look too proud as she pulled a thread through the tough black hide of the saddle strap.

``They are beautiful and big,'' she said of her catch. After a moment she found, as Hemlock knew she would directly, a reason to bring up the fox. ``I'll need to share mine.''

Hemlock looked up at Toffy, who did not meet her gaze, then over her friend's bowed headdress into the flames. Her hands continued polishing spurs--these were Fury's extra pair with small five-pointed stars stamped into the shanks--as she divided her mind to accommodate a gentle and perennial amusement over Toffy's shy affections and also a fresh and unexpectedly powerful wave of anxiety over Fury. She looked back down at the spurs, the copper acquiring the dark lustre that was so moving to the archers, the specular fracturing of ambient firelight that was its own bound flame, that described the curvatures of the shank, that was its own at least temporary allegiance to the hand that machined the bevels of the rowel's five vicious blades. That hand belonged to the goose-fairy Oca, who along with the bee-fairy Ape kept the one copper shop in the Forest two day's ride past Three Nations.

``You can eat it from a bowl by the fire,'' she teased Toffy, after a delay that betrayed her distant thoughts. Calling the fox a dog was a well-worn avenue of irritating Toffy, but Hemlock could picture the absurd scene. On more than one morning they'd found her curled up with the creature on the very rug where she now sat, arms thrown about his neck, both snoring.

Toffy turned her head in slight attitude of frustration, and raising her eyebrows said: ``Maybe I will.''

They both chuckled.

``Hobbs,'' Hemlock called into the kitchen, ``What do you reckon, half an hour.''

``Yes,'' came the reply.

``I'm doing my pipes,'' said Hemlock, putting Fury's spurs on the settee next to her and pulling her pipes before her on the table. ``I'll do the rest of this stuff tomorrow.''

The pipes with their black hide bag and bright copper drones and chanter were deliberate homage by Oca and Ape to the archers' uniforms. Hemlock knew Oca would have trimmed the bag in red pelt were there a source and had that not been illegal.

She scraped more polish out with her cloth and began working it into the copper cylinders, machines, and stops of the exquisite instrument. The privilege of playing it was never lost on her, and almost always on her mind as she worked the device were Oca's deft black and white hands working the copper and quiet Ape's gentle golden fingers scraping, tanning, dying, trimming, stamping, embroidering, and sewing the hide. More magic had been kneaded into these pipes in their crafting than ever could be wrung out in their playing, however prodigious Hemlock's was. Sometimes though, and it felt arrogant, she imagined her own inspiration was just as inexhaustible. Fury was the best bowman. Toffy the best horseman. Hobby was the greatest warrior any of them had ever known. But Hemlock's piping was the closest to matching the skill and beauty of the animals' music. Oca and Ape had made flutes and pipes of all design for Hemlock, from copper, maple and other more exotic woods, and fired clay. The chest at the foot of Hemlock's rack upstairs held some. Others, like these pipes, sat on shelves above the badger's drum kit and the hedgehog's bass amongst the varied horns, guitars, and concertinas the goose and bee had crafted for the other archers.

Maybe they would come tonight as well.

``You were in Three Nations today.'' she asked Toffy.

``At the market, yes.''

``You didn't see Oca or Ape, did you.''

``No. I would have liked to.'' In one motion cross-legged Toffy rocked herself to the right, drew a knife from her left boot, with a flourish of her left hand sliced the leather thread she'd pulled taught with her right, re-sheathed the knife, and rocked back upright. ``I wish they lived closer, don't you.''

``Yes, definitely.''

Toffy knew better than to bore Hemlock with reminders of the tightly knit, closely gathered community she'd enjoyed in Italy, though later that evening, like every evening, after drinking and smoking, Toffy would be on about it to anyone. But Hemlock also felt lately the compulsion to gather friends about, to account for them all. That's what was unsettling her, she decided, with Fury being out of the Forest.

They had been drawn together over the centuries by circumstance, but as far back as she could remember, Hemlock had trod alongside and angling ever towards Fury with deliberate purpose. There had never been a soul whose radiance nurtured her more fully nor whose company she craved with more eagerness. Here at the barracks lodge, which they all now just called ``home,'' she slept in the rack next to Fury's every night, and knew the sound of every phase of her friend's sleep. Over the years, restless late night whispered conversations had evolved into a communication of thoughts, movements in their respective beds, sniffles, stretches, and, rarely, expostulations as dramatic as a spurred boot-sole dropped to the red maple floorboards, a shared stifled guffaw, an elicited ``please, please shut up.'' from an exasperated Hobby. So many centuries of war, and they still harboured and cherished some shared immaturity.

In their music, Fury deferred to Hemlock's genius, the bespectacled archer's melodeon a vindicating and never reproachful harmonist to the melodic excursions of the flute, the pipes, the whistle, whatever instrument Hemlock played, however audaciously. Their music together alone in the woods was a delight to the Forest. In the now almost nightly hootenanny at the lodge, set amongst Hobby's horn, Toffy's mandolin, and the perfect arrangements of the woodland creatures, it could intoxicate a mountain.

They would play outside tonight.

As Hemlock settled her mind on this, the badger and hedgehog came in the wide open door.



CHAPTER: Thomas \& Fury Reach the Edge of the Forest

A Stream by a Waterfall, Night



In the moonlight he watched her drink from the little stream, her bottom in the air, and he knew he'd never known love. Desire, alive in him now the way a volcano is alive, was just one of infinite components, all infinitely powerful. If this hierarchy of infinities had a structure, it was not to be reckoned in the limited dimensions of any world Thomas had ever known or imagined. Mr Bradfield had alluded to the manifold nature of the Deep White Forest, and suddenly Thomas felt he understood, here at its frontier, how ill-equipped he was to understand such a place.

An intelligent man, it occurred to him to wonder what she, Fury, specifically had to do with this: the inevitability of his love for her felt a lot like proper--by which he meant deliberate--enchantment.

She looked back at him. The tendency of his eyes to want to rest upon her face felt like a kind of detent in coordinate space. Equivalently, the hidden substructure of spacetime notwithstanding, any aspect of her countenance became an arrangement of shapes and colours he had longed, all his life, and without knowing, to see.

She was staring at him now, another instance in what was to become a tradition of Thomas failing to read Fury's expression as he admired her face.

``You should fill your canteen, Thomas.''

The swaying of the landscape upon hearing her say his name illustrated the boundlessness of the obsession through which he now journeyed. This is a problem, he thought. I wonder if I will pass out.

He filled his canteen and sat beside her.

``Are you alright.'' she asked him.

``Yes, thank you.''

``I walk fast,'' she said, idly grooming her tall red fur boots. Thomas observed the polished black hide straps buckled round the heel, sole, and bridge of the foot to affix the bright copper spurs.

``Are those good for walking.'' he asked her.

``They're good for everything,'' she replied.

At their camp Thomas had changed into casual civilian hiking clothes and boots. He was having a little trouble keeping up with her, but, no, that wasn't the problem.

The waterfall was rather tall, but gentle, far from roaring. Thomas looked up at the little wooden bridge that crossed over the top of it.

``Who built it.'' he asked Fury.

``People. Settlers. They are a marker of sorts, of the frontier. A bridge over a waterfall. There's symbol for it.''

She made a little drawing in the air, which he thought he could reproduce in his notebook later.

She looked at him now. ``You coming in.'' she asked.

He was nonplussed. He had been adjusting his behaviour over the course of many hours to compensate for how interested he was in her and how uninterested she seemed to be in him. However successful the artifice, it not deluded him into imagining he had any real choice in anything anymore. That his mission momentarily aligned with her trajectory was this kind of terrestrial good fortune that was so muted under the glare the sublime and terrible providence of her advent, that he had honestly taken it for granted. Thomas never once thought ``lucky me.'' that he had a legitimate excuse to be in Fury's presence. There was something deplorable about such a thought. It's safe to say he worshipped her, which may have overshot the mark.

CHAPTER: Fury Considers Killing Thomas

A Bridge Above a Waterfall, Night



The hare once sang her a song--well, he sang a song in her presence, in a sunny birch grove on a hill, on a morning she'd followed him round swatting blossoms, feeling sorry for herself, being unimpressive, resenting him, adoring him, talking uselessly and endlessly past ears that only turned her way if she stepped on a twig, and only if it hadn't been deliberate, which it was sometimes--about his own funeral. In the song, everyone is dancing round his grave; meanwhile he assures the listener that, to him, this ``seems like a nice way to go.''

It was a bouncy kind of number, and it became a staple of the hootenanny, everyone enjoying the rollicking celebration of Death, whom the archers knew, though not as well as they knew Spring.

But on that morning, when he'd sang it just for her, maybe having just finished writing it in his hare-brain as they walked, she had made the first of many attempts to decode his messages to her, for surely you cannot spend as much time as they did together and not wish to comfort or rebuke a companion so obviously out of sorts. She had passed the lyrics through various transforms hoping to find a coordinate system in which the sentiments, less cryptic than in some of his songs, took the shape of him reaching out to her. Or telling her to go away. Or inviting her to live with him in his...whatever you call where a hare lives.

Fury shook her head a bit too violently and hissed an epithet as she mounted the bridge over the waterfall.

``What.'' Thomas whispered behind her.

Bottom line: if Hobby had chosen her for this assignment because Hobby knew Fury's honour would compel her to complete it and not run away for another year, well, that kind of insight and immediate pragmatism was why Hobby was their squad leader. If Fury had welcomed the assignment because she could use it as an excuse to stay in the Forest and lose her mind over the hare instead of escaping to who knows where, well, that was, Fury supposed, the beginning of a self-deception that was sure to consume her. Here at the boundary between Ratatoskr's Sanctuary and the secular cosmos He bent to His will by means of her bow, she knew she was a conduit of a malevolent corruption that stalked His domain.

She turned and looked at Thomas. What a perfect emblem he was of her own error, a recklessness unbound here outside the Forest, a foolishness she carried back to the hare, to her friends, to her country.

She thought about just killing him.

War with Newfoundland \& Labrador, she supposed, would result. Reeling herself back in to a place where that made a difference to her was immediate, but it took a hardy cranking. No, she would not actually have killed him. She looked at his upturned face, which she supposed she hadn't really looked at before, maybe for a moment after seeing his drawings. Gentle Thomas was, Fury could see, a good person.

She'd killed good people. They may have all been good.

No, her orders were to protect Thomas, and she could see by that face of his, those wide oblivious eyes--and by a dread that sat too thick over the Forest before them to be just her imaginings, and too copious to be the protoplasmic manifestation of her own sinfulness--that he would need protecting.

CHAPTER: Thomas Follows Fury into the Forest

A Bridge Above a Waterfall, Night



``Panthers.'' he thought he heard her whisper.

She was ahead of him on the little wooden bridge above the waterfall. Cowardice appeared beside him instantly, skinny and shaking, with gritted teeth, gripping his upper arm. Thomas fixed his own jaw and dismissed that pitiful cousin to all civilised men, a ritual he'd practised since childhood, before asking Fury:

``What.''

When she turned to him, alarm was not what he saw on her face. Her quizzical expression calmed and interested him. He had an instinct that it was she who wasn't confident about crossing the border, though he couldn't think why this might be the case. Was he about to be betrayed?

She frowned at him, but something in her eyes--he forced himself to ignore the blue that, even turned away from the moonlight, even in the shadow of her headdress and behind her glasses and overlong bangs, pierced through to pin his heart like a specimen to the black wax of night--reassured him, and with less condescension than he'd read in them before. It was a motherly look.

Thomas could see that the woods beyond the stream became denser, but the trees looked no different than the trees on this side. There was nothing frightening about the night, nor the Forest around them.

``I'm sorry,'' he whispered to her, ``did you say panthers.''

Then she blushed, which immolated his poor pinned heart. Thomas decided right there that his situation with her was emergent, that it threatened the success of his mission. He needed to draw on some reserve of strength to hold himself together when interacting with this woman.

``That's a curse word here.'' She nodded toward the Forest. ``In the Deep White Forest.''

``Oh,'' he said, ``I'm sorry.''

She laughed softly. ``No, it's not a very bad one.'' She looked away and thought. ``Well, it can be.''

``Um,'' he said, ``Fury,'' and she looked back at him, eyebrows raised as he said her name, ``are you reluctant to bring me in there? Am I going to die in there.''

Maybe this was the way. If he couldn't pour out his affection, maybe a candour about their respective missions could provide some kind of satisfying and slightly forbidden intercourse and at least distract him from his distraction.

She leaned on the rail of the bridge and regarded him.

``We don't know,'' she said, ``Hobby, Hemlock, Christoffel, and I--that's my squad, that's all of us--we don't know why you are here. You are very welcome, Thomas. We are going to take very good care of you, and no enemy of yours has a prayer of harming you in our company, I can assure you.''

Her confidence was electrifying. Nevertheless, this was working, and Thomas had surer purchase in the real world as he replied:

``Arrowheads.''

Now it was Fury who asked: ``What.''

``I have arrowheads for you. In that rucksack on your shoulder.''

CHAPTER: Hemlock Talks to the Animals

A Forest Lodge, Night



Hemlock rolled a joint on her lap. She sat on a chair in the circle watching the badger and hedgehog tuning their respective instruments.

``What will you play tonight.'' she asked them, uselessly. Their inscrutable eyes gave, as ever, no indication they acknowledged her presence. The badger tapped repeatedly on the snare drum as he cranked it into tune, and the sound seemed to wake up the hall. One by one, the hedgehog gently plucked endlessly sustaining bass strings, and Hemlock felt herself sinking warmly into the tones, impossibly low, impossibly rich, moving both her gut and the long white hairs on her ears.

``I will play the pipes,'' Hemlock went on. ``I hope you'll like it. We love your playing so much. Christoffel is beside herself.''

Tears filled Hemlocks eyes.

``We love you so much,'' she continued. ``We comprehend you not. We are like the musical instruments messily arrayed round Saint Cecilia's feet. Our meek talents impair your perfect music. Though we fought upon the plains of Thessaly, we cannot match you in any measure.''

She lit the joint on the candle in the stand beside her and inhaled deeply.

``We never stop trying,'' she croaked, then exhaled. ``And I think you'll acknowledge we don't play any wrong notes. But there is a place we cannot seem to go, where you live. I don't know if you credit our enthusiasm. I don't know if it counts. Uncanny, you are. Especially that hare, to whom song itself seems to belong.''

The hare hadn't yet arrived, nor the fox, nor the otter. She and Hobby had seen them all together in silhouette atop a far hill outside Three Nations. They'd evidently had divergent business since. For the moment, Hemlock had the rhythm section all to herself.

``What is this alien flavour you bring to song.'' Crossing her legs, Hemlock became philosophical. ``It's familiar, and it's mysterious. It's a fiction, and it's true. It's a memory of something yet to occur. Do you understand.''

They ignored her.

``No, of course you do. An unconscious consciousness. A crisp blur both concealing and revealing who we were before we became ourselves. Fury sees something, hears something I mark her, how she attends the hare's melodies with her counterpoint, it's different. How her fair attention is captured by his colloquial human tongue. Oh, you are strange, with your wet onyx eyes that tease us with silent demurrals. Watch Fury when the hare sings: there is something of cherish in her gabled brow. Something there is that pulls her to him, though I know the love she carries in her heart belongs only to Lord Ekkor, may it never perish. But I think she dreams of him. The hare. I think our friend Fury dreams of our friend the hare. She has fitful dreams.''

Hemlock dragged again deeply on the joint and moved her eyes across the paintings and mementos that filled the wall to the left of the shelves full of musical instruments.

``But she cries out for a fish. In her sleep. Can you comprehend.''

She thought for a moment.

``Do you know any fish who sing? Or, I don't know, swim through streams of consciousness in song? For whom a fish might stand? What a fish might portend.''

She looked at the hedgehog's sweet face with its black, moist nose as he pressed his ear to his instrument, stretching himself tall as he could to turn the peg and fine tune the heavy copper string. His spines splayed behind him as he reached, a treacherous fan of white-tipped black lances. His bright, black, round eye was a deep and indifferent cosmos.

``Such beautiful eyes, so dark. How they loom in the mind. Wonderful peace, woeful doom, there ensphered.''

She thought of Fury returning from a morning walk, eyes red, laconic.

``Does she love him.'' she asked the hedgehog.

The creature seemed now to be satisfied with the tuning of his instrument. He pulled the bow from its affixed leather sheath and dragged the waxed horse hair across the lowest string. Hemlock felt the note in the hard maple seat of her chair. She closed her eyes. A tear dropped from her cheek onto her wool skirt making a dark stain.

The badger looked at the hedgehog and nodded approvingly.

``All at once,'' Hemlock said, ``I recall a room in a village we sacked. A fair, unsoiled place that was a girl's bower ere we came, with white sheets. We left it an abattoir.''

Christoffel came in from outside.

``They're here,'' she said, a bit giddy. She saw and smelled Hemlock's joint and frowned. ``Hey, give me some of that.''

Hobby followed her in.

``I thought we were playing outside,'' said the tallest, quietest archer. She leaned over the hedgehog to retrieve her horn from the its place on the shelf. He looked up at her, and she looked down at him. ``Hello,'' she said.

``I forgot,'' Hemlock said. ``I was lost in thought.''

Toffy passed the joint to Hobby, who took a small drag then passed it to the badger. The fox walked in, guitar strapped to his back. Then the otter carrying maracas. Finally the hare with his guitar and his ideas.

CHAPTER: Thomas Shows Fury the Arrowheads

The Deep White Forest, Night



Thomas had read whatever intelligence the Navy had provided about the Deep White Forest's Icelandic settlers. They'd been here for centuries. It was said that many of them were wholly ignorant of their Icelandic roots. Attendant theories abounded, none very convincing, most ultimately devolving into discussions of geography. The presence of Icelandic, but not Newfy, settlers was invoked to support hypotheses on the Forest's terrestrial location, which, paradoxically, Iceland--as far as Naval Intelligence could discern--had yet to identify. Meanwhile, Newfoundland \& Labrador's Royal Court's early, serendipitous, accidental communication with the Forest's Royal Court had developed over seven decades into diplomatic access, and the kind of physical access protected by the elaborate procedures Thomas and Asa had gone through in the previous few days.

Thomas knew little about, and was not very interested in politics. What he did know was that providing copper arrowheads to the Deep White Forest and its millions of mounted archers was good for Newfy industry. Actually, he didn't know that, but that's what he'd been told, and he'd been trained up on these new advanced bodkins, given some samples, and sent to open up the market.

He watched Fury's face as she looked at the arrowheads.

She'd led him across the bridge and they'd sat down side by side next to the stream, now properly on the God-King Ekkor's lands. He'd unbuckled the rucksack she'd been carrying for him, pulled out the heavy, flat walnut box covered in Navy supply codes and numbers, entered the combination into the security lock, unlatched it's lid, opened it, and handed it to her.

Sixteen shiny torpedo-like copper bodkin arrowheads sat in sheep-hide-lined slots, two rows of eight reflecting stripes of moonlight onto Fury's broad cheek. They were perfectly machined, indistinguishable from one-another except for tiny unique serial numbers etched into each base.

The fairy archer ran her fingers over the polished copper admiringly.

``We use broadheads,'' she said.

``I know,'' said Thomas. ``They're--we're working on a design that's more familiar to you. These are a prototype.''

``They're big,'' she said.

``Working on that, too,'' said Thomas.

She turned her head to look at him.

``They don't seem particularly sharp, Thomas,'' she said. ``Is Newfoundland \& Labrador also working on making sharp arrowheads.''

``They don't need to be,'' said Thomas. He looked down at the arrowheads, a rare occasion of him forsaking an opportunity to look in her eyes.

She looked back down, too.

``Well,'' she said, ``I've seen many kinds of weapons, including some Newfy ones, and I trust there is something special about these.''

Thomas nodded.

``We should get going,'' she said after a moment. She handed the box back to him. He secured it and returned it to the rucksack, which Fury returned to her shoulder.

They walked side by side now, on a level leafmeal trail wide enough for a carriage or even a truck. It wound round low hills thick with pine trees, scattered with budding maples, elms, and ash. The full moon rode along between the branches of the trees on either side of the road, throwing Thomas and Fury's shadows behind them. The fireflies had all gone to sleep or been eaten by bats. Though owls conversed across distances from time to time, the woods were a rather quiet background to the soft clink...clink... of Fury's spurs. Sometimes the peeping of frogs would grow and fade as they passed unseen ponds. Thomas supposed the road followed the stream, or a branch of it, but not very closely.

The warm night had cooled, but only a little. Thomas felt comfortable in the walk, and there was nothing very unusual about these woods. He oddly felt that had his mission simply been to walk silently beside Fury along this moonlit road for the entire year, he would have been up for it. She had told him the walk would take about three hours, and she'd slowed the pace.

This was Thomas' fourth assignment to a foreign land. He'd been to the South Asian Islands, to Arabia, to Italy, and in each place he'd been popular with the local militaries. He'd delivered Newfy weapons, Newfy training, and handed out hundreds of tickets for travel to St John's, Hopedale, and Goose Bay for advanced military schools.

Everywhere he'd gone, after a while, at least once, though they'd likely been instructed not to, someone had asked him about the DWF or about the archers. He'd never needed to be coy. He knew as little as they did. They had chuckled knowingly. He had said: ``No: honestly.''

Now here he was.

As awed as he'd been on the journey by some of the covert operatives he'd met or seen, both uniformed and civilian, many of them clearly very highly trained, he was beginning to get the sense that none of them had actually ever set foot in this Forest. He had, in the fleet, heard the DWF called the ``forbidden forest,'' but as a joke.

``Fury,'' he said, and how it thrilled him to say her name, ``am I the first Newfy ever to come here.''

``You might be,'' she replied. ``I would have thought you'd know that better than I.''

``Why are there no border guards.''

``You will have seen for yourself how difficult this place is to find, Thomas.''

Thomas knew that the reputation and size of Ekkor's legion of mounted archers was the only deterrent a trespasser or potential invader would need to consider. When he'd asked Fury for a number, her answer had been as vague as Naval Intelligence's estimates: hundreds of millions, billions, some staggering amount. Given that historic battles had reputedly turned on the arrival of only four of these archers and their horses, geopolitically speaking, Ekkor was both irresistible force and, if you could find Him, immovable object.

``Your Navy protects Newfoundland \& Labrador,'' Fury said.

``Yes,'' he confirmed.

``Have you spent a lot of time at sea.''

``A fair amount. I've been doing security assistance for four years now. When was the last time you did it? Advised somewhere, I mean.''

She thought for a moment, then looked at him, considering.

``What.'' he asked her.

``Kalkriese, I guess,'' she said finally. ``I mean, we were fighting too, but we knew a lot of those guys. Especially on the other side.''

A distant crow objected to something. Thomas let a moment pass before asking: ``What were you going to say.''

She let out a little laugh. ``No,'' she said, ``it's nothing. There are some places we've been that you wouldn't understand. Don't be offended. And I don't mean it's a secret, necessarily. I just don't think it will make any sense to you.'' She smiled at him. ``We have a year.''

They walked in silence for a while. Despite not feeling particularly tired and being very interested in these 'places' she'd been, Thomas agreed that there would be time to understand more. Besides, processing her smile in a way that did not lead to his own annihilation was occupying all his faculties.

After a half hour, they saw the first quartered square of yellow light through the trees. A house.

``Settlers,'' said Fury. ``There's a little village over that hill.'' She pointed. ``Not Three Nations, where your hotel is. That's past the barracks. We may not be able to check you in until morning.''

``It's okay,'' Thomas said quickly. ``I can camp.''

``No,'' she shook her head, ``We'll go to the barracks.''

She seemed hesitant.

``I look forward to meeting your squad,'' he said.

She didn't reply.

They passed more houses, all some distance from the road, from which side-paths now occasionally diverged. Horizontal lines of livestock fences were now visible here and there, criss-crossing the trees at their bases, describing clearings of uncertain geometries.

``The trees are sacred, right.'' he said.

Fury's gaze followed his into the Forest to where a small expanse of a farm was obvious.

``They pay for every one they cut down,'' she said absently, apparently in affirmation, and he was surprised by her casual conjunction of commerce and the sacrosanct. Then it occurred to him there was a more sinister interpretation of her remark. He didn't know which to prefer.

It didn't matter.

Everything she did, everything she said, every glance, every laugh, every evasion, every rebuke, the way her feet fell with soft padded clinks on the path, the way her knees shone in the moonlight between her boots and skirt, the relaxed and somewhat exaggerated way she swung her lanky arms as she walked, the soft-looking hair on her forearms, the rough, capable look of her big hands, her broad shoulders, the strange, long, white, whiskery tufts of hair that grew from helix and targus of both ears, the way the twin oblate copper octagons of her glasses sat on her nose, a nose she wiped now with the back of her hand as she walked in the cooling night, her low, breathy voice that delivered her accented English to his ear like a calm river of rusted honey, her enormous red headdress with its tall, tufted fur ears and its black hide strap that hugged her downy cheeks and chin the way his hands longed to--

--he wasn't sure if he'd sighed just then. He sniffled to cover in case he had.

And her smell, oh her smell. He'd first noticed it when they'd sat on the bank of the stream looking at the arrowheads together. It was a chemical smell, not like benzene or medicine, but like skin after an electrical storm, though richer, more coppery, he supposed, and a bit animal. It was intoxicating to him. When, by virtue of a thoughtful head-scratch and the absent momentary collection of her hair into her hand, he chanced to see the soft brown down on the back of her pale neck, he came the closest to fainting, imagining her smell there would be the most intense, that his nose and lips in that place would find a softness and richness so profound that only the oblivion of death might suitably attend the calamity of such a moment ending.

Now her head was down, her eyes on her boots as she strode. Thomas felt the tall, strange reality of her, walking so close beside him in the ever-shifting volume of space she occupied, that Fury-shaped absence of anything that was not her. His love was absurd. There was no action he'd rehearsed with the women of St John's or various ports of call that was appropriate to this extraordinary form and function. Slipping an arm round Fury's waist, running his hand through her soft brown hair, gazing into her eyes: all were comedies. His simple awe felt like the only response condign to her nature.

They walked in silence for another half hour, passing one more collection of small farms and houses. A smaller path diverged to the left, and Fury pointed and angled him towards it. Though his shoulders were stiff from the burden of the two packs, Thomas didn't welcome what appeared to be a closing in on their destination. He'd've walked forever with her.

He smelled a home-fire. He heard music. Topping a small rise they looked down on a bridge over a small river, and a two-story log chalet in a clearing just beyond. The windows glowed warmly with a hazy amber light that seemed to pulse with the music. Smoke rose and drifted toward them on a light breeze--the night was definitely getting colder--from one of two large chimneys. A stables with a loft sat off to the right, nearer the river.

Thomas paused but Fury kept walking. When she stopped and turned to him, the moonlight shone on her face, her home behind her. He captured the moment for a drawing to be done later; he'd been doing that since he first saw her.

``We don't have guest quarters,'' Fury said. ``There's a couch in the tack room.'' She looked toward the stables. ``It's comfy.'' She looked back at him and nodded emphatically.

He laughed. ``That sounds very nice,'' he said. He looked at the lodge, the shifting glow from its windows and the lively music evoking a celebration within. ``Is it a party.''

She looked at the lodge, then back at him. ``It's the Hoot.''

Thomas raised his eyebrows. ``The Hoot.''

``Hootenanny. Making music and singing, dancing. You know.''

She lifted her forearms, bent her pale knees, and bopped a little to the beat coming from the lodge. The sight was so surprising to Thomas that he snorted, expelling a long trail of clear snot down his face. It hung and swayed from his stubbled chin in the moonlight. Fury stopped dancing and stared at him for a moment, then turned and resumed walking toward the lodge. He wiped his face and followed, flicking snot into the grass.



CHAPTER: Christoffel Plays with the Band

A Forest Lodge, Night



Oh, how he played.

Christoffel was doing her best to keep up with the fox as he strummed, finding stretches and hollows in the architecture of his masterful harmonies that she could humbly and sweetly decorate with her balalaika filigrees. She stared into his eyes, knowing that if he met her gaze, it was probably an accident, knowing he'd soon blink and look away, as he did, as they all did.

Meanwhile the hare sang about ``the Forest moon tessellating the gloom in a Stygian lace of polygons betokening: no one can break your heart.'' His inscrutable poetry.

The badger and hedgehog bounced the triplet rhythm along, with Hobby cheekily overblowing the accents on her horn, the tall otter beating a tambourine and swaying with Hemlock, who buoyantly swung her hips left and right as her wooden flute hopped up and down the registers. Hemlock was locked onto the hare's singing, and cued imperceptibly by him and an abrupt key change dropped her flute from her lips and sang the next verse to God with ecstatic lyrics that strained the propriety of mere reverence:

``Oh to climb the forbidden Mountain, and drink from the King's own fountain, clutching shocks of his rust-red down.'' It was the kind of lyric that once would have made Hobby dart narrowing eyes at the other blonde, and made Toffy herself giggle or gasp, but they were all used to it now.

The hare joined Hemlock with a harmony as she continued:

``Oh to taste what I've longed to taste, winding rivulets of His grace streaming down from outer space and pouring over my heart.''

Christoffel had written about this to Arthur, about how in song nothing seemed to be taboo. Arthur played flute, like Hemlock...but not at all like Hemlock. He had replied in a letter--smuggled like all their letters through a network that terminated on this end with Oca and Ape, Christoffel's access to it sustaining a special bond with, and debt to, the two winged craftsmen--that she cherished above all his others. In it he had provided a framework for her understanding of her own joy through music, establishing the art as fabrication intended not to deceive, but to bring one gently, lovingly, willingly to deeper truths than could be understood through reason. Those truths, as far as Christoffel was concerned, must belong to God, and if the journey to His House passed through secular fantasies and corruptions, it was well worth it!

``I can see His House from here,'' she thought, the essential archer's prayer, as she closed her eyes and plucked her balalaika, tripping down the profane wooded path now painted by Hemlock and the hare's voices in a syncopated stichomythia of terrestrial pleasures.

When she opened her eyes, Christoffel was the first to see Fury and an agog Inuk boy standing in the door, staring at the exuberant song circle.



CHAPTER: Thomas Meets the archers \& Animals

A Forest Lodge, Night



What struck him more?

The three fairy archers--one playing a balalaika and looking directly at him, one apparently even taller than Fury playing a copper horn, and one with a breathtakingly pretty face and electrically green eyes singing her heart out--all in those same splendid uniforms and astonishing headdresses?

Or the monstrous woodland creatures, also singing and playing musical instruments?

The hall was filled with pot smoke, and he had an immediate thought that the scene could be explained by that. That they were all high, and appearing the way they did was an externalisation of that, so it made sense. It took him a moment to arrest this inverted logic and resume his bewildered awe. Shame on his arrogant and ultimately ill-equipped reasoning mind for interrupting his feeling heart and instinctive gut, the two sectors of tripartite Thomas better suited for an honest reaction to such a sight. All three were overwhelmed in the end, and poor Thomas--exhausted from journeying, hiking, and treading for many hours straight-faced and bare-soled across the infinite plain of white-hot coals into which ardour for Fury had transformed his emotional landscape--fainted.

CHAPTER: Hemlock Greets Fury

A Forest Lodge, Night



Fury was back.

Mid-phrase and floating on gusts of pot and music, Hemlock looked over just in time to see the Newfy officer collapse in a heap next to Fury, who looked down at him then back at Hemlock, shrugging and flashing a comic smile.

The unspoken signal to cease precessed through the band, measure by measure, player by player, until all that remained of the song was a long, low, sustaining note from the hedgehog's bass. All eyes were on Fury and Thomas at her feet. The hare took the opportunity to take a long drag on the joint that had lain burning in an ashtray on the chair next to him. Without looking, the fox slowly leaned over, reached out, and muted the hedgehog's string with a gentle paw. There was silence.

Hemlock placed her pipe on the chair next to the ashtray and crossed the room to Fury.

``Let's pick him up,'' said Christoffel, slinging her balalaika round onto her back. Fury put down the rucksack she'd portered for Thomas. Hemlock punched her in the shoulder.

``Hey,'' said Hemlock in a chiding tone.

``Hey yourself,'' said Fury. They smiled at each other then watched as in one fluid motion Christoffel hauled Thomas by his collar and belt off the maple floorboards onto the long teak bench beside the outside door. His jumper tore in the process.

``I'll mend that,'' she said.

Hemlock would look at the stranger directly, but for the moment, and through a pleasant delirium, she regarded her friend's face. There was something comforting in Fury's expression, a kind of resolve. But also there was a tincture of sadness in the deep blue of her eyes, making them darker, wetter than usual.

Hemlock put her hands on her hips and said to Fury: ``I. Am. High.''

Fury laughed. ``Yes I can see that.''

``Are you alright.''

Fury stretched. ``I'm fine. I'm hungry.''

``There's an eel for you in the kitchen,'' said Toffy over her shoulder as she nudged Thomas' legs into steady resting positions on the bench.

``No there isn't,'' called Hobby from across the hall. She was seated, idly polishing the flare of her horn with the inside hem of her skirt. The other archers looked at her. She casually pointed at the otter who was sharing the hare's smoke, his eyes closed, his long body lulling into a relaxed S.

Hemlock glanced at Christoffel and gripped Fury's elbow, and for a moment they all stared lovingly at Hobby seated in the candlelight, horn in her lap, the hare and otter smoking behind her. Hobby saw their looks and shook her head, returning to her horn polishing. The others traded amused grins. Hobby's evolution from cautious enabler of and skeptical participant in the Hootenanny to chartered member was complete, thought Hemlock.

She looked down at the dark-haired, unconscious visitor on the bench. Christoffel was still kneeling beside him. He had a nice, gentle face. He looked very young, and Hemlock couldn't put the term ``ma.'' to this boy. She looked back at Fury, who was also regarding him.

``It's really funny you brought him here,'' Hemlock said to her.

Fury looked up, and Hemlock saw the darkness in her eyes again.

``I wanted to come back,'' Fury said.

``You couldn't have gone to the Chanticleer,'' said Christoffel.

``That's for sure,'' said Hemlock. The hotel in Three Nations may have once been a full-time, full-service resort, but now there were rarely guests, and staff seemed to work very limited hours. It seemed a sad place, though its proprietor, whoever that was, Hemlock had no idea, kept the building and grounds looking beautiful. The leaves were raked in the Autumn, snow cleared in Winter, hedges trimmed in Spring. Even the swimming pool was kept open and clean in the Summer.

Maybe this liaison lying here would bring The Chanticleer back to life.

As she looked at him, he opened his dark hooded eyes.

CHAPTER: Thomas Meets the archers

A Forest Lodge, Night



The green-eyed, blonde, very pretty fairy archer was looking down at him. She stood next to Fury, coming only up to her shoulder. Another, with dark hair and copper eyes, was kneeling beside him.

Thomas sat up sharply, and they all pulled back slightly, on guard but unafraid. The kneeling one stood up, revealing herself to be the shortest, and joined her comrades in their consideration of him. She gathered the long dark hair streaming from beneath her headdress into a ponytail and secured it with a black hide band from her wrist.

``I know. I passed out,'' he said.

``This is Thomas,'' said Fury.

``I'm Hemlock,'' said the blonde one.

``I'm Christoffel,'' said the dark-haired one. ``Don't stand up. I'll get you a drink.'' She hurried to the kitchen, calling back over her shoulder: ``Are you hungry.'' He heard her opening drawers and cabinets. ``We have dried fruit. We have bread. We have cheese. We don't have any eel. We have nuts.''

There was a run of bass notes.

Thomas turned his head and took in the sight again, this time safely seated.

Unmistakably, though in a haze of smoke and in the softening amber glow of a multitude of candles and lamps, a hedgehog was playing a double bass. Directly, a badger joined him on a copper and hide drum kit. A fox and a hare joined in on their guitars. An otter gently tapped a tambourine. They played a gentle, folksy instrumental number.

``We have a lot of brandy, Hemlock.''

From the midst of this musical menagerie, another fairy archer, taller than Fury, with straight blonde bangs that nearly hid her eyes and a single plait that reached her bottom, stood from her chair and strode towards him holding a hunting horn. Suspended between her copper brooches were three copper triangles. Thomas looked back at Fury and Hemlock. Fury wore three copper five-pointed stars. Hemlock wore three copper squares. He hadn't looked at what the fourth, the one in the kitchen, wore.

``We have dried seaweed. Where did we get seaweed.''

``This is Hobby,'' Fury told Thomas, ``our squad leader.''

``Triangles,'' he said. ``Do all squad leaders wear triangles on their breast.''

The archers exchanged glances.

Hobby frowned. ``Only this breast,'' she said, tapping her chest, ``bears this symbol.''

The one called Christoffel emerged from the kitchen with a clay plate of bread and cheese. She handed it to him. ``Each archer's battle dress,'' she said, ``displays a unique symbol.'' She lifted her chain of three copper spirals. ``Mine's a whorl.''

``What does it mean.'' asked Thomas. ``The whorl.''

``It describes the abyss that is Christoffel's charity,'' said Hobby.

``It's the swirl of her senses when she sees foxes,'' said Hemlock, twirling her eyes and a finger in the air.

``Fury, Fury, Fury,'' said Thomas, shaking his head, reeling, holding up his hand like a schoolboy stopping a lesson to ask an important, clarifying question.

``Yes, Thomas.'' said Fury, leaning in to him.

He pointed past Hobby to the creatures. ``Is this-.'' he faltered. He whispered: ``Am I seeing this.''

Fury stood erect and looked at the other archers, then over at the creatures. Her eyes scanned them. She seemed to regard them contentedly, then look away abruptly. She cleared her throat. ``Yes, they're real, Thomas,'' she said.

``They're weird, right.'' said Christoffel. ``Try the cheese, it's good, it's Icelandic.''

CHAPTER: Fury Helps Thomas Acclimate

A Forest Lodge, Night



Back in the hare's presence, Fury felt relief, anxiety, misery, warmth...her attempt to take stock of her feelings trailed off, promising only an infinite sum of inadequate, pathetically inadequate, terms for a longing that anyway could not be teased apart into components, that was not the superposition of all those things, but was its own irreducible and terrible entity. Playing his guitar in the candlelight, his eyes shining, his long body rocking, his fine ears casting twin lenticular shadows on the red hidebound volumes of Ekkorbok in the floor-to-ceiling shelves behind him, he was lovely, and she was lost in him. He was gently tapping one large, soft, white-soled foot on the maple floor, and she felt she could hear and feel that soft thumping below and above and through and over and beyond all the other instruments, that her heart would slave to its tempo, whether he slowed or rushed, larghissimo or prestissimo, however life-threatening either might prove.

The band had continued the number after the interruption, and now the hare sang about the blackness of the sea at night. How could he know about that? When she saw Thomas' reaction to hearing the creature vocalise, she surmised that the verse was for their guest, and she felt resentful that Thomas should get this kind of attention. For a year she'd stretched and pulled at the hare's lyrics trying to fit them to herself, but they'd always fit poorly, like borrowed clothes that make one appear like the lender. Now this Newfy sailor walks in and the creatures accord him a nautical serenade.

``Aye, they sing,'' Hemlock was saying to Thomas. Fury detected that Hemlock tuned quickly to Thomas' wavelength, more quickly than Fury herself had done, if she had at all. The hare, Thomas, Hemlock, all connected to each other in some way that excluded her. She knew she was descending into an outright pout, and turned to the most reliable source of cheer she knew.

``Toffy,'' she quietly interrupted the introductions continuing with Thomas. Christoffel turned to her with big solicitous amber eyes, and Fury's mood was instantly buoyed. ``Is there any eel left.'' She watched her friend's eyes shift from sympathy to determination.

``Here,'' said Christoffel and surprised Fury by popping the lit joint she'd been holding into Fury's mouth. ``I will find some.''

Fury laughed, inhaled, coughed, and croaked: ``Okay,'' calling ``thank you.'' after Christoffel, who was already in the kitchen.

``Your singing is very beautiful,'' Thomas was saying to Hemlock.

``Me.'' said Hemlock, looking round to Hobby and Fury. ``I am a crow over an empty grain field. It is their genius, and it is not one part will, but they sway in the music's breath and they yield to its eddies.''

They all watched and listened as the band played on, the otter now harmonising with the hare.

``They open their mouths and fill their lungs with song,'' Hemlock continued, stoned and rhapsodic. ``They don't warble and trill out their longing, rather they invite longing. They are passengers on the music. He doesn't talk who would sing.''

``They can't talk,'' Fury added helpfully to Thomas. ``Well, anyway, they don't.''

Thomas watched the creatures play and sing. He mimed perplexedly with his own hands and jaw. ``How does that even work.'' he said.

``Their strange faculties dance in flight and only light on gut, skin, bone, and fragments of the Moon.'' said Hemlock, swaying.

Fury tried to explain: ``The instruments have a magic.''

She offered the joint to Thomas, who thought for a moment. She watched him quickly employ an equation--familiar to her--that calculated his duties as officer, ambassador, and cultural liaison before shrugging and accepting.

Fury continued: ``They're made by Oca and Ape, two craftsmen in the Forest who specialise in copper, but also work in, as Hemlock said, pieces of the Moon. It's the name of their shop, in fact. In their language.''

``Meteorites.'' asked Thomas, squinting, exhaling a cloud. He handed the joint back to Fury, who dragged on it again and thought.

It was her turn to shrug. ``Sure,'' she said.

``It is they,'' Hemlock said, nodding toward the band, ``who are magic.''

Fury marked in Hemlock's voice the despair of a virtuoso for whom virtuosity can never be enough. She handed the joint to her.

``Your talents give glory to Ekkor, Hemlock,'' she said. ``I should wish the one to burn in Hell who does not love to hear you play and sing.''

Hemlock glowed, and Fury saw Thomas do a double-take, then satisfy himself that it must be the weed. She smiled, not sure why this amused her.

Instead of asking why Hemlock had briefly illuminated, Thomas asked: ``Why do you wear those hats.''

The three archers looked at each other.

``Those, um,'' Thomas looked at each of them in turn, absurdly patting the top of his head, ``red, you know...''

``Red like blood,'' said Hobby, straight-faced, and Fury felt the first diplomatic challenge coming on. She knew her friends would be civil, but there were some things that...

``Red like roe,'' said Hemlock, which was just confusing to everyone. Fury looked at her and frowned, squinting in sisterly reproach.

``They're dark orange, is what they are, Thomas.'' interjected Toffy, emerging from the kitchen with a plate of eel scraps arranged and decorated with garnish so lovingly and artfully that Fury felt tears come to her eyes. ``Like ground up pottery. Here.'' She handed the dish to Fury, who shook her head and smiled in mock wonder and authentic gratitude. They were smiling at each other when Thomas asked:

``Why do they have the ears of the red rlisquer.''

Fury had never seen Hobby kill someone with a horn--she'd never seen anyone kill anything with a horn--but that's what Hobby held at the moment, and Fury knew that's what was about to happen.

Hemlock, instantly sober, flew to restrain Hobby even as Thomas chuckled, licked his lips and attempted to repeat the word that the Forest would not allow to be uttered nor writ.

``Thomas.'' Fury shouted, almost dropping her plate.

Christoffel moved to help Hemlock, and the two shorter archers shoved their tall squad leader away from Thomas and toward the band, who were playing and singing, unconcerned.

Thomas stared at Fury, more confused than alarmed, still working his lips, which he believed had failed him. She looked over at Hemlock, who, still shoving a fuming Hobby, looked back over her shoulder with wide eyes, but also a grin to let Fury know things were under control.

Fury widened her eyes back at Hemlock, pushed her free hand under her bangs to rub her forehead, and shook her head in exaggerated relief. She sat next to Thomas, plate in her lap, and looked straight ahead at the volumes of Ekkorbok on the opposite wall by the spiral staircase. After a moment she turned her head to look at him.

He raised both hands in a gesture of ``What.''

Christoffel installed herself and Hobby into a new song the band was starting, placating Hobby's appetite for slaughter as gracefully and resourcefully as she'd addressed Fury's literal appetite. A competent diplomat herself, Toffy became even more artful as she got stoned. It was something Fury had observed dozens of times but always forgot. She looked down at her plate: leftover scraps of eel masquerading as delicacies on discs of sliced pickled plums atop crackers, all drizzled with barbecue sauce and sprinkled with fresh ginger and flakes of dried herbs. Fury knew there would have been very little meat left from the archers' repast--the badger, she knew, would have eaten Fury's own share whole--but she also knew Toffy's skill and speed with a dagger, having watched her rapidly blind scores of enemy prisoners at the orders of more than one field commander. She could picture Toffy deftly poking residual meat from between the delicate ribs of the eel's comblike skeleton.

``Thomas,'' said Hemlock, returning and sitting on his other side. ``Thomas,'' she repeated, then reached across his lap to steal one of Fury's eel hors d'oeuvres. ``We have a lot to learn about each other,'' she said through a mouthful.

``He's brought arrowheads,'' said Fury.

Hemlock raised her eyebrows. ``Really.''

``Yes,'' Fury said through her own mouthful, ``they look interesting.''

She could tell Thomas was still perplexed about what had transpired with Hobby, and that her attempt at a change of subject hadn't quite taken hold.

``We should have a demonstration,'' said Hemlock, taking the silent cue. ``Tomorrow.''

Fury began to object until she realised Hemlock was prompting Thomas' own inevitable objection in order to distract him. It worked.

``Tomorrow.'' said Thomas, snapping into the moment.

``Sure,'' persisted Hemlock, ``why not.'' She threw a glance at Fury, who subtly raised a hand to caution her flirty blonde friend not to push it too far. Hemlock's face and charm had a way of subjugating stronger wills than gentle Thomas'.

``Although I think it is tomorrow,'' Hemlock said. She looked at the clock on the mantle. ``Not quite.''

``I had thought to wait until after meeting Lord Ekkor,'' said Thomas.

Both Fury and Hemlock stopped mid-chew. A brassy note from Hobby's horn indicated that she hadn't entirely stopped listening to the idiot envoy. Fury looked over and observed Toffy leaning into Hobby, both literally and musically, entreating her to calm down, to play with her, and to ignore what was clearly the naïve blathering of the weary and overwhelmed traveller in their midst. They continued duetting over the creatures' deft accompaniment. Fury's eyes met Hobby's, and the formidable squad leader tilted her head to let Fury know she was safely, privately, but with some difficulty, processing Thomas' persistent blasphemy.

``Thomas,'' said Hemlock, ``I don't know what you've been told, but you won't be meeting Lord Ekkor.''

She looked at Fury. So did Thomas. Fury shook her head.

``Let's have a drink,'' said Hemlock.

CHAPTER: The Satyr Employs Kimberly

A Lecture Theatre, Late Morning



``These are legendary horsemen. Prodigious archers. Among the most storied warfighters known to history.''

He crossed from beside the podium to centre stage. He'd learned that pacing in a wheelchair was particularly distracting to students, but a well-timed roll could add emphasis.

``None of you will be surprised to learn how hard these four women partied.''

He got an intended laugh from his military audience.

``Their musicianship might surprise some of you, but I have discovered among you, from all nations, and particularly among you special operators, a disproportionate number of lovers and able practitioners of music. Now, typical of a sailor, Thomas also indulges in the grog...''

Some more laughs. He paused, then segued into the day's topic:

``...whereby Thomas traverses the second of three critical thresholds: oratory, gustatory, and physical, surrendering, one by one, each of three tiers of man, the cerebral, the thoracic, and the visceral.''

Kim, who had volunteered to assist him for the length of the course, auditioning for a permanent position on his team, called up an image of a pertinent diagram on the amber screen behind him.

``I'll say this plainly: in the company of fairies, one may happily dance all night and the next day to many a pitched and spritely reel. Or drink with them to Diana and to Pan. Or declare one's Christian name. But do all three: dance, drink, and tell them your given name, and they will turn on you and steal your soul.''

Now there was silence. He let it sit a moment.

``In the meadow when he'd met Fury,'' he continued, ``he'd said I'm Thomas.''

``Actually, he said I'm sorry I'm Thomas,'' an N\&F Marine captain in the front row said, eliciting more laughter, mostly from other Marines. The naval officers, including Kim, and the foreign students remained stone-faced.

Only the second lecture, he thought. Might as well address it.

``I understand some of you will have personal feelings about Lieutenant Shattering and about his trial. I'm going to ask you to keep an open mind. There is privileged information in this course which I think--even if it doesn't change your mind about the man--may help contextualise the decisions he made.''

Three sentences he had to utter every year, at some point.

He returned to the lecture.

``Now, Thomas has not danced with any fairies at this point. He is, as you've seen, a somewhat shy person. Maybe a bit of a sorry chap.''

He smiled at the Marine captain, who shrugged and nodded good-naturedly.

``Let's take a moment to consider the word dance. It comes from an old Frisian word meaning to tremble.''

Kim brought up a diagram of the word's etymology.

``Thomas trembles on this, his first night in the Deep White Forest, a night that has turned out to be colder than anticipated, but far from dancing it is rather a fearful shivering in hay, in a stall, kneeling before Fury's horse, Ontario.''

Kim called up the next slide.



* * *



``Dancing is fucking, right.''

Kim smoked a cigarette as he finished his pie. It was cool and sunny in the city. They sat outside the Diamondback, heavy lunchtime foot-traffic brushing past them on the narrow boardwalk. It was a popular spot at all hours for faculty and students, despite being a half hour walk from campus. Half the lunch crowd on any given weekday were in uniform. Both of them nodded and smiled frequently, greeting acquaintances and colleagues as they passed. Sailboats leaned on the harbour and tugs pushed a submarine tender out toward The Narrows. The seagulls were legion.

``Sometimes,'' he replied, taking a sip of his beer.

``Explain, Professor,'' she said and sipped her own.

``We have a letter that must have sat inside a volume for many years, pressed so firmly against the printed text that in made an imprint onto the letter.''

``Christoffel's letter? Can we talk about this here.''

He looked around briefly, reflexively, before dismissing her concern.

``It's fine,'' he said, lowering his voice anyway. ``It's not secret. It's like the course: 'unclassified but sensitive.' No, not the archer's letter, but Arthur's reply. It was written on a unique paper pressed from an extremely alkaline Florentine pulp: cypress and an unusual reed that grows along the banks of the Arno only after it floods. The blood and soot ink used by Ekkorbok scribes binds to the fibres. The transferred text addresses your question.'' He leaned back in his wheelchair. ``At least we think it does. It is mostly figures and equations, some kind of analytic description of the region of behaviours and participants subtended by the expression 'dance with the fairies'. But it's a fragment, and what we've been able to translate is abstruse even for Ekkorbok.''

``How much have you read of Ekkorbok.'' she asked, lowering her own voice. ``Word is it's more than anyone outside the Forest.''

``That may be true,'' he said.

A seagull landed on the boardwalk's steel rail and eyed the remains of his pie and mashed potatoes. He regarded the unfeeling, yellow-eyed scavenger.

``Except Tom,'' he amended.

She would ask now.

``Do you speak to him.''

He weighed his answer, knowing she'd read the truth in the weighing. Kim's father could have him fired, imprisoned, deported, all before dinner.

``Never mind,'' she said and smiled.

They sat in the sunshine as the wind picked up. The sailboats leaned more acutely. Seagulls worked harder to hover in place over prospective targets. Uniform hats flew off heads escaping flailing, grasping hands. Kim crushed out her cigarette half-finished: smoking wasn't any fun in high winds. This was air fresh from Labrador. He felt it's chill in his wounds, his skull, his femurs, his tailbone.

``Do you want to head back, Professor.'' Kim asked, showing a concern that depressed him. His ageing, long forestalled, had progressed and was evident. White spirals had begun to populate his beard. When his enormous afro, its dimensions comparable to the fairy archers' headdresses, receded enough, he would need more surgeries.

``Let's sit a bit longer,'' he said. ``I like the wind in the sunshine.''

CHAPTER: Hemlock Reconnects with Fury

A Forest Lodge, Night



The liaison was peeing in the woods. He would not be permitted upstairs where there was a toilet, just as he would not touch an archer, nor speak the forbidden word in the Forest.

``You could have prepared him a little,'' Hemlock said to Fury as they reclined on the couch before the fire. They both had glasses of whisky in their hands, Fury's resting on a small black pillow on her lap bearing a white embroidered scene of nymphs and satyrs. Their booted feet knocked idly into each other on the coffee table. Toffy had resumed her position on the rug, now mending Thomas' jumper. Hobby, uncharacteristically, was still playing with the band, a gentle nocturne with the badger using brushes on the drums. The animals would play until morning, which was almost here.

Toffy looked past Hemlock and Fury to Hobby playing her horn. ``You guys forget how devoted she is to Him, because she does anything you want.''

Hemlock and Fury looked at each other then at Toffy.

``It's true,'' said Toffy, returning to her sewing.

Hemlock, after a brief hunt for something soft to throw at Toffy, chose the small pillow Fury had on her lap. Fury spilled a bit of her whisky, laughing as the pillow bounced off Toffy's headdress and into the fire.

``Panthers,'' said Hemlock, slumping back onto the settee and grinning.

``That's what you get,'' said Toffy without ever looking up or breaking the rhythm of her stitching.

The pillow combusted instantly, filling the room with the stench of burning swan feathers.

``That'll get them going,'' said Hemlock, meaning the Fox and Otter, who loved, above all things, to eat swan. Fury and Toffy laughed.

``Ape made that pillow,'' said Fury.

``I know.'' barked Hemlock. ``Anyway this is your fault.'' She punched Fury's thigh.

``Ow.'' laughed Fury. She punched Hemlock's thigh and barked: ``I know.'' More whisky spilled on skirts and the settee.

Thomas walked in the door, which had been opened to cool down the room a bit. He stopped. He was steady, but quite drunk. He wrinkled his nose at the smell. There was something Hemlock liked about the helpless way he looked standing there in the threshold, the Forest night behind him, the glow of the fire on his Inuk face. She elbowed Fury and nodded towards him.

``Thomas, are you alright.'' Toffy asked. ``It's feathers. We had an accident.''

``No,'' said Thomas, ``it's just a nice picture, you all by the fire.''

``Oh yes,'' said Fury. ``Thomas draws.''

``Oh really.'' said Hemlock. Mischief, never far from her, wrenched her head around to address the band. ``Hobby, did you hear.'' Hobby's eyes were closed as she softly blew. She ignored Hemlock.

Fury punched Hemlock's thigh again, this time hard.

``Panthers.'' cried Hemlock.

Thomas sat on the chair at a right angle to the settee, his back to the open door.

``What is that, 'panthers'.'' he asked.

God, that sounded funny coming from his mouth, Hemlock thought. She saw that Fury and Toffy thought so, too.

``It's a curse word,'' Hemlock told him.

Thomas said: ``Like....''

They all stiffened.

``No! No, no,'' said Hemlock. ``Not anything like that.''

Hours earlier, over the first of many drinks, they'd carefully explained to Thomas about the forbidden word, and how the Forest would never allow it to be formed by voice nor ink, and that it was profound sacrilege even to try. He had started to ask why that word in particular was forbidden, but Fury had sternly explained that even talking about the word was heresy, and Hemlock and Toffy had distracted him with drinking and teaching him card games of the Forest. The archers had cycled in and out of the song circle. Thomas had stayed out of Hobby's way, and she'd politely ignored him. Drinking and smoking and singing had carried on, more snacks had been foraged from the kitchen cabinets by Toffy, and Thomas and the creatures had cycled into the woods and the archers upstairs to relieve themselves.

Hemlock had watched Thomas grow a bit less nervous round the creatures, but still he kept his distance from them as well as from Hobby. The creatures showed no sign of interest in Thomas, naturally, though Hemlock thought she'd detected the tiniest augment in their performances tonight, as if they'd discovered a way to bisect into strips that infinitesimal region separating their art from perfection, and then traversed the near half as a matter of course.

Thomas had told the archers about his life in St John's, about his job at Navy headquarters, and about his previous assignments overseas. They had told him about the Forest and the Icelandic settlers, about their wide-ranging patrols, and a little about some of the operations they'd been involved in over the centuries.

She suspected that he'd given himself over to the drinking and smoking when he'd realised that his sober mind would be no more capable of apprehending all he was taking in. Hemlock knew the Forest was an unusual place, and that she and her sisters, despite outnumbering all other beings, were a mysterious culture to those outside it. Everyone knew this. But this historic liaison, this first envoy, signalled a change in how Lord Ekkor, her King, her Father, chose to relate to those mortal nations.

So why wasn't he at His Central Force in Vedauwoo, the ring of mountains surrounding the Mountain, His Mountain, at the centre of the Forest? Why out here at this lonely outpost? She supposed HCF and St John's were easing into the practice.

``Are there,'' Thomas was asking Toffy, ``pan--those animals in the Forest.''

``He means cats,'' Hemlock said.

``Oh,'' said Toffy, ``it doesn't mean that here.''

``That word is older,'' said Fury.

``Yes, there are cats.'' said Toffy cheerfully. ``We know one who plays a tuba.''



CHAPTER: Thomas Considers the archers \& Animals

A Forest Lodge, Early Morning



He was not going to make it a year here. He'd fallen in love with one of them, infuriated another, and found the other two equally confounding in their respectively bizarre humours. He'd discovered they were, every one of them, difficult to look away from. The fairy eye held the human eye, even as it terrified it. And now that he had three other faces to compare, he realised many elements of Fury's alien beauty were simply features common to the Deep White Forest's fairy archers.

They all had the strange, wispy tufts of snow-white hair growing from their ears. It projected out and up and back, and drooped in arcs like plumes almost to their shoulders. They all had thick eyebrows and pale skin. Their faces all had that same soft down as Fury's, catching the firelight in a glow at certain angles. Their bodies were very slender and sinewy, like marathon runners, and they were all terribly strong, with broad shoulders and a relaxed bearing, a capable presence that girdered, rather than filled, space. The effect was particularly powerful with Hobby and Fury, who were very tall. Only Christoffel was shorter than Thomas.

They wore identical uniforms, except for the three medallions suspended between their brooches. A star, a whorl, a square, a triangle. They assured him they were unique, but he thought it unlikely that four such familiar symbols should adorn the breasts of these four squadron-mates, with perhaps billions of sisters across whom such devices must be distributed, the simple and recognisable, like a square or triangle, covering only a small portion. They'd had no explanation for this, and he hadn't pressed the point. He'd shelved this mathematical paradox in his mind amongst a small but growing collection of things about this place that didn't add up.

The one called Hemlock had a dizzyingly attractive face and bright green eyes that seemed particularly to see through Thomas. She was not unkind, but she was the clown of the group, her barbs occasionally quite sharp. She reminded Thomas a bit of Asa, also a fairly attractive blonde, also as likely as not in conversation to reward sincerity and earnestness with gentle, not necessarily unkind, ridicule.

Christoffel's-.''Toffy,'' the others called her--eyes were a copper as metallic and bright as her whorls, and were the only pair in which Thomas detected an authentic and troubling lunacy, the kind folklore might ascribe to the eyes of a fairy. She was very talkative, conveying a great deal of meaning, but from all points of view at once, ultimately revealing very little about her own thoughts.

If humour was Hemlock's preferred method of distancing herself from others, and verbosity was Christoffel's, then silence was Hobby's. The towering squad leader, whose ice-blue eyes pierced out from behind pin-straight blonde bangs, set her long face and wide jaw with a firm expression Thomas had yet to witness soften, even as she drank, smoked pot, and sang and played with the others. It wasn't angry, nor even especially hard--they all had thick lips that tended to undermine grim looks. It was simply immutable. The other three were very expressive when they sang. Hobby's singing was not without emotion, quite the contrary. But her face kept its secrets, and outside of song she was nearly as silent as the woodland creatures.

The creatures.

What was Thomas to make of these beasts? His urgency to sketch Fury was as covetous as it was documentary: he wanted to possess her beauty. But the creatures had to be seen to be believed. Legends over the years, and Mr Bradfield over thirty minutes, had alluded to confounding wonders of the Deep White Forest, but in the scant intelligence shared with Thomas there had been nothing that was not abstract. He thought he understood why. Such stark unreality did not affect one in any predictable or even mensurable way. Walking into that hall and seeing them, and now spending time in their presence, dislodged entirely a rationality that in hindsight seemed always to have been poorly secured, teetering. He foresaw turning in his drawings of animals playing musical instruments to Naval Intelligence, and he foresaw a medical discharge.

He watched the creatures sing and play. The dread was profound. If such things exist, what else exists?

``Are all the Forest animals musicians.'' he asked Fury.

``That,'' said Christoffel as she sewed, ``is an interesting question.''

``There was a time,'' said Hemlock, ``before we knew they could sing.''

``It was a long time ago,'' said Christoffel. She looked up at Fury, who was silent and expressionless. ``Fury heard them first. Out past Oca and Ape's workshop.''

``It was a long time ago,'' a distant Fury said.



CHAPTER: Fury Tells Hemlock About Meeting the Animals

By a Forest Lodge, Afternoon



``Hemlock,'' said Fury, ``may I tell you something.''

They were chopping wood behind the stables. Hobby and Toffy had felled a maple in the thick grove by the Chanticleer, chopped up the branches and piled logs in the sheds by the hotel's outdoor fire pit, then dragged the trunk back to the barracks lodge on ropes behind Mercury and Cheops. Those two horses and their two riders were in the river now.

Hemlock was dripping sweat, bringing down the copper axe with cheerful vigour, her tanned forearms like maple themselves. Without breaking her rhythm she replied to Fury:

``You may tell me-.'' Chop! ``--anything.''

``I have met some musicians.'' Fury, also sweaty, sat smoking a cigarette in the sunshine. ``Some other musicians.''

``Settlers.'' Hemlock reoriented herself on the trunk and swung into fresh bark. Chop!

Fury had thought about her next words for many months. ``Creatures,'' she said. ``Animals.''

``Ha,'' said Hemlock, ``that's interesting.'' Chop!

Fury had known Hemlock wouldn't necessarily be surprised. In centuries of warfare in other realms they'd seen all manner of strange creatures engaged in strange activities. But it was usually something violent, or as a beast of burden like their own horses, and usually in the service of some person or divine being. When she'd first come upon them in the Forest, after hearing their music from a distance, Fury had assumed that's what the musical woodland creatures were doing: entertaining someone. When she'd crept up to peek out at them from behind a wild rosebush, she'd expected to see a golden-robed God or some legendary master of animals stretched out on the Forest floor in the broken sunlight, delighting in their music. It would not be the strangest thing she'd seen in the Forest.

The animals had been playing for themselves, and that was the strangest thing she'd seen. She'd watched and listened for hours, undetected. The next day, she'd gone back, and they had been there again. And the next. Fury had just set out on a long Summer patrol, so she hadn't been expected back at the lodge. She'd returned to that hidden place--it wasn't very hidden--to watch and listen for two weeks, before finally setting out towards the foothills, and she'd pushed poor Ontario to exhaustion making up the time on a six-week patrol squeezed into four. Toffy had repeated the patrol in the Autumn, and if she'd noticed the late entries in the remote logbooks--of course she had--she hadn't mentioned it. What did they find on these patrols anyway? What threats to Ekkor, what evidence of insurrection, what rents in the fabric of His apparently mostly empty Forest society? They never found anything.

``There's a fox,'' she said to Hemlock's swinging back and shoulders. ``He plays guitar.''

``I see.'' Chop!

``And a little hedgehog with an enormous double bass.''

``Mmm.'' Chop!

``An otter sings.''

``Oh, they sing, too. Huh.'' Chop!

``A badger plays the drums.''

``Badger on drums.'' Chop!

Fury heard Toffy singing down on the riverbank. Hers was a voice that was round and crystalline at the same time, like a glass bell.

Chop!

The sun was getting low and huge and orange. Fury crushed out her cigarette and blew a plume of smoke into the slanting rays.

``There's a hare,'' she said.

Hemlock stopped chopping and turned to look at Fury. She held her axe across her hips, her breast heaving a bit from the exertion.

``Yeah.'' she said. ``What does he play.'' Fury looked into her friend's bright green eyes, always so alive and warm to her, always knowing her, always understanding her. She felt tears coming to her own eyes, tears she couldn't explain any more than she could explain having kept the creatures a secret for a year. Nor did she need tears to communicate with Hemlock. She could see in that emerald gaze realisation that something important was being divulged, and a loving patience that would wait an eternity if necessary to hear--or never to hear, if Fury preferred--it spoken.

CHAPTER: Fury Reconciles Herself to Her Duty

A Forest Lodge, Early Morning



Hemlock hadn't worked it out. Not that day by the woodpile, during Fury's continued description of the creatures and their songs. Not in Fury's admission that she'd made herself known to them, that she'd since visited them in secret, even using patrols in other directions as a pretext, and that she'd brought along her accordion and joined in their playing. Not in Hemlock's own first encounter with them, together with Fury in that same grove weeks after their wood-chopping conversation, playing her wooden flute and joining Fury in vocal harmonies of simple oohs and aahs.  Not when together they'd solicited Hobby for permission to invite the creatures to the lodge, nor when Fury and Hemlock had exchanged confused, hopeful glances after watching the badger take the little map Hemlock placed on his snare drum and lay it gently in the grass beside his wooden stool. Hemlock hadn't worked out, in the ensuing years during which the creatures had become a bigger part of all their lives than any of them might have predicted, that Fury had fallen in love with the hare. And that failure of her eminently perceptive friend, who was adept at discovering all manner of secret doors and passages, factored large in Fury's feeling that this terrible love was unthinkable. She'd wanted Hemlock to guess. She'd wanted Hemlock to know a part of her soul no longer belonged to their Father, did not give glory to Him, and was in fact more insane than He.

``I've mended your jumper, Thomas,'' Christoffel said as she folded it neatly in her lap.

``Thank you very much,'' said Thomas. ``You didn't have to do that.''

The hare was now singing about ``this old Wood,'' presumably the Forest, how it was ``a cannibal, sometimes,'' and the badger evoked jungle drums on his tom-toms. Hobby blew percussive honks on the downbeats, and the hall took on an atmosphere of everyone getting a second wind. Hemlock sat up straighter and put her arm round Fury's shoulders. Fury leaned her headdress into her friend's. She met Thomas' gaze as he drank. His eyes were watery and narrow. Christoffel had found rum for him in the storehouse, which he seemed to like much better than whiskey.

The band wrapped up the number and paused while the badger and fox drank and smoked. Fury watched Thomas watching them, his wonder and alarm having been soothed now into a curious awe.

What was she going to do with this person for a year? She mapped it out in her head: a week to get settled in, another to establish a routine, then...

The main question was: could he ride with them? She didn't relish it, but a couple long patrols could fill up a good part of the year. They had no horse for him, so he'd have to double up with one of them. Hobby was thinking about it, but had warned Fury that they might have to get HCF approval for this. Physical contact just wasn't allowed. People--mostly enemy combatants--had tried to touch Fury and her sisters over the centuries: all had been quickly killed or de-limbed.

Why them? Why here? Fury supposed--they all supposed--this was a way of easing into a new practice. Send an inconsequential junior officer--Thomas fit the bill--to an inconsequential outpost. What harm could he do out here at the edge of the Forest?

What destruction could he bring Fury she wasn't already bringing herself?

And here it was: she could give Thomas the time she'd been giving the hare, and even if Thomas proved as uninteresting as he so far seemed to be, it was a healthier use of Fury's time. She looked at his watery eyes, now watching the band as they kicked off a new tune.

``I went out to the Deep White Wood.'' sang the hare. Fury smiled. She saw Christoffel smile. She knew Hemlock was also smiling. They all liked this number.

CHAPTER: Thomas Mistakes Ontario for the Holy Ghost

A Forest Lodge, Early Morning



``'Cross the mountains and prairies.'' sang the hare.

Thomas recognised himself as soundly drunk now. Cute Christoffel had found him a bottle of delicious, crystal clear Island rum--God knows how they'd gotten their hands on that. He'd stopped smoking the pot hours before. He preferred the rum. The archers preferred pot. The animals liked both.

``And there in the Deep White Wood I found beautiful maids.''

Fury was resting her head on Hemlock's, both of them staring into the fire, which Christoffel was twisting round at the waist to feed from the woodpile behind the spiral staircase.

``Banging on the snare and bass.''

Behind the woodpile, more bookshelves. Much of the wall space in the hall was taken up by built-in bookshelves filled with matching dark red hidebound volumes with copper titling. Ekkorbok. Their Bible. ``If each letter of the Hebrew Old Testament were itself a volume,'' Ted Bradfield had told him, ``you'd have a work a tenth the length of Ekkorbok.'' There was a small desk by the window catty-corner from where Thomas sat, opposite the band. On it some volumes piled up, some open, and a bottle of ink. They study it, Thomas thought. It was more than he could say for himself about his own Bible, though he considered himself a devout Catholic. He looked forward to reading what he could of Ekkorbok. If that was permitted; it wasn't clear.

``Dressed in furs of red squirrels.''

Wide with alarm, Thomas' eyes snapped to Fury's face, then Hemlock's, then Christoffel's. He saw only dreamy or closed eyes, smiles, and heads nodding to the beat. Hobby, still sitting with the band but evidently having no part in this song, at least not yet, cradled her horn in her lap and looked unperturbed, and in fact more relaxed than Thomas had seen her so far. He felt an absurd indignation, but he had no wish to tattle on the hare, whose blasphemy the archers had obviously been too stoned to notice.

They smoked a lot of pot, these women.

Maybe it was alright for animals to say squ--the forbidden word. He made up his mind to ask Fury at some later point, so as not to incriminate the hare.

``I joined that ring of fairy girls.'' the hare continued.

He looked at Fury again, resting her head on her friend's, holding her hand now, and gazing into the flames. A wave of longing for her washed over him, and he turned his head away.

``This is one of those nights you wish would never end,'' said the happy elf on the hearth, smiling up at him in his chair, his jumper still in her lap. She was almost right, Thomas thought. If the night had infinite possibilities, the way a magical night was meant to, then forever would be acceptable. But from its inception his longing for Fury had a core of impossibility, maybe because she had a core of impossibility. The Forest itself had such a core. Thomas, who'd had a privileged upbringing, and who had never sought anything not readily available to his talents, had little experience with futility. He was not an ambitious officer, and had fallen into his security assistance role almost by accident. Ironically had allowed him to see a lot of the world, more even than most sailors, and enough to slake even a profound thirst for cultural exploration, which his was not.

As for the women of St Johns, Thomas had never pursued anything more than idle dalliances, and had rebuffed--occasionally with a cowardly insensitivity--anyone ardent. His father's sisters--four of them--had taken an interest in suggesting eligible women to him over the years, but none of his aunts were married, and their choices reflected an unfamiliarity with or antipathy towards his tastes. As for the temptations of the world's ports, Thomas had been less Catholic here and there, but he'd surprised--happily he thought--many contractors with a relaxing, well-provisioned and relatively chaste hour of modelling as he sketched them.

Thomas' father, Captain William Shattering, Royal Newfoundland \& Labrador Navy, retired, owned a drawing by Rubens. It was a simple chalk sketch of a Spanish maid leaning against a stone garden wall draped in wisteria, and it hung in the conservatory overlooking the grassy slope down to the cliff above St John's Bay. Thomas had copied the drawing many times as a teenager, in the Summers, home from boarding school, in the evenings, observed in the faceted yellow glow of the conservatory by hundreds of rabbits on the slope. The woman in the drawing was lovely, the Flemish master's technique salient and sublime, but what inspired young Thomas to copying was her wrinkled brow and slightly open mouth, as if Rubens had captured her expressing impatience with his laboured sketching. Rubens' wish to preserve a reaction most artists would deny struck Thomas as funny and self-deprecating.

To say that Thomas was comfortable in Fury's ambivalence would, however, this evening, be taking it a step too far. Ephemeral notions of self-destruction coalesced about him, threatening to solidify. Rum can do that, he thought. Really, he thought, he ought to get to his hotel.

Instead, childishly, he chose to provoke her.

``Don't you ever take them off.'' he asked, his eyes indicating Fury's headdress.

All their eyes fixed on him.

``And when I emerged from the Deep White Wood I hung my head in shame.'' sang the hare.

``They're sewn to our scalps,'' said Hemlock, expressionless.

Thomas blanched. He looked to Fury then Christoffel for confirmation of this grisly detail.

Fury nodded solemnly. Grimly, Christoffel reached into her sewing kit and held up the large needle and hide string she'd used on Hobby's saddle strap.

After a moment Hemlock grinned, then the other two cracked smiles as well. Fury snorted, which made the other two laugh openly.

Thomas managed a wan smile through what he was certain was a deep blush.

``For I'd danced among the fairies.''

``Excuse me,'' he said, rising. Their amused eyes followed him. He turned and, even drunker than he'd realised, walked shakily toward the open door.

``Your jumper.'' called Christoffel.

He turned in time to catch it, smiled at them over this little triumph, and walked out into the still dark morning, intending only to pee again.

* * *

So this was Fury's horse, Ontario.

After peeing in the woods, he'd been drawn down to the river by the half moon's wobbly reflection. He'd looked at his own unsteady moonlit image on the water's dark surface then suddenly realised that he was proper cold. He'd donned his jumper, smelling now of Christoffel's lap: eel, marijuana, the home fire, and was it field mint? He'd wandered back up the bank and heard a soft nicker from the stables. He'd gone through the oversized portico into the darkness, even as from below the horizon an infinitely thirsty sun began to leech the ink from the fabric of night.

Now he found himself standing in hay inside Ontario's stall, looking into the large, quiet animal's darkly shining eyes. Thomas resisted an urge to pat its nose.

From the lodge, he heard the band and the hare still singing. ``Had I another soul to trade, I'd trade if only once more...''

Ontario. How'd you get that name? Thomas wondered. More and more, he was becoming aware that both the Icelandic Republic and his own kingdom had pollinated the culture of the Deep White Forest more extensively than anyone in St John's imagined. To the extent Fury and her friends represented that culture, that is. Unselfconscious about partying all night in the presence of a newly arrived emissary--leaving the magical animals aside for a moment--the archers reminded Thomas of the few special operators he knew in the Navy. They played as hard as they worked and had nothing whatever to prove.

Ontario was enormous and brown, with a darker brown tail and mane. The morning light crept in while Thomas stood there, admiring the animal's immaculate coat. There was something comforting about seeing an animal that was just an animal. Steam came off his hide and the hay.

``...to dance among the fairies.'' The song ended. There was laughter and clapping.

There exists a line in space, Thomas now chanced to observe, passing between two stands of trees on a hill just South of Three Nations, a few miles from Ontario's stall, meeting the road after its westward turn, joining it in its approach to the archers' lodge, passing through the window of Ontario's stall, connecting at the far end the rising sun, and at the near end the red maple wall to Thomas' left. An amber rectangle appeared there quite suddenly, illuminating the room until Thomas looked at the rectangle itself, at which point he was blinded. It subtended a prism of hay dust, steam, and swirling cross sections of Ontario's breath that spanned the darkness of the stall. Having appeared, it travelled quickly down the wall, striking after some minutes an array of copper horse armour hanging there, throwing an elaborate reflection onto the wall behind Ontario.

``To dance among the fairies,'' Thomas said to the horse. ``I think I'm in love with your, is it 'owner'? 'Rider'? 'Master'? What do you call someone who controls your destiny? Who steers you? Who restrains you? Who provides you sustenance? Who lances your flank with her cruel spurs.''

Ontario was motionless, steaming, its breath heavier than air, swirling, sinking. Thomas watched the reflected pattern on the maple behind the horse evolve as the light shifted, now the aspect of a star-flecked nebula, now a laughing dragon, now suddenly erect golden wings, from his vantage appearing to emerge from either side of the horse's withers.

``You might be a God,'' Thomas said, smiling. Here in this strange place, he supposed any animal might be magical, any tree might be animate.

Ontario might be a God. Ontario might be his God.

``What does the Holy Ghost look like,'' six-year-old Thomas had asked the nuns in Montreal, where he was to board and study for the next twelve years.

``Petit Tom, on ne Le voit pas,'' Sister Jennifer, as fresh to her vows as Thomas was to the world, had replied. ``One cannot see Him. But if you ever do, you will know Him. Le connaitras.''





CHAPTER: Hemlock Finds Thomas in Ontario's Stall

A Forest Lodge, Early Morning



The badger started another number with a gentle, steady kick.

``You found me down here in my Hell,'' sang the hare.

Fury was lost in the flames.

Hemlock lit another joint, took a drag, and handed it to Toffy, now flat on her back on the rug before the fire.

Hemlock had to admit to herself that parts of Fury had become opaque to her. Thomas, meanwhile, was clear as glaze ice. He was smitten with Fury, pathetically so, but Hemlock still knew her friend well enough to know that Fury had played no intentional role in it. The only thing that had developed in the hours between their rendezvous outside the Forest and this morning was the Inuk's imagination.

``Know me better than I know myself.''

Hemlock found it troubling that Fury was oblivious. The four archers knew the world of men, and how vulnerable educated men are to abstractions of their own primal nature, particularly very civilised men like Thomas from very civilised kingdoms like Newfoundland \& Labrador. Stags in rut are easier to discourage than a well-read and besotted artist like Thomas, for whom a smack on the nose might only eject with a ding!, from a slot on the top his carnival-toylike head, a sonnet.

Ooh she was high.

``What are you giggling about.'' asked Toffy.

``Is our gentle envoy,'' Hemlock wondered aloud, having picked up the epithet from Fury, maybe telepathically, ``a little bit ridiculous.'' She sipped her drink.

``Still, You think I'm good.''

``I thought they'd send an assassin or an explorer or something,'' Toffy said at the ceiling. ``He's very...'' She put a finger to her lip and closed her eyes, searching for a word.

``Useless,'' said Hobby from across the room, just loud enough to carry over the band.

Hemlock guffawed, then sputtered, having found herself with two uncomfortable nostrils full of whiskey. Toffy's eyes widened and she bit her lip in mock alarm. Hemlock recovered to find Fury still lost in thought, staring into the fire.

Panthers! thought Hemlock, suddenly irritated with Fury. She got up, breaking her friend's reverie. Stepping over Fury's legs just roughly enough to communicate her annoyance, she crossed the room, picked up her pipes, and took her place next to Hobby.

``Not put off by this life of sin,'' sang the hare. ``Not fooled by this animal skin. I've been hiding in the Wood.''

When the song reached a point that invited it, Hemlock crushed mightily the hide bag between her hip and elbow and filled the hall and surrounding countryside with the heartbreaking sound of her pipes.

By the end of the song, both Toffy and Fury had been drawn back into the circle, singing gentle harmonies in a chorus of the morning. They always knew when it was the last song, though never when it started.

Hemlock looked at Fury's face in the deep silence that fell afterward. Sunshine poured into the hall. A blackbird whistled somewhere. Fury eyebrows went up and she smiled. Hemlock smiled back. The creatures began packing up their instruments. Christoffel began moving chairs. Hobby started picking up glasses and copper ashtrays.

``Someone had better go look for him,'' said Hobby.

Hemlock volunteered.

She stepped out into the morning sober and alert, as if she'd piped away all weariness, all intoxication. It was Saturday, and apart from chores there was nothing to do. As soon as she found Thomas--maybe he'd drowned in the river--she'd gallop Puer out to the hilltop. Fatigue would hit her mid-morning, and he'd graze while she slept in the flowers, bees working round them.

* * *

She found Thomas in Ontario's stall, passed out in the hay.



He had nice clothes, this boy from St John's. They now had horseshit on them. He lay on his side with his mouth open, lightly snoring steam, causing a hay blossom to quiver before his parted lips. It looked as though Ontario may have tousled his hair once or twice out of curiosity, but the large, muscular horse now ignored the slender vagrant in his stall.

Hemlock leaned against the wall, took out the makings, and began to roll a cigarette.

``Thanks for looking after our guest,'' she said quietly to Ontario. It was enough to stir Thomas. He rolled onto his back and opened bleary eyes to meet her grinning ones. He sat up sharply, apparently skipping disorientation and proceeding directly to shame. Hemlock had already noticed a candour about Thomas that she liked. It bespoke courage, which when added to uselessness summed to a certain charm.

``It's morning,'' he observed.

There was that uselessness, though.

``Want a smoke.'' she asked him.

He considered, looked down at himself, seemed to assess his be-shitted condition and the scant prospect of starting the day afresh, shrugged and said: ``Sure, thanks.''

He rose, not wobbly, not even very slowly, just sheepishly. Hemlock lit the cigarette, dragged on it and passed it to him.

``There's a settee in the tack room,'' she told him. ``You could have slept there. Also the bench in the hall. It's hard. Teak. It's from a shipwreck.''

They shared the cigarette, leaning on the wall, both looking at Ontario.

``What shipwreck.'' Thomas asked.

``There's plaque on it with a poem: Please have a seat, this humble chair, Salvaged from the Heart of Autumn. Upon the sea long did she fare, Longer still she'll foul its bottom.''

``Huh,'' he said.

Hemlock looked at his clothes.

``You were lying in shit.''

``My shit,'' she heard him say.

``I don't know about that,'' she said, amused. ``Ontario's for sure.''

``My ship,'' he enunciated. ``My ship. The Heart of Autumn. She is my vessel.''

This caught her attention. The bench had been in the hall longer than Thomas could possibly have been alive.

``She is brand new,'' he continued. ``Homeport Hopedale.'' He dragged on the cigarette, and said with total confidence: ``She is there now.''

``Was it named after an older one.'' she asked.

``Must have been,'' he said with doubt in his voice. He looked at her. ``It's chilling to hear of her lost, even the idea.''

``Do you miss the sea.''

``Aye,'' he said. ``Just thinking about her, the Heart of Autumn, stirs me as the sight of forests or mountains never could. The ocean is my real kingdom, all its wonders. Now having seen these strange creatures here,'' he rubbed his eyes, ``I am amazed to consider what sentient mischief, what artistry or music might be observed from a ship-length blue whale. What pageants take place under the sea.''

Hemlock considered. She'd been on many voyages and had found them mostly boring. She'd slept mostly. Or drank. She preferred horseback and the open prairie.

``I should like to take you on a long patrol, Thomas,'' she said. ``If it's permitted. The Forest can be very beautiful.''

``It is.'' he said quickly. ``Please don't mistake my meaning. Already what I've seen is lovely. I had hoped Fury would be able to show me as much as was allowed.''

She smiled inwardly. It was Fury he wished to ride behind all those hundreds of miles.

``She is the best of us,'' said Hemlock, knowing she now claimed all his attention.

``Yes,'' he agreed. He shook his head: ``I mean-.''

``She is,'' Hemlock excused him. She looked deep into his dark Inuk eyes, seeing within each a flame burning for Fury. ``She is the kindest, most intelligent, most caring, capable, generous friend I've ever known.''

``Aye,'' he breathed.

Still holding his gaze, she grinned and gestured grandly with one arm: ``And this is her horse, Ontario.''

Thomas looked down, blushing. Hemlock giggled.

``Aye,'' he said. ``We've met.''

He looked at Ontario. ``I dreamt He was the Holy Spirit,'' he said matter-of-factly. ``I dreamt He held me to His breast.''

``I've known him a long time,'' Hemlock said. ``Finer, more fully fashioned for combat, more blended of coltish exuberance and stallion sagacity, no other horse, not even my Puer, could truly claim to be.''

Upon hearing his name denigrated, Puer nickered objection from his stall nearby.

``That's right, you heard me,'' Hemlock called to him, eliciting a proper whinny.

Thomas was looking at her boots.

``Why do you all wear such cruel spurs.'' he asked, then looked up, apparently remembering his blunder about the headdresses. She quickly suppressed her annoyance at his accusatory tone to relieve him of his anxiety.

``They love it,'' she told him, meaning it but knowing he'd take it as a joke.

``I pity them,'' he said, which made her annoyance surface again.

``I envy you your mortality, Thomas. The only ecstasy available to the undying is violence, as you must know.''

``I don't know,'' he said, and Hemlock decided that however much she might find to like in Thomas Shattering, he was, for some of the same reasons, a very bad diplomat.

She could meet him there.

``These vestments-.'' she tugged at the hem of her hide bodice ``--are not difficult to fashion, you know. Your great God could have made His own Son quite unimpalable had He wished to do so.''

Thomas stood rebuked.

It wasn't his fault, she thought. They sent him here like they were sending him to Antioch or China, where he would not find himself sharing a cigarette with one of God's daughters.

``Look,'' she said to him, taking her cigarette back, ``you can say what you want to me, Thomas. I think I get you. Just be careful around the others.''

He looked a bit shocked, but also relieved, maybe for finally being addressed clearly and directly. Fury's was an ordinarily warm hospitality, but her friend was not herself these days, it was clear.

``Hobby-.'' he started.

She cut him off: ``Even kind, gentle Fury.''

Thomas began to speak. She cut him off again.

``Your darling Fury slew a settler's pet the other morning, on patrol.''

``Darling.'' he tried to protest.

``Thomas, listen to me,'' she said, resisting the urge to grab his shoulders. ``You've got no secrets. I'm trying to help you.''

She watched him process.

``You uphold the law here, in the Forest,'' he said. ``It can't always be pleasant.''

``'Twere a child's puppy off its lead, I saw, and the next instant watched my best friend draw her bow and put an arrow through its head, fastening it to the road.''

Thomas winced, just as Hemlock suspected the hapless, sentimental, gentle envoy would.

``Clutching its paw,'' she continued, ``a wailing lass. Clutching the lass, in his dread, the child's father, his eyes pleading—-instead of hating, as mine would have—-that the act be somehow undone.''

``God,'' Thomas said.

``Fury is Red,'' she told him, relying on context to teach him the special meaning of that word. ``We all are Red, and it can be a difficult thing for your kind to fathom. How strange our pact! I can see why you are drawn to her, just as Newfoundland covets this Forest and the 'power of these trees'.'' She couldn't help a mocking tone with this phrase. The archers had heard such comic invocations for centuries and were well beyond being moved, flattered, or grateful for what had proven to be ignorant and irrelevant platitudes.

She persisted in a parody of flirtation, swelling her breast and moving toward Thomas. ``How you must crave this ancient vitality,'' she breathed.

``I'm sorry,'' he said, and she could tell he wasn't sure exactly for what he was apologising.

She handed the cigarette, now a mere butt, back to him. They both watched Ontario, who was showing the first signs of restlessness, flicking his tail and scratching his chin with a hind hoof.

``Did you really mistake him for a God.'' Hemlock asked Thomas. He was looking at the horse with an absurd reverence oddly familiar to her. She'd seen the look in Fury's eyes under the full Moon, dominion of their Mother, but not something appropriate to worship. There was a symmetry to these heresies, and, as was her talent, Hemlock sensed a connection obscured by some transform whose kernel she had not yet discovered.

She took the cigarette back from Thomas and extinguished it on the hide spur strap that passed under her heel.

``Fury stares at the Moon the way you're staring at her horse,'' she said to him. ``That's why she needs glasses.''



CHAPTER: The Satyr Visits Melody

A Park in St John's, Evening



It was Christmas Eve, and she was in there, digging. He rolled his wheelchair slowly along Newbury Street, alert for patches of ice, but his eyes scanned through a blur of passing wrought iron bars the shadows of bare trees and marble benches and balustrades in the park to his left. He heard her insistent shovel sink into rocky, frozen soil. She was tireless.

On his lap, milk, eggs, and rust-red flowers that didn't grow anywhere on Newfoundland. The Korean grocer was open every hour of every year, and he'd gone there to replenish the larder as Caroline nursed their light skinned baby in front of their cosy apartment's fireplace, surrounded by gifts and cards from her Cape Breton family, none of whom had ever visited. The flowers he'd gotten from the grocer's grandson, out back in the alley where deliveries were made.

The digging stopped, and he heard sobbing from within the park.

He rolled up to the park's iron door, seated between its marble columns, decorated with a pastoral bas relief that suffused him with irony, nausea, melancholy, disgust, and not one bit of its intended wonder. Black iron nymphs fed black iron grapes to black iron satyrs, the nymphs' faces all bearing an eagerness that he now recognised as maniacal, the open-mouthed smiles that distended their cherubic cheeks, the contortions of their physiques that cheated their nudity out to the viewer even as they performed their feeding duties, and the gleeful hunger in each wide, spherical metal eye all tracing their origins back to the prosaic imagination of a mediocre Albion blacksmith. The satyrs, for their part, were endowed with all the most impressive aspects of goat and man. Black iron fig leaves abounded to make the whole affair tasteful.

A fittingly absurd black iron skeleton key lived in a secret pocket under the seat of his wheelchair. He inserted it now, noting for the first time and without surprise the clitoral bump at the apex of the lozenge-shaped keyhole.

A plaque on the right hand column identified the artist. He sometimes thought of defacing it but each time decided the door itself was mockery enough.

Inside, an ice-resistant ramp had thoughtfully been installed over one of the smaller flanking marble flights from the semicircular forecourt up into the park proper, and he ascended as the sound of shovelling resumed. His wheels inches deep in undisturbed snow, he navigated the concentric oval pathways to an interior sector popular with wintering swallows, thick with ash trees and dark green bushes that yielded wild berries year-round.

In a small clearing he saw her, calf-deep in a hole, sinking her shovel, feeding a pile of dark earth beside her. Her long blonde hair swirled round in her motions, her dark, knee-length beaver coat open to reveal dirty white knees below a dirty white linen frock. She was muttering unintelligibly as she worked. Her dirty hands were pale blue and skeletal. He winced to see her stamping the back of the shovel's blade with a bare, frozen, dirty foot.

``Melody,'' he said.

She looked up with alarm. Her pale, dirty face was beautiful as ever, her large sky-blue eyes twin destroyers of men's resolve. Looking at him, she bit her lower lip which began to tremble. Tears welling in her eyes, she inhaled with a gasp.

``I'm almost done,'' she said pleadingly.

``It's okay,'' he reassured her immediately, rolling forward. ``Take your time.''

They had repeated this salutation thousands of times, always the same. What would follow varied little. He recognised the place she was digging as one she'd dug before. Around her under the snow were many an erstwhile hole, refilled by her and re-innervated by roots and worms and ants, reintegrated into the bulk and plane of the park, the turf in that place bearing no scar from the avulsion caused by her questing spade. The holes had been big and small. They'd overlapped. There was by now, he reckoned, no part of the park's lawn that hadn't been a hole.

``Any luck.'' he asked.

``Not yet,'' she said forlornly. ``But I'm not giving up.''

``Of course not,'' he said.

She stepped out of the hole, and he looked at her pitiable feet.

``I gave you boots,'' he said.

``I can't wear those,'' she said, wiping tears and sniffling. She sat down crosslegged in the snow and looked up at him pathetically, shaking her head. ``I just can't.''

``Well at least you're wearing the coat,'' he said.

She hmm'd, then looked down and began muttering again. Strings of numbers.

``Melody...'' he said.

She looked up at him abruptly. ``I'm going to find them.'' she cried, startling some swallows to flight from the berry bushes.

``Of course you will,'' he said, unable to confront the madness in her eyes with anything other than cowardly affirmation.

He held the flowers out to her. She smiled wanly and took them.

``Thank you,'' she said. She began to eat them.

Locking the gate to the park, he heard her shovelling resume. He could not go directly home to Caroline and the baby. On Christmas Eve the bar at the Hourglass would be quiet but would be serving. He went there. Constantin, the bartender, put his milk and eggs in the refrigerator behind the bar and brought a brandy to his small table by the window. His view of the intersection of Newbury Street and Argyle Avenue, their lamps and decorations, .

``Thank you, Connie,'' he said.

``Sure thing, Professor,'' the young man replied. ``Merry Christmas.''

Alone with his drink, he swirled the brandy and watched the amber glaze thin and separate into legs on the inside curvature of the snifter.

Melody had been in the park for a century, digging, searching for items she'd never find. They had been destroyed, but he feared that to tell her so was to destroy her also. The ache in his stumps, his tailbone, and his skull called out for the brandy, and he drank it in one.

``Another, Professor.''

He nodded assent.

A wintry breeze hit him as the pub door opened. A cheerful group of students came in, out of uniform, some with festive hats. Kimberly was among them. As she saw him, he watched with satisfaction as her face change from that of a carefree young person to that of a serious scholar and potential operative. There was nothing false in Kim, but she had multiple modes. She would need them. Among her companions, he quickly observed realisations, variably crestfallen, that they had lost her company to something more interesting. ``I'll be right back,'' he heard her say to them. ``Sure,'' one young black woman replied. ``Bye Kim.''

She sat down across from him, setting her rucksack at her feet.

``Merry Christmas, Sir,'' she said with a grin. In the three months she'd worked for him, she had learned much that freighted such a greeting.

``Yes, Merry Christmas,'' he replied.

She tilted her head and looked at him.

``What's wrong, Professor.'' she asked.

Connie dropped the second brandy.

``Same, please,'' Kim said to the barman. Her concerned gaze returned. ``Professor.''

``I have something for you,'' he said.

``So do I.'' she replied gleefully. She quickly unstrapped her rucksack and produced a red and gold gift wrapped box. She placed it triumphantly on the table before him.

He reached under his seat into the same pocket where the skeleton key was secreted. He gently placed the brown envelope bearing the King's seal in front of her. She knew what it was. Actually, maybe not. It was likely to exceed her expectations.

``Are these orders.'' she asked, her eyebrows high but steady.

``They are,'' he said. He was not certain of the contents of the message, but he knew at least one aspect of it. He knew he was breaking the law by giving her the envelope here--he was breaking the law by taking it off the base. But he was trusted in some things, and it was time to trust her in the same way. She'd been vetted thoroughly, if hastily, her father having insisted that no segment of the process be waved. ``Sy,'' Rusty Jack, Fleet Admiral and Head of Navy, had said in the second of two meetings in their lifetimes, ``am I doing the right thing.''

``I'll look after her,'' he'd sworn.

Ironically, part of looking after her was to make her complicit in such transgressions as served, and were indulged by leadership in, their community.

``Open it,'' he said.

``Here.''

He sipped his second brandy. ``Sure.'' He smiled.

The relevant code would be at the top right of the first page, and he knew she would look there first. He watched her pale eyes dart, read the code, read it again, then look up over the edge of the paper into his.

``Are you fucking serious.'' she said.

He made no reply, and she returned to the letter. One by one she removed her leather gloves with her teeth so as not to interrupt her reading, and when she'd read the last word of the last page, she ran a finger over the King's signature, feeling the grooves made by his pen.

``Who is the other.'' she asked. ``The lead.''

``Lieutenant Commander Asa Roos.'' She knew him. Her vetting had revealed that.

``Yes, we served together on the Silhouette.''

He met eyes with the black woman in her group of friends at the end of the bar. She smiled at him, and he let her know with the shape of his own smile that they had indeed lost Kim for the evening, and that he was sorry. She raised her glass. He nodded. Kim was absorbed in re-reading.

An hour later the bar was noisier as those bound for Midnight Mass prepared themselves for the experience. He was on his fourth brandy, she on her third. Cigarette smoke was thick in the air. Christmas carols played on the gramophone.

``I was four when my parents died,'' Kim was saying. ``My ittu had never been to the Island. He'd never left Labrador. He came to St Johns--no happy adventure for him--collected me, and would forever have kept me with him, hunting the Big Land.'' She drank. ``But I turned out to be ever so clever, so he sent me to Hopedale, note in hand for a CPO with whom he had tanned leather, canned fish, panned for gold, Heaven knows, but he owed my ittu a favour, and Admiral Jack owed him. And so it goes, I became Kimberly Jack.''

He knew she knew he'd known all that.

He looked down at the gift in front of him. It had sat while he had suppressed her most professional, but least appropriate to the setting, inquiries about her orders. He had urged her instead to focus on what their successful execution meant for her career. Brandy had helped move the conversation into the personal.

``Should I open this.'' he asked her.

``I opened mine.'' She grinned.

He removed the wrapping to find a carved maple box. Opening the lid he discovered a copper bell on a red silk lanyard. He looked up at her. Her grin widened.

They sat in silence for a moment.

``Why were you out tonight.'' she asked him.

``Milk,'' he said. ``Eggs.''

She turned her head and eyed him askance. ``Is Caroline in Cape Breton.'' she asked.

``No, she's home,'' he said. ``She's here,'' he clarified. ``She's nursing. It exhausts her. Dimasha is there.'' Their housemaid, who was not a Christian. ``Are you going to Mass.''

She nodded. ``Yes. Maybe. I don't know, it's hard to think about that stuff now.''

He knew that by ``stuf.'' she meant not Christ, but rather the Newfy Church's naïveté about Him. She was on her way to meeting folks who might have known the Man Personally.

``Dad is in Lisbon, as you know,'' she said. ``Christmas there is wonderful.''

He nodded. Indeed it was.

She was staring at him again. They'd worked together very closely for three months now. Their talk seldom got personal, but the nature of the material they studied was undeniably philosophical, sometimes penetratingly so. It was difficult to conceal one's own traumas when Ekkorbok had apparently been designed to attach to them at every verse. Her empathy for what Lieutenant Shattering must be going through had been occasionally profound, even moving. He hadn't feared for young Tom, knowing him now as old Tom, admittedly broken, admittedly lost, but with no regrets save one.

He looked at the bell she'd gifted him.

``It is not a very well-kept secret,'' he said.

She smiled. ``I know. I mean, most people think you are from the Five Islands.''

``Not an unreasonable theory,'' he remarked.

``You're a veteran,'' she probed. Another common idea.

He shook his head.

She levelled her gaze at him. ``But you are from Akrotiri,'' she said in a low voice.

He nodded.

She hesitated, then asked gently: ``Were you maimed in the-.''

``I had them cut off,'' he said.

She sat back, her face pale, a contrite expression immediately conquering her brow.

He hadn't meant to be cruel.

``Here in St John's,'' he continued. He reached for her tobacco, which sat on the table, and began rolling a cigarette. ``There's a doctor on Dundee who does it for gold.'' He handed her the cigarette and began rolling another for himself.

If he hadn't just seen Melody, if the Crown hadn't just put its own faith in this young officer before him, and maybe if it had not have been Christmastime, with its cheer and the brandies, he might not have allowed himself to take any comfort in Kim's compassion. She admired him, and now he admired her. This unfamiliar commutation with a student inclined him to show her the cracks in the edifice of the institution he and Ted had become, lest she discover them herself.

``I will anticipate your question: I never met one of his archers. But as a refugee I heard stories, from Hittites, from Mycenaeans, even from Babylonians. Ekkor wasn't as promiscuous as He would become half a millennium later, but already one got the sense that no ideology but Ekkor's will commanded their hearts, and that his will was for sale. Whatever quantity of my own blood that remained Nubian was stirred by a kind of imagined affinity. Even then I suppose I recognised a purpose all its own in war. More purpose than...'' He looked at her meaningfully, allowing her to finish the idea with her own literary understanding of satyrine life, more or less accurate.

``I see.'' she said.

``Yes, so-.'' he started.

``Wait,'' Kim cut him off, waving her cigarette in a motion that left an S of smoke slowly ascending between them. ``So you're, like, four thousand years old.''

He chuckled. ``I feel older,'' he said.

He told her about Melody, about whose arrival the surgeon had warned, and whose search for his shorn parts would continue as long as reality itself continued.

``But I wanted a family,'' he said. ``This was the only way.''

``What if she finds them.'' Kim asked.

He took a drag of his cigarette then crushed it out in the green glass ashtray.

``She never will,'' he said.

Outside a light snow began.

CHAPTER: Christoffel Visits Oca \& Ape

A Fairy Workshop in the Forest



``Cara Christoffel,'' Arthur wrote, ``God shares with noble gases the property of expanding to fill a volume and push out contaminants. For man, the volume in question is his capacity for a priori knowledge. I am horrified to discover that in having rejected the unreasonable--you, Christoffel, cannot be reasoned--I was as Christian as any of my fellows, unconsciously reserving that faith-space for the Holy Spirit.''

Toffy rolled her eyes and smiled. Arthur always spent his first paragraph coming to terms with her very existence.

She sat astride red and black Cheops in a light snowfall outside Pieces of the Moon, Oca and Ape's Forest workshop. The sign on the door read ``back in one hou.'' in the bee fairy's sweet penmanship.

``If you hear an echo when you speak to me,'' his letter continued, ``it is because you are all alone in that cavernous space, as nothing else on this Earth has given me cause for any faith whatever.''

She blushed at this, but she also recognised a guilt trip when she saw one. As happy as he was to receive her letters with their tales of quotidian Forest life, and as sanguine and generous his replies, his useless longing to visit was always just below the surface. It was something she could not effectuate, even if she wanted to. She had teased him that he might enter via the extreme of his genius, but that none of those men whose genius he rated over his own, not even Petrarch, had been spotted here, as far as she knew.

She read on.

``Let me proceed directly to reactions to the concerns of your last letter, while needlessly reminding you that I have never myself been able to maintain consistently pleasant relations with anyone for any length of time, save via correspondences such as we enjoy. I'll quickly add, just as needlessly: yours are my favourite.

``Your sister-in-arms, Fury--whom you say you have known and loved for more years than has existed Italy, or Germany, or any other country I know--has begun to act strangely and to isolate herself from you and the other two members of your foursome, Hobby and Hemlock. You intimated this in your Summer letter, but your Autumn letter was full of despair, where you wondered if the arrival of a naval envoy--from a place you felt you could not share--called Thomas--how unaccountably fortunate a young man--had somehow exacerbated the trend you'd already marked in Fury.

``Your engraving of the hare's song--and I agree, he has gotten to the heart of the matter--is as lovely and heartbreaking an arrangement of ink on paper as ever has been achieved, and the bleeding caused by eel oil and your tears as necessary to the design as those delicate strokes unaffected. I can hear your balalaika in my mind, and I would seek out a Berliner musician to play your part if I believed none would suffer dreadfully by comparison to your prodigious talent. To hear you sing what he has written for you to sing, seeming to look into your heart-- making me as envious of that strange beast as I am of the visitor Thomas--would be a joy beyond measure, even as the lyric would require I share in your grief. In tristitia hilaris, in hilaritate tristis.

``With the familiar caveat that as (a) a woman and (b) a soldier you occupy a union of two categories of person to whom I am traditionally least able to relate, allow me to offer, as you requested, the following interpretations.''

Snow had fallen on the first page as she read, blurring Arthur's ink in places, just as tears had blurred her own. As she turned to his second page, she leaned forward in her saddle and tipped her head forward to shield the paper with her headdress. Cheops thought she wanted him to move, so he did.

``No,'' she said, and he stopped.

``'Pulled up lame, nothing feels the same, are we falling apart?' He will have known it would affect you, this opening image of an injury that can prove minor and on the other hoof can prove a catastrophe. As you know I watched my father euthanise more than one horse. But already we have a picture in our minds of an errant one of a foursome. I continue to be impressed with his insightful poetry.

``'Once in rhythm together, copper to feather, a four-chambered heart.' You may remember that it was this odd expression, 'copper-to-feather' that featured in our very first conversation in Pisa. I thought it was an aphorism I'd missed in my diligent study of English, and of course I learned that no one else had heard it either, but our fellow party-goers were too shy to ask--you know I am being kind, as we agree their pretence was to blame. From copper arrowhead through black bone shaft to white swan fletching, the entire length of an arrow, or anything. In German we say x. They French say y. My favourite was the Portuguese: z. But I conclude there is no expression as nuanced, and I should like to use it in my daily life were it not certain to elicit odd looks.

``But I don't imagine you need my help at all with the opening couplet. So let us move on:

``'It is not our way to be so melancholy.' You have told me many times about your happiness in the Forest; how can I be expected not to long to visit you there? And you have confounded my own limited experience of war with what cheer you conduct yourself in your terrible work, for example in the blinding of prisoners with your dagger, though I do understand and accept your philosophy in that anecdote.

``'What does Herr Baudelaire know? Beauty, it can be jolly!' I don't know any Baudelaire, but as we have worked out, you are as many as one and a half centuries displaced into my future, so I shall be on the lookout for him and may be lucky enough yet to encounter this philosopher, whom I detect from the hare's epigram shares my affection for Bruno. Had your long-eared friend known me and heard our many arguments on this very point, he might well have written 'What does Herr Schopenhauer know?' Alas my surname is not nearly so yodel-able.

``I think your friend mocks you here, as I have--lovingly!--also done, and here I make my boldest attack on this, our stagnant front: you, violent Christoffel, are your legion's covert pacifist! Your conclusion that you should be happy in war follows reason, but haven't the last few years been lovely without it? You have written that you could stay in the Forest with Fury and Hobby and Hemlock forever, singing with those animals--maybe eventually arranging to host me--performing your patrols, as tiresome as you claim to find them, yet always but a line or two removed from exhortations of the Forest's beauty, or bound with the tear-stained transcription of a duet for mandolin and horn you and Hobby discovered together in the voice of the leaf-tousling breeze on a mountain overlook under the yellow glow of a Badger Moon. Must a blood-red gesso of war's horrors undertone such dear illustration to imbue it with the depth of painterly fine art?

``So: you give up being a warrior, and I will give up being morose.

``'How grief doth spread like the stench of the dead. I never stopped to wonder.' Now this is unfair! I have come to know your tender nature, and how essential it is to a loyalty with which it is occasionally at odds. Again, I think he mocks you gently. Once, in Siena, I asked you if you didn't lament your typical exclusion from victory celebrations, and you replied to me: 'I am happy we leave even before they raise the flag. I should not want to wallow with the war-widows amidst the browning and crusting over of the bright slaughter.' Perhaps the hare would mock me, too, for the naïveté I demonstrate in detecting pity in that ghastly sentiment, yet I do.''

Christoffel let her hands gripping the letter fall to her lap and lifted her face to look up at the black, naked branches above her and the grey sky above them. Snowflakes settled on and cooled her cheeks, which were flushed with Arthur's flattery and affection. But the tears that filled her eyes were not for joy of being loved by her secret friend, nor were they for despair over the miseries of war--Arthur was just wrong about that, or maybe he thought he was being nice--they were for Fury. Without intending to, Arthur was describing not Christoffel's furtive good soul, but the salient good soul of her friend, a soul upon which she relied to sustain her own tenuous connection to reality. In Italy, Arthur had nicknamed Christoffel l'Eterodossa, The Heterodox. But Fury was The Paradox, which was just fine with Christoffel, because her broken compass, all sluggish in the viscous fusion of her hateful parents' royal bloodlines, could never orient on any coordinate in space that did not possess at least one non-zero imaginary component.

When she looked down to see Ape's dear, concerned Chinese face looking up at her, she laughed with relief.

``Is that the latest letter.'' Ape asked.

``Hi Ape,'' Toffy said to the bee fairy, in whose presence she always felt at once more grown up and more looked after--another paradox. ``Yes,'' she said, folding the letter roughly and shoving it into her skirt pocket. ``It's boring.''

Ape was carrying a large bundle of hides on her back, her bee wings crushed beneath it.

``Here let me help you.'' cried Christoffel, throwing her leg over Cheops' neck and sliding out of her saddle into the calf-deep snow. She lifted the heavy pack off little Ape's back.

``Thanks,'' said Ape. ``It's deer.''

``Wonderful.'' said Christoffel, looking down at the pack. ``We could have brought you another. We traded it for booze at the Red Lion. We have meat and eels for you, for honey and candles, and we need some copper-work.''

``You're out with Hobby.'' asked Ape, exercising her wings with a grimace.

``Hemlock actually,'' said Christoffel. ``She's a couple hours behind me.'' She pushed her nose into the deer skins. Bucks from the far north, beyond His Mountain. Now she saw the red highlights on the soft black fur. ``Where did you get these.'' she asked.

Ape smiled skeptically. ``I'll let Oca tell you that story,'' she said, shaking snow out of her fine black hair.

Inside, Ape lit candles. It was not terribly cold yet, but sunset--and another storm, Christoffel suspected--approached. While Ape went to the toilet off the kitchen, Christoffel prepared a fire in the workshop's enormous stove.

``Oca went to the Red Lion,'' Ape called from the toilet. ``We are coming out to you tomorrow.'' The goose fairy would be arranging a wagon with settlers in the hamlet by the inn.

``You could ride with us,'' Christoffel said as Ape emerged with a kettle and cups.

``Light that, I'll make hot chocolate,'' Ape said.

Christoffel lit the wood burner and settled into the pillows on the window seat by the front door. Plants hung above her in intricate macrame, Ape's work. She looked out at Cheops, reminding herself to throw a blanket over him.

``Does he want hay.'' Ape asked.

``No, we just ate,'' Christoffel said. ``The falls by that little fork aren't frozen over yet. That's where I caught the eels.'' The eels and deer meat sat outside in the snow. No scavengers came near Oca and Ape's workshop.

``That's going to take a bit,'' Ape said of the stove, sitting to face Christoffel in the window seat. ``We thought we'd leave today, but Oca wanted to try to finish Hobby's horn.'' When Christoffel gave her a puzzled look, she added: ``A new one. How is your balalaika doing.''

``Perfect,'' Christoffel said, pointing a thumb at where the instrument sat in its case with her pack by the door. ``I didn't know Hobby wanted a new horn.''

Ape shrugged.

Christoffel enjoyed talking to Ape, and the gentle bee fairy seemed to enjoy listening to her. There was always a moment of recognition, when they both knew Ape would shut up and Christoffel would pour forth. It had arrived.

``This patrol went longer than I expected. I don't mind. Hemlock wanted to go up to Waccabuc. We camped there for a couple days. It's very beautiful. So many cows, and the milk is very good. When it's colder I'll bring you some. The woods are very thick where it hasn't been cleared, it can be hard riding if you leave the trails. There are deer paths Puer and Cheops can only just navigate.''

Ape looked down at Christoffel's boots, which took abuse when pushing through thick woods.

``No, they're fine.''

But Ape reached and hauled Christoffel's feet up onto her lap, mindful of her spurs, and began combing the thick, shaggy fur of her boots with her fingers. Christoffel leaned back on the pillows. She feared she'd be asleep before she could drink any hot chocolate.

``Oh, one of your pillows went into the fire,'' she said, her eyes closing.

Ape chuckled.

``Hobby has been doing maintenance on the lodge. I would've thought she'd want a new axe before a horn. She's like a one-man sawmill. I think it's to do with Thomas. She thinks if she keeps busy with the barracks, she won't have to talk to him. I don't know why she dislikes him; he's very nice. Do you know that I can do an entire patrol with Hobby, without her saying a single word. I know I talk a lot. I look in her eyes, and I know she loves me. I miss fighting alongside her. You should see it. With that axe. I know you hate war. You make such lovely weapons though.''

Christoffel's bow was Ape's handiwork, a heartwood double-f whose curves Christoffel could have moulded by her hands' memory. She longed to run her palms along its length, but now it hung on the rack with Oca's hunting bow across the room, and Christoffel was drifting off. Ape's craftsman fingers may as well have been combing through the hair on her calves.

``Fury meets Thomas every day for lunch. I honestly don't know what he does other than that. He reads the notes I made, the little history. He borrowed some volumes of Ekkorbok; I doubt he understands it. He comes to the hoot. He says he can have electric instruments sent from St John's. Have you ever heard those? I think they have them in Vedauwoo. Copper cells.'' She yawned deeply. ``The stag...''

``Toffy,'' Ape said, gently extracting her legs from beneath Christoffel's boots, ``before you fall asleep, I'm just going to make the chocolate.''

``Oh yes please,'' breathed Christoffel. ``Thank you Ape. It's lovely being here.'' Through half-closed lids she watched Ape's little bare feet as the fairy puttered. Ape's own deerskin boots sat in a puddle by the front door. Looking at the fairy's toes on the cold stone floor of the workshop, Christoffel felt keenly jealous. The closest she ever came to being barefoot was when she swam and could feel the cold water surrounding her feet inside her boots. Head, waist, and feet, she'd worn His red hide, all her life.

``Did you see Fury in the Autumn.'' she asked Ape.

``No.'' Ape brought the cups of chocolate over, hooking a small wooden stool with a foot to drag it into place by the window seat.

``Thank you,'' said Christoffel. She sipped the cocoa, which was sublimely sweet with honey, and placed the cup down. ``She was up here I think,'' she continued. ``She likes to solo these days. I like going out with Hemlock. Her copper whistle. Oh, her piping. Autumn wasn't Autumn this year. Everyone seems out of sorts. I'm sure Thomas feels unwelcome. Fury is-.''

Christoffel began to cry. Ape put her own cup down and took Christoffel's hands into her own.

``Ape, there is something wrong with Fury. It makes me sick to my stomach when I think about it. She is so distant and sad. That's it, she is just plain sad, and she has never been sad. She's not always laughing and joking like Hemlock, and she can be just as serious as Hobby is, but she has never been sad.

``I have tried talking to her, but you know me, I say confusing things. I'm always confused. But it never mattered before, I could be an idiot, because Hobby led us where we needed to go, and Hemlock kept us cheerful, and Fury was-.''

She sobbed deeply, discovering an outlet that at least felt better than nausea.

``Fury is our soul.'' she cried. ``And if she is in despair, then our soul is in despair, and I know, I can see His House from here, but nothing has ever made me feel so far away from Him as being frightened for Fury. Panthers!, Ape, Panthers.''

She reached out, and Ape took her in her arms.

The patrol with Hemlock had been miserable, on top of what had really seemed like a lost Autumn. She knew that Fury was on both their minds, but they hadn't spoken about her once in the three weeks on the trail. They'd made music, so as not to talk, but there had been something sinister mixed into the harmony. Hemlock had her talent for finding secret passages, but Christoffel had her own talent for detecting demons, and there had been more than usual, mostly tiny, hideously beautiful, hiding in the reeds near streams, accomplishing their inscrutable chthonic tasks, unsettling the fishes. Why did He put up with them?

She'd carried the letter from Arthur the entire patrol, never finding the right moment to read it, hoping his reaction to the hare's song would provide some answers. But he was getting it all wrong, faithfully imagining that he saw in Christoffel what she knew properly to be housed in Fury when she was healthy, which, oh God on the Mountain, Christoffel was certain Fury was not.

``She's sick.'' she cried out, and Ape cradled her in her lap.

``There, there,'' said the bee fairy, wiping aside strands of Christoffel's hair now glued by tears to her cheek.

``And Hemlock knows it, and Hobby knows it, and I can see Hobby working it out in her head whether she needs to report it. But I know, Ape,'' she sat up and looked intently into Ape's dark eyes, ``I know there is no tremble of hand, no, nor gust of wind can steer Fury's arrow from its mark. Where she aims--from God's first day to God's last--follow ever copper, shaft, and feather forthwith, piercing what would be pierced and what would not, fastening to her will His foe's demise altogether, arcing his blood before his eyes even before he knows he's shot.''

``Does that matter anymore.'' Oca asked. That difficult-to-name part of Christoffel that kept her alive for centuries had heard the goose fairy come in, but had elected, for the moment, to cede centre stage to Christoffel's easy-to-name self-indulgence.

As taken aback as she was, Christoffel knew what the goose fairy meant, and she let it show in her smile, her sniffle, her exaggerated, self-mocking wiping away of tears. They hadn't been to war in years, and despite Arthur's exhortations that she enjoy the peace, idleness was making all of them crazy, not just Fury. They worked on the lodge. They performed these useless patrols. They sang with the animals. They smoked a lot of pot.

``Somewhere,'' Oca said, setting her heavy backpack down beside Ape's drying boots, ``right now, a security group is pitching its services to a newly wealthy individual who, despite his success can neither,'' she stuck out her thumb, ``rise to his imagined level of importance, nor,'' she stuck out her forefinger, ``conceive of a more creative way to compete.'' Her thumb mimed a pistol's hammer striking repeatedly. ``War will come, Christoffel.''

Oca took off her hide overcoat and trousers to reveal the white and gold summer dress she wore year round. She spread her black, white, and brown goose wings magnificently for a moment to stretch them, the large primary flight feathers at the tips flexing open like fingers, and Christoffel sighed at the black fairy's beauty. Oca's spherical afro, large as an archer's headdress, was frosted with snow which the tall fairy now shook off onto the floor. The fire was strong now, and the flakes quickly melted on the warm stone. She kicked off her boots, joining Ape in barefooted luxury, and her white soles left dark snowmelt footprints as she padded across the workshop to the kitchen. Christoffel's own feet were sweaty now, a misery to which she was, sadly, well accustomed.

Oca emerged with a copper cup and helped herself to the hot chocolate. Christoffel and Ape picked up their own cups, and Oca sat on the footstool. The sun was setting on the other side of the workshop, its orange glow spilling from the kitchen into the workshop. Meanwhile the Forest outside the window seat was already dark.

Oca and Ape exchanged glances, and Christoffel saw the information passing between the pairs of dark eyes, sequences of obscure fairy symbols just discernible in the darkening workshop.

Oca looked at Christoffel and leaned forward.

``Tell me,'' she said.

* * *

``Thomas, as you know, has been here since the end of Summer. We all know he's in love with Fury, that he has been since the day he arrived. We tease her about it. She ignores us. He stays at the Chanticleer, but he meets her every day for lunch, sometimes in Three Nations, sometimes at the lodge. Sometimes they would picnic, before the snow came. It's charitable duty for Fury; for Thomas, it's his whole world. Hobby jokes we'll never be rid of him, and you know her face: in faith I say she is joking. He, Thomas, finds reasons to visit the lodge every weekend. It's fine. Hemlock and I like him. We take him fishing, riding, hunting--he's a better bowman than you'd expect--he helps us with chores round the lodge and with work for the settlers. They seem to like him, the settlers. I think the little maids at the Chanticleer fancy him. He's handsome.

``He brought arrowheads from Newfoundland and Labrador. Oca, I know you'll be eager to see them, but he's only been authorised to show them to us, and Hobby hasn't decided whether we should have a demonstration. As eager as she seems to be rid of him, she stalls on permitting him to carry out certain elements of his mission. Hemlock offered to take him on a long patrol--I'm not sure I'd enjoy that--but again, Hobby says she has to think about it. He thinks she's awaiting approval, but that's her sort of lie by omission: she doesn't need to contact His Central Force about this. We have our orders, and they're as ambiguous as ever. They'd relieve her if she couldn't make decisions, but, it's just that, I don't know...

``Everybody is being weird! You guys haven't been round since last Winter, since Fury came back from up North. Hobby has gone from virtually silent to completely silent. Fury says odd things and spends a lot of time alone. She and Hemlock were once inseparable. Hemlock is now stoned all day, every day, and I don't blame her: there is nothing to do!

``Of course you're right, Oca. Of course there will be war, and those little envelopes will arrive, and we'll be off. But I don't know: maybe we won't. He has infinite daughters to do his bidding, and as ardent as we are, there must be, however tightly packed we are round Him in faith, a kind of root-mean-square orbital shell beyond which all are automatically, mathematically, apostate. I mean, Hemlock still reads Ekkorbok every day, and it's hard to imagine anyone more pious than Hobby, or a more devoted daughter than Fury. You see me sitting here in steadfast sartorial allegiance, all hidebound and phylactery'd up while you both relax and wiggle your toes by the fire, but maybe it's not enough. Maybe such long separation from the legion, or singing with woodland creatures has diluted our ardour. Maybe next to our sisters-in-arms we are fallen from His Grace. Look where we live! You cannot get farther from His House and still be in the Forest.

``Maybe Fury's moods, Hemlock's zaniness, Hobby's recalcitrance, my own--do you know what I was reading outside, Ape? This. This is a letter from my friend in Italy. Well, he's in Germany now, but I met him in Italy. I've been corresponding with him. Do you know how illegal this is? I hide his letters in volumes of Ekkorbok. They're all over the goddamned house!

``It used to be nostalgia. Or I liked him flirting with me, like the fox does, or Spring. Now I just write about Fury, about the change in her, and how unapproachable she has become, even as she is still there to hug, or sing and play with, or ride with. I'm asking a philosopher for his diagnosis, because my instinct tells me she is beyond the explanations of other arts.

``I'm supposed to be the loony one! 'Daffy Toffy,' You know?

``It is dread. Dread and grief. If I had stopped to think about it, even once, in a hundred thousand hours on the battlefield, where it surrounded me, I should have concluded that were such forces to take hold of an archer's soul, particularly an archer like Fury, good, good, good, deeply good Fury, that soul would devour light like an inverse sun. Because she'd hold it forever at her centre, and compress it, and unwittingly nurture it with the radially inward energy of her effort to forestall its contagion.

``But what has Fury to mourn? Not the enemy, nor immortal archers, nor any men, I can tell you. I suppose Fury and Hemlock shed a tear for the enemy commander at Teutoburg, but those were unusual circumstances, and he was a special man. We were bred for war, not just to be great bowmen and horsemen, but for a temperament aloof from such confounding passions. That's why Thomas calls us 'fairies' sometimes, though for him it is a complaint about Fury's indifference to him specifically. One cannot call us indifferent to laconic Death Himself, for He is a cousin of ours as sure as is bonny Spring or avuncular Circe, absent as she's been.

``I would mourn a sister fallen in battle, were that possible. And though we haven't seen any of our fellow archers--apart from we four--in many years, Fury cannot grieve for their absence or the remoteness of our duty station, knowing that we are everlasting and none have ever fallen, for we would have heard. I have read the volume of Ekkorbok that addresses the demise of an archer, because His comprehensive Bible addresses everything, even the impossible. Such an unthinkable event triggers a message to every address under HCF.

``We've received a single message in half a decade: Newfy coming, staying for one year. Our standing orders, as you know, is to make entries in logbooks hidden in tree trunks and under stones.

``Anything else is up to Hobby.

``I resist discussing Fury with Hobbs. I don't want to tip the scales if she's weighing contacting...His...''

Oca and Ape watched as Christoffel began to sob again. She'd felt Ape's hand continually brushing the toe of her boot as she had made her little speech. Ape never cried, but twin wet lines ran down Oca's black cheeks into the bright white, throat band that cradled her face like a chinstrap. Christoffel felt her own chin itchy and soaking in salt tears that collected in her own actual chinstrap, sharing in the misery of her sweaty feet and scalp.

She thought she could test the archer death-message system by removing her boots and headdress right here. If she was quick enough, she could strip and die naked here between Oca and Ape.

Christoffel wailed at this thought that brought Fury's face to mind in sharp and terrifying relief.

``Oh Toffy, Toffy.'' cried Oca, taking Christoffel into her long arms.

``She's got a fever,'' Oca said to Ape, who immediately rose and hurriedly crossed the workshop to the kitchen.

Snot flowed freely from Christoffel's nose onto Oca's bare black shoulder.

``I wanna go for a swim.'' Christoffel bawled.



CHAPTER: Hemlock Rides to Oca \& Ape's

On the Road to a Fairy Workshop, Midnight



The road to Oca and Ape's was dark and secret even on a bright day. Hemlock imagined it was a sales gimmick, that only a ``dark and secret roa.'' might lead to a fairy workshop of any repute. In the snowstorm it was blackness. Both she and Puer knew the way, though, and it was with a relaxed hand she held the reins draped over the deer carcass lying across her saddle horn. She'd killed this second one, a doe, after Toffy had left their camp, thinking to surprise Oca and Ape with the gift. The skinned cuts of the bigger buck were packed onto Puer's rump behind her.

Puer was good in snow and mud. So was Ontario. Cheops and Mercury were better on ice and rock. The temperature had dropped sharply, but the wind was gentle. Though abundant, the snowflakes were tiny and dry and crystalline, and the layer of powder Puer's belly now skimmed along offered only minimal resistance to his advancing legs. Hemlock reached down to scoop a handful and filled her mouth with snow, catching the note of His Flower amongst the minerals in the ice water. This weather had hit Vedauwoo first.

She allowed herself to drift along in the darkness, rocked gently by Puer's smooth walk, feeling the snow crystals melt on her forearms. It was midnight, but there was no rush. She and Toffy were ahead of schedule, having ridden hard from near Waccabuc down to the fork. Their path along the river had taken them tantalisingly close to the grove where Fury had first met the animals, where she'd later brought Hemlock to join them, and oddly sheepish as Fury had been, there had been an excitement in her friend's eyes that had in turn excited Hemlock herself.

These days Fury's eyes held bewilderment and despair, and though Hemlock knew she'd been the first to notice, it was clear Toffy now saw it too. Hobby never missed a thing, though a remark on any particular observation was as unlikely as any other utterance from the towering statue of an archer. Hemlock smiled, thinking on Hobby's ice blue eyes, always bisected by the uncannily regular line of her blonde bangs, always steady, and always--Hemlock suspected--walling off like ancient glaciers a vast, convecting cauldron of emotion. Hobby had been sent away to be trained in Babylon, before there even was a Babylon, and who could know what turmoil such training could engender in a woman's soul, or what galactic palisades she would need to erect to contain it. Momentarily eclipsing her concern for Fury, Hemlock's love for Hobby swelled in her. Thankless job, being in charge of this little cadre, and unlikely to yield distinction. Hemlock knew the four of them were among His best, and she had always sensed that Fury in particular had some outsized measure of His love, that Fury would be provided with companions condign to her special status, even if Hemlock could not exactly define that status. But this long duty was a vacuum of glory, and these patrols, while often pleasant, were making eternity pass more slowly. If Hobby took any satisfaction in her reports to HCF, it was such as one takes in a mantra.

Which brought Hemlock's thoughts back to Toffy's remark by the campfire. ``HCF could send a vet.'' They'd been talking about a colicky spell Puer had gone through near Waccabuc, which the local beer had sorted out.

The beer had sorted Hemlock and Toffy out, too, and there was a Waccabuc farming family who now had a tale to tell of two archers baying at the Badger Moon from the farm's barn rooftop before being suddenly carried off it by thirty tons of sliding snow. The family had all run out with shovels to help them, but the archers had tumbled free of the avalanche as it had piled up against a sturdy stockade fence, and Hemlock and Christoffel had been found rolling in pig shit, laughing idiotically, being nuzzled eagerly by shoats who'd seemed happy to have been disturbed.

Hemlock had seen the farm boy's eyes fix and had looked down to discover her skirt up, her muck-stained thighs and hide quiver-straps a shocking privilege for the lad's stare. The mother had quickly put a hand over her son's eyes and smiled gently at Hemlock. Hemlock had adjusted herself and mouthed a voiceless ``sorr.'' at the woman. The woman had shrugged and pointed across the pigsty to a frozen duckpond. Hemlock had nodded thanks. The family had returned to their house, glancing with polite caution over their shoulders. ``Thank you.'' Hemlock had called after them. ``Sorry.'' Toffy had added.

Steaming in the night air, still drunk, still drinking, at their campfire in the nearby woods after having broken through an inch of ice on the duckpond to swim themselves clean, Hemlock had said to Toffy: ``That will define his tastes for life.'' Toffy had spit out her beer at the joke.

Sleep eventually had asked to join them round their campfire, and the petering conversation returned briefly to Puer, who stood quietly nearby and hadn't pawed nor rolled since the morning. Toffy, the horse expert, hadn't seemed too concerned, so it jarred Hemlock when the expert horseman, as an afterthought, and close to unconsciousness, had mentioned HCF sending a vet.

They would, immediately. He'd bring medicine and a sidearm.

She squeezed Puer with her thighs, out of love rather than to impel him, and he knew the difference. He snorted and shook his head for her.

Hemlock could visualise the contours of this section of the Forest, and she knew she would have seen light from Oca and Ape's windows as she'd made the last lazy turn to the right, following the road. Everyone must be asleep.

But when she pulled up in front of the workshop, Hemlock knew something was--just a little bit--wrong. Cheops was out front; he greeted Puer eagerly. She could make out a dim glow from the wood burner through the window, but no one was about. Cheops had a blanket, but Toffy would not have left him out front all night; there were six stalls and a paddock behind the workshop.

She let the doe slide off her lap into the snow and dismounted.

A note was affixed to the front door. In Ape's hand it read: ``Hemlock, come to the cave. Christoffel is unwell.''

She folded the note and put it in her skirt pocket.

She placed her pack inside the workshop door, where she found Cheops' tack and Toffy's bow and quiver.

She untacked Puer and placed her own saddle beside Toffy's.

She put Puer and Cheops in stalls, and the dead doe in a third.

She filled water buckets in the workshop and hung them for the horses.

``Drink it before it freezes, boys,'' she said.

She found hay in the box outside the stalls and tossed each horse a flake.

Then she set off for the cave.

CHAPTER: Kimberly \& Asa Attend a Meeting in the Forest

A Barge Upon a Lake, Evening



The barge's dining room was lit with copper lanterns suspended on copper chains above its three long cloth-draped tables. Kim's eyes followed one chain up to where it connected in a copper rosette to the teak plank ceiling, then across the ceiling, past a half-dozen identical chains and rosettes, to the lace-curtained teak and glass hatches--French doors, really--leading to the command suite. Commander Roos, seated to her right, reviewed their checklist for, as far as anyone knew, the first in-country meeting with King Ekkor's Chief of Staff, whose military and diplomatic rank St John's equated with its own most senior flag officers.

``I have met him once before, in Kandy, with the royal party,'' Lieutenant Commander Roos had told Kim in the interview that had preceded her selection to accompany him on this visit. ``That's the only reason I'm going,'' he'd confessed to her, not conspiratorially, but rather with a weary ambivalence. Roos had known who her father was, and even if he hadn't, Dad had descended seven flights to poke his head into that interview, kiss her on her cheek, genially greet and shake hands with the apparently well-connected Roos, and demonstrate to everyone in the Headquarters that if the Commander were, uncharacteristically, to influence the selection process, it would not be covertly.

By that time, Kim had proven herself, both in the schoolhouse and in her first months at the DWF Desk, bringing to bear the fruits of her research under Newfoundland \& Labrador's most eminent Forest scholar. Her knowledge was profound, her ideas audacious, but Commander Roos had demonstrated to her, without any self-satisfaction, that it was academic.

``There's no physical border,'' he'd said. ``Nothing to cross in the Euclidean sense.''

She now knew--one of the few State secrets she possessed, divulged to her in a short brief by Mr Bradfield in his basement redoubt--that Roos' and her own access to the Forest proceeded from Lieutenant Shattering's entry, and that no filter had been devised by which visitors using this ``piggy-bac.'' mechanism would be able to perceive their surroundings in any way not characterised by the unique experience of the pathfinder. The idea was not alien to her, from her research, but she and her mentor had not been successful in advancing research along those lines. The ``firs.'' Icelandic settler had been impossible to identify. Rumours of shipwrecked Newfies were unsubstantiated by any real evidence. If anyone else from any other nation had entered the Deep White Forest, they'd been lost forever, and with no apparent benefit to their sponsor. Newfoundland and Labrador retained the only diplomatic ties to Ekkor, Iceland the only known settlers.

So the Forest she and Roos now beheld was the Forest Thomas Shattering had, in his hopeless love, ``invented.'' In a way, they'd stepped into Shattering's imagination. As her mentor had suggested: St John's had a use for this incarnation of Ekkor's realm. The details had not been shared with her, nor Roos as far as she could tell. This meeting was the first of what would likely be many, and the Courts of St John's and King Ekkor were not the only participants.

The door at the other end of the dining room, opposite the command suite, opened, and Kim and Roos both turned to see a tall, onyx-skinned woman with fine features in a gold evening gown. She had daisies in her flowing black hair, and she moved with mesmerising elegance. Roos was already on his feet when Kim began to stand.

``No, no,'' the woman protested, motioning them back into their seats. ``I'm no one,'' she said smiling. She sat herself opposite Kim at the long table, and extended a long-fingered hand.

``Gwen,'' she said.

``Kim,'' said Kim, ``um, Lieutenant Junior Grade Jack.''

``Lieutenant Commander Asa Roos,'' said Roos, reaching across the table to shake Gwen's hand.

This woman was, Kim knew, the representative of Circe, who was cousin to Artemis, the mother of Ekkor's daughters. They hadn't known exactly what she'd look like, but Kim was certain this woman did not represent the fourth and final party to these talks. About that representative, they knew very little. ``Le connaîtras,'' Ted Bradfield had said, in a rare upstairs appearance at their final pre-mission briefing with her father's own Chief of Staff and a young bespectacled man Roos later identified as a member of the royal family.

``How was your journey.'' Gwen asked Kim.

Kim shot a quick look at Roos, who nodded, a brief interaction that elicited a smile from Gwen. She was striking in her gold outfit, the bright whites of her eyes, her white teeth, and the pale palms of her hands contrasting with the deep black of her pupils, skin, and hair to give the impression of a figure painted in ink, then gilded.

``It was long,'' Kim said.

``I understand,'' said Gwen, nodding.

If St John's intelligence was accurate, Gwen's journey would have taken ``eighty-six days by fast horse.'' After entering the Forest, Kim and Roos' journey would have taken a couple weeks longer than that. But no one at this meeting had travelled by horse.

``How can a place be so central and so remote.'' Gwen asked rhetorically, spreading her ashen palms. ``Like the nucleus of an atom.''

``I don't know,'' said Kim.

Gwen seemed to look deeper into her eyes.

``He values His isolation as much as His influence,'' Gwen whispered.

The doors to the command suite opened, and a well-built older man in casual business dress stepped into the dining room. He was followed closely by a much younger, much thinner man carrying books. The obvious respective demeanours of principal and aide were familiar to Kim. This was Ekkor's Chief of Staff and either his aide de camp or perhaps Ekkor's own.

``Gwen.'' said the COS, as all who were seated rose. He crossed immediately to embrace the woman warmly.

``Hi Mike,'' she said with a smile and tone that Kim recognised as indulgent.

Meanwhile, the aide shook hands with Roos. ``Asa,'' he said.

``Daniel,'' replied Roos. They smiled at each other.

``Asa.'' proclaimed the COS in a big voice, reaching a big hand across the table.

``General,'' said Asa, shaking it. He indicated Kim. ``This is Lieu-.''

``You look good, boy,'' said the COS. ``Strong. Your vigour much replenished here among the maples, here in the snow. Doesn't snow much where you live these days, does it.''

``You're not wrong, General,'' said Roos, smiling.

Asa Roos was a born diplomat. Kim and everyone else in her department, including its leadership, were in awe his faculty with this part of the job in particular. The blonde Scandinavian was just as handsome as the role required, no more. There was something warm about his smile, but not too warm. His humour had an edge, but one that drew a line rather than cutting along it, a humour that, like his technical-speak, tended to demonstrate his intelligence without showing it off. Most of all: he never spoke what need not be spoken.

``Not often, my boy,'' said the COS after legion such unspoken things crisscrossed the table between the eyes of the two men.

``General, this is Kimberly Jack,'' Roos said. ``New to the Forest Desk.''

The General's eyes, pale and grey and intelligent, fixed on Kim.

``General, it's an honour,'' she said.

He extended his hand--he had enormous hands--and she shook it. His palm was soft and warm, giving her the impression of a cloud enveloping her fingers.

Still looking at Kim and smiling, the General said: ``Daniel, who are we missing.''

Before the aide could reply, Gwen spoke. ``They're here, Mike. I saw them on the pier. Or rather, on and off the pier. They spied eels, and whoop!-.'' she mimed a dive with her hand ``--in they leapt, like retrievers.''

``Oh dear,'' said the General, taking a seat beside Gwen. Daniel sat down on his other side, placing the armload of books on the table. They were bound in red hide, with copper leaf titling Kim could not make out.

``Asa,'' said the General, shaking his head at Roos, ``the company you keep, these days. Do Icelandic vessels appear as pacing dragons in Foggo's restless sleep and on his horizons.''

In her entire life, Kim had never before heard the King of Newfoundland \& Labrador referred to by his surname, with no honorific. It was stunning. She sensed Roos stiffen, but only a for a moment.

Gwen's eyes swept all their faces quickly. She folded her beautiful black and white hands in front of her on the table and addressed them all, smiling. ``Likely to leap off from a treaty as from a pier, these companions, having spied eels, or polished copper, or something cheap and shiny.''

Kim was surprised when Roos spoke up. ``We can start without them, General,'' he said.

``That's fine,'' said the General. ``Does anyone want a drink.''

Kim and Roos shook their heads.

``No thank you, Mike,'' said Gwen. ``Let's get started.''

``Daniel,'' said the General.

Daniel opened one of the volumes and pulled out a folded letter. He opened it and placed it on the tablecloth in front of him.

``The King has reviewed this Letter of Agreement, and He will sign it, entrusting the Chief of Staff's office to review the critical text and the attachments, and to address dissent-.'' he looked up momentarily at Gwen then Asa ``--such as may arise here today.''

He paused, seeming to wait for input from Gwen or Asa, but none came.

``Keep going,'' said the General, a bit impatiently.

``And...'' Daniel stammered a bit. ``And to otherwise to ensure that it articulates the intent, um,'' he began reading from the text of the letter, ``one, of Circe to lay claim as sinecure for her liaison, Gwendoline, to the armature, structure, and influence of the Black Church and its Parish, those holdings Iceland's to abjure upon the King's demand; two, of St John's to furnish Copper bodkins that expand to penetrate axiodistally upon impact-.'' he looked up at Roos. ``Am I saying that right, Asa.''

``You command the language well,'' said Roos.

``If not the science.'' chuckled Daniel.

The General needed only to inhale and turn his head two degrees toward Daniel to again move things along.

``And three,'' said Daniel, returning smartly to the letter, ``of our Kingdom to contract to St John's one squad of archers-- called 'fairies' here-.'' he turned to look at the General.

``Close enough,'' the General said, smiling at Asa.

``--to prosecute her warlike adventures abroad, except such adventures as injure those dear to the King, or degrade somehow, uh, 'fairy' repute...'' he looked round at everyone. No one spoke.  ``...or if Circe demurs,'' he concluded, looking at Gwen.

There was silence. It was as Roos had told her during their crossing: Ekkor's forces were formally to be aligned with the interests of Newfoundland \& Labrador, and a detachment of the King's innumerable red-hatted daughters would advertise this to the world, but most importantly to Iceland. Iceland also appeared to be losing a diplomatic foothold in the arrangement, with Circe taking over the Black Church in Waccabuc, long the seat of Icelandic faith for the Forest's three million or so settlers.

``The Black Church.'' said the Chief of Staff, looking at Gwen.

``Yes,'' she replied, nodding slowly.

``Where are you living now.'' he asked her.

``A lovely villa, General, on the brow of a Vedauwoo outcropping.''

``	Why should anyone flee Vedauwoo.'' He looked at Asa. ``I'll allow: the fishing is better in the woods, but if ever in history there stood a more majestic cathedral in air than the King's forbidden Mountain, scarce could I credit it. The woods are so thick down there in Waccabuc, the trees block one's view of the Forest. Iceland's God scant hears a prayer amongst the myriad words Icelandic hymns plant in His ear, so it's fitting His priest chants His praise in the jungle.'' He turned back to Gwen. ``But for you, Gwen, please, from Aeaea to Waccabuc, it can't be an easy transition.''

``There are trees on Aeaea, General,'' said Gwen.

He stared at her, his smile fading a bit.

``Not like these,'' he said.

The door behind Kim burst open, and she felt a chill and a bit of spray hit the back of her neck. She turned to see two jagged red polygons with spindly arms and legs enter the dining room. They had wide circular eyes and huge grinning black mouths filled with bright white needle-like teeth. As they moved, Kim saw that their almost body-length heads were completely flat and depicted a mirror image of their lunatic faces on the reverse.

They locked onto her immediately.

The polygons leaned toward her in tandem, and Kim leaned away. She watched their pupils slide toward each other then back to centre to regard her. She realised she was holding her breath.

``What.'' one of them shouted at her.

Kim flinched and blinked. They just stood there and stared at her. Roos would not meet her gaze. She looked at Gwen, who smiled at her wanly and rolled her eyes.

``Gentlemen,'' Daniel said.

Apparently finished with her, the polygons walked past Roos and turned to address the table.

``Please excuse us,'' one of the polygons said in a high voice on the edge of a wail. He was highly asymmetrical, with at least fifteen sides, the angles alternating between concave and convex, some quite sharp, his two-dimensional aspect giving the impression of a break in the glass of reality. ``We were chasing eels.''

The other polygon, just as irregular in shape, its voice lower and just as maniacal, looked at and named each of the party in turn. ``General...Gwendoline...that guy...that guy.'' It now ignored Kim entirely.

When the angles of their chins happened to move aside to reveal the place on their skeletal red bodies one might have expected to see genitals, Kim was helpless not to notice they had grinning faces there too, smaller, less polygonal, just as wide-eyed and insane. One caught her glance and its eyes grew even wider with excitement at being beheld. She was instantly nauseated.

The deeper-voiced polygon continued: ``I am going to say we are honoured to be among you. I am going to speak Japanese. I am going to give a history of Icelandic settlers in--where are we, Bickle.''

``The Deep White Forest, Pupkin,'' the other shape said.

``Thank you,'' said Pupkin. ``I'm going to say 'chrysanthemum'--wait! The Deep White Forest? With the elsequir, the reelsiqu, the liqu-.'' With each nonsense word, the enormous toothy mouth flickered and scrolled, like an oscilloscope losing its tracking.

Gwen had, evidently, had enough.

``Must these creatures address us so informally, Mike.'' she said.

Bickle hit Pupkin, bending an acute spike of its face.

``Aye, Pupkin.'' said Bickle.

The flat spike slowly, sickeningly, returned to its original shape.

``Rhyme and swerve.'' Bickle continued, doing a little dance. ``Put your words out of common order.'' It looked at the General. ``For not to speak normally is surely to speak fairy.''

``Never doubt,'' rejoined Pupkin, ``my deference to local custom, about which I know more than you, Bickle. But please remind me where we are again.''

Bickle's grin grew, impossibly, wider. ``The Deep White-.''

``Wait.'' shouted Pupkin. ``First inform these fools which of the gentle Eumenides we pursue.''

``A kind, bespectacled babe,'' Bickle said.

Pupkin focused his attention alarmingly on Kim. ``Have you seen this girl.'' it yelled, launching into a parody of riding a horse and firing an arrow. ``Glasses? Bare knees.''

When Kim just stared, Pupkin appeared to grow angry. It stopped its pantomime and walked toward her.

She recovered her bearing.

``Don't touch me,'' she told Pupkin, stopping it in its tracks.

``Aye,'' said Bickle. ``Don't pester people, knave.''

The General, who appeared to have no intention of asking these two to sit, said to Daniel: ``Are they talking about an archer? One of Ratatoskr's daughters.''

``Ratatoskr.'' Bickle and Pupkin shouted together, their horrible voices harmonising with a surprising musicality.

``Have you heard that song.'' Pupkin said to Kim.

``Don't talk to me either,'' she replied. She caught Gwen and Roos exchanging glances of approval, detecting that they both were impressed with her standing up to what was obviously a demon from Hell, a servant of Errour. Kim didn't care what Roos or anyone else thought at the moment. Her disgust with these creatures was profound.

``Shiroi mori. Futsuu no,'' said Pupkin, now standing erect and pompous, a poet giving a reading, ``Usagi no hiyaku. Yuki o...'' he turned his head to look at Kim again, this time as lovingly as his preposterous countenance would allow ``...wasuremashita.''

``White woods,'' said Roos, helpfully. ``A hare leaps. I forgot it was snowing.''

``What the fuck is going on, Sir.'' Kim asked him.

Daniel leaned and spoke to her from across the table. ``They bring madness with them,'' he said. He was a handsome young man, she noticed, with a kind face. ``Just ignore it.'' He smiled.

``Yes,'' said the General. ``Where were we.''

``The Black Church,'' said Gwen.

``Ah, yes, the Black Church,'' said Bickle. ``Now I hear its dark bells pealing. Pupkin, please,'' it entreated its partner.

Pupkin now spoke as one reading an encyclopaedia: ``Shipwrecked Icelanders, generally thought to be the first people to settle the Deep White Forest, in particular a sect worshipping a benevolent aspect of Christ, built the Black Church from blood- and soot-stained granite one may still collect from the foothills of Vedauwoo. The trees are thick in Waccabuc, but the soil is good, and so they chopped and farmed and raised livestock and thrived, and from this stony womb that has there stood one-followed-by-many-zeros years, was derived a civilisation of villages and farms, a folk simple of soul and innocent of arms.''

``Bigots and litterbugs,'' said the General.

``Certainly,'' said Bickle.

``Simple to govern,'' said Gwen.

``They pollute everywhere they go,'' said the General, sternly. ``They believe everything they read. The church is Circe's.'' He took the letter of agreement from in front of Daniel and passed it to Gwen. The eyes of the demons followed.

``What,'' Bickle said, ``does Ekkor need of high-tech arrowheads? Are his one-followed-by-many-zeros archer daughters not sufficient to the task of suppressing rabble.'' No one spoke. ``Bring out the archers.'' Bickle shouted.

``Are they here.'' said Pupkin, excitedly. ``I want to see one.''

The General cleared his throat, preparing, Kim thought, to dismiss these two.

``I want to see,'' Pupkin said, its voice growing louder with each word, ``right now, a horse-borne fairy archer.''

``Pupkin, be calm,'' said Bickle.

``Nay.'' shouted Pupkin with a dramatic wave of its stick arm. ``let me say what others cannot say, silenced as they are by custom or qualm. Of the Fairy archer I sing a psalm, she who is so lean and dextrous and fair, whose ever warm and dry and able palm is to bare skin as is God's love to the bare soul, as fatal and as rare. In her eyes adventure beyond one's sanity may be embarked upon should one dare stare. If God plus animal equals humanity, she is the pinnacle of that profanity! Her grace in war achieved without conceit, her fullness of faith given without vanity. Her deity's pelt adorns her head and feet. Her horsemanship is chief among her many features. Her music is surpassed only by woodland creatures.''

To Kim, it didn't necessarily feel like an infection of the demon's lunacy that she too wished to see one of the archers.

Asa voiced her sentiment. ``General, we also had hoped to meet one of Lord Ekkor's daughters.''

The General looked at Daniel.

``We are prepared,'' said Daniel, addressing Asa and the demons, ``to send a delegation to Walpurgisnacht.''

The demons looked at each other.

``Really.'' said Bickle.

``Will that suffice.'' said the General. ``There may they be conveniently compared with all the warriors, diplomats, and spies the universe has to offer.''

``A delegation.'' asked Bickle, in whom Kim now detected the operator beneath the lunatic.

``A squad,'' said Daniel.

``Is that four.'' asked Gwen.

``That is four,'' Daniel confirmed.

``Fully twice and twice again what is needed for any Earthly war,'' said the General.

``No, four is all we need,'' said Bickle.

``Bickle...'' said Pupkin.

``Oh.'' Bickle snapped its fingers. ``We want the one with glasses.''

``Glasses.'' the General said.

``Glasses,'' repeated Pupkin.

``No daughter of Ratatoskr has such a defect,'' said Gwen. ``They are expert archers and horsemen.''

Kim detected a genuine protectiveness, though by all accounts the archers needed no one to protect them. But this third enumerated point in the letter of agreement was consequential: according to Mr Bradfield the archers had participated in hundreds, maybe thousands, of wars over thousands of years, some in extraterrestrial theatres, but always directed by Ekkor's Court. This seconding of DWF forces to foreign--to Newfy--control was unprecedented.

The reaction of the demons to Gwen's interjection was inscrutable. Kim sensed they awed her somewhat more than they did Ekkor's Chief of Staff. Their slanted brows made them look persistently angry, so it was purely Kim's instinct that they hated Gwen. They were demons; perhaps they hated everyone. But just now there was a pinch of surprise in the loathsome admixture of their expressions, and not the sort of surprise at being rebuked, rather the sort of having discovered they knew something Gwen did not. There was a momentary heightening of the component that made their malevolent, violence-worshipping faces most sinister: glee. And when, as she stared at them, all four pupils now slid in concert to fix on Kim herself, her revulsion was replaced with authentic fear.

``What.'' shouted Pupkin, ``are you staring at.''

Kim recoiled, and the demons laughed.

``Pupkin, is it.'' said Roos.

The one called Pupkin's eyes moved further to regard Kim's laconic supervisor. When the diabolical mouth affirmed with ``mm-hm.'' it was with no meeting of lips, such as they were, no concealing of the white dagger teeth.

Roos opened his notebook, saying: ``I have your real name written down in my notes, I think. Shall I show it to you.''

The glee departed from both demons' faces.

Before Kim could either wonder at the nature of the threat Roos had evidently made, or be touched by his defence of her, the Chief of Staff broke in.

``I would be careful,'' the General said, addressing Bickle. ``Newfoundland has demonstrated herself to be formidable in recent years.''

Bickle scoffed. ``You are much beguiled, Chief of His Royal Staff, by the indomitable wit of this shapeshifter.'' It pointed at Roos.

``What does that mean.'' Kim said, wanting to steady herself, wanting to reciprocate Roos' support, but finding a bit too much courage. All eyes turned to her, and the moment became no different from any other high level meeting in which a junior had spoken up and regrettably invited scrutiny.

Gwen gave her grace.

``Dear,'' she said, ``don't bother. One cannot but encourage the incorrigible.'' She turned to the General and lowered her tone. ``Mike, are you sure their Holy Father wants the girls going to Germany? It's rather a ribald crowd attends Walpurgisnacht. And there will be nuclear warheads and other alien technologies.''

``Aye, machine guns,'' said the General, leaning back in his chair, his eyes still on Bickle. ``Tanks and missiles, et cetera.'' He thought for a moment, then added: ``Lasers.'' He looked at Gwen. ``None of these are mysterious to us.''

``They're in the Bible,'' Daniel said, patting a volume in front of him.

``Yes, Ekkorbok,'' said the General. ``These all are by our scholars, and our immortal archers, understood.''

``Well...'' Gwen dragged out the word, making it clear that the Walpurgisnacht ribaldry had been more her point.

Bickle took her meaning.

``Spring will be there.'' the demon announced excitedly.

``And his brood.'' chimed in Pupkin.

``The troubadour that strums.'' said Bickle.

``The cock that come.'' said Pupkin, pausing lasciviously before concluding ``to greet the sun.''

``Pipes an drums.''

``Chrysanthemums.''

Bickle hit Pupkin again, bending another of its pointy bits.

``Will you shut up about-.'' Bickle's eyes scanned the other faces in mock concern, and with mock apology it explained: ``Pyrethrums abound in Hell. They grow in the slums. Pupkin likes the smell. Don't you, dear Pupkin.''

Pupkin looked at Kim with a grotesquely entreating sheepishness. ``They grow from out people's bums,'' it explained.

``That's great,'' said Kim.

Pupkin pulled a live eel from, Kim guessed, its anus. ``Eel.'' it offered her.

``No thank you,'' she said with a smile.

She could feel Gwen's and Roos' subtle approval, as if she were passing a test both had themselves previously passed. Her gorge descended somewhat, but she could see in the wicked eyes of the demons that the taunting could get much, much worse.

Roos opened his notebook and scribbled something Kim couldn't make out. As Kim looked round the table, she perceived that the demons were somewhat to be indulged. The General had fixed a cold smile, and Daniel the aide was opening a bottle of ink, she assumed for signatures.

``Our lasses,'' said the General, turning to Gwen, ``will acquit themselves with the grace for which they are as famous as their war-fighting, don't you think.''

``Of course,'' said Gwen.

The General turned to Asa. ``Asa,'' he said, ``you've been to this thing before.''

This would have surprised Kim a week ago. She was beginning to understand that Lieutenant Commander Asa Roos was a node at which many cosmic threads connected.

``Witches' Night.'' Asa said. ``Yes, Sir.'' He glanced at Gwen, then back at the General. ``This year's procession commemorates Arlo Hill.''

Now Roos and the General both looked at Gwen.

``Oh.'' she said.

``The program antedates our commitment,'' said Asa. The General's smile had faded. His eyes were fixed on Gwen's.

``That's my miss, Sir,'' Daniel said to the General, who motioned absolution and silence with a quick gesture of his hand.

``Olympus sends many delegates,'' Asa explained. ``They like to reminisce.''

``Is She going to have a problem with this, Gwen.'' the General asked.

Now the demons were giggling.

``What is the problem.'' Kim asked Roos.

``The problem, kitten,'' said Bickle, ``is a slap in the face to Her Grace.''

``Newfy guy,'' Pupkin said to Asa while looking at Kim. ``Hey Newfy guy, who is she? I see ermine in her eyes. What, do you have to be blonde to be in the Newfy Navy.''

``The problem,'' Asa said to Kim, ``is Circe may proscribe Diana's daughters' participation in celebrating what She--Diana I mean--judges a perversion of history.''

``An excursion from history, anyway,'' said Gwen gently. ``But I am not here at her behest--Diana I mean.'' She smiled at Roos, then turned to the General. ``Surely the deployment of His daughters' noble service is best determined by their loving Father, lest he appear distracted.''

 The General regarded her coldly. ``They will attend,'' he said with finality. To Daniel and Asa he said: ``We'll have assessed these arrows by then.''

``Yes, Sir,'' they both replied.

``Lieutenant Shattering will accompany them, Asa.'' Daniel asked Roos. ``Their man,'' he clarified for Gwen.

 ``Is he sincere.'' Gwen asked.

 ``He does what he's told,'' said Roos. ``He goes where he's sent.''

 ``He lives with them.'' Gwen asked Daniel. ``How long has he been here.''

 ``No, Ma'am,'' said Daniel. ``He lodges at the Chanticleer in Three Nations.''

 ``I know that hotel,'' said Bickle.

 ``Oh.'' said Pupkin.

 ``He has been here for a few months,'' said Asa. ``Since Autumn.''

 ``Have you met him, Mike.'' Gwen asked.

 The General looked at Daniel to see if he had. Daniel shook his head.

``You may interview him before they go,'' the General said to Gwen. Looking at Asa, he said, not asking: ``Is that okay with you.''

 Kim started to object. Newfoundland \& Labrador had no relationship with Aeaea. Navy law was crystal clear on this point.

But Asa said: ``Yes, of course.''

``Send him up to Waccabuc,'' the General said to Asa.

``When the snow melts-.'' Asa started.

``Right away,'' said the General.

The two men looked into each other's eyes for a moment. Kim got the feeling from Roos that rather than cowing to the man, Roos was accepting a transaction, that the General was expending some kind of diplomatic capital in so ordering the Newfy Navy round like this. Roos scribbled in his notebook again.

``Is he a bowman, this Thomas Shattering.'' Gwen asked Roos. ``Can he ride a horse.''

``Uh, yeah, no,'' said Roos, closing his notebook.

``Newfoundland and Labrador's Navy does not possess a single archer,'' said Bickle.

``Nor equestrian,'' said Pupkin.

``Nor child of divorce,'' said Bickle.

Pupkin guffawed. ``He must stick out like a sore thumb amongst those billion riqrusel girls.''

Gwen rose. Everyone stood in response. She extended her hand again to Kim.

``It's been a pleasure meeting you, Kim,'' she said. The warmth in her eyes was real, and it moved Kim. She felt happy to have pleased this woman, though she didn't know how she'd done it.

``Mike,'' she said to the General, then nodded at Daniel.

``Gwen,'' said the General.

Gwen glanced once at Roos, then looked at the floor for a moment. She exited through the door she'd come in, not acknowledging the demons.

``Guess she's not signing anything today,'' the General said to Daniel, who capped the ink bottle.

The General then stared at Bickle and perhaps expended some capital with that party in making it clear they were to leave. The demon's absurd face took on a momentary expression of a skilled envoy.

``Shall we go.'' it said to Pupkin.

``Yes,'' Pupkin replied, ``let's go.''

Kim didn't turn around to watch them leave, suspecting that seeing them from behind would challenge her composure again. She felt the cold air on her neck again, heard the door click shut, then felt the barge rock and heard a splash as they evidently leapt into the lake.

Daniel made a face of disgust to Roos, who just shrugged.

Kim was familiar enough with these sorts of visits to know that the next glances between Roos and the General had less to do with business and more to do with whether they'd all go out now and get drunk.

``I gotta be up,'' said the General after a moment.

``I understand, Sir,'' said Roos.

Guess not.



Their hotel overlooked the lake and the barge upon it. The barge was kept brightly lit, and its reflection rippled delicately on the water's surface. Beyond the lake, the dark trees gave way to the pale foothills and rock outcroppings of Vedauwoo. Beyond that, the mountains. Towering over all, His Mountain, at the moment just a horn of missing stars on the horizon.

The barman, a Settler like everyone else who worked at the hotel, placed their drinks on the small circular table between them. Two large globe glasses with icy gin and tonic and fresh sliced lemons.

``You could have prepared me better,'' Kim said to Roos, referring to surprises in the meeting so obvious they scarcely needed to be enumerated. ``Clearances be damned. I mean, if I'm going to be in the room.''

``None of this is classified,'' Roos said, sipping his drink. His face was expressionless. ``Honestly, I just didn't think of it.''

More likely he'd wanted to test her.

Fuck him, she'd passed.

They looked out the picture window at the splendid view.

``So those are demons,'' she said.

``Mm-hmm.''

``Like, from Hell.''

He looked at her and chuckled. Then his face went blank again. ``Yeah,'' he said. After a moment, he asked: ``Are you Catholic.''

Her mouth full of gin and tonic, she nodded, swallowed, then said: ``I wasn't raised Catholic, but, you know, my Dad.''

Roos nodded understanding.

``My Grandfather, my actual Grandfather, knelt at altars of whalebone.''

Kim had noticed that when distracted and faced with having to react to an evidently heartfelt overture in conversation, Roos loaded from a bottomless magazine of inscrutable platitudes.

``Hegel would approve,'' he used now.

He finished his drink, got up, and said: ``I'm going to bed.''

``Goodnight, Sir,'' Kim said, remaining seated.

Their journey back to St John's would begin at three, now just four hours away. Kim sat for another few minutes, looking at the silhouette of His Mountain. If there were demons, if they could walk around the Forest and speak and catch eels, what else was possible?

Kim finished her gin and tonic and went upstairs to bed.

By ten the next morning she and Roos were seated three stories above the tarmac in a Royal Newfoundland and Labrador Air Force transport. As far as Kim knew, the airman in the jump-seat facing them was the only other passenger on an aircraft that could accommodate sixty in the seating area, in addition to thirty tons of cargo--or ordnance, or refugees--in the hold below. Kim hadn't seen the hold as they'd ascended the narrow stairs to their seats. It might be empty, such was Roos' juice. Roos had briefed everyone entering the DWF in a secret meeting with Mr Bradfield, a meeting to which Kim had not been invited. Asa was personally acquainted with Tom. He could enter. So could someone acquainted with Asa. That's how it worked. ``Third order contacts? Unknown,'' both her advisor and Mr Bradfield had told her, and she'd found no record to convince her either way. She'd been nervous when they'd first approached the airspace, but she'd held onto the words of her advisor: ``You won't be repelled. You will not find it.'' When they'd landed in Vedauwoo, Kim had assumed that Asa had managed to establish personal contact with everyone on the flight crew. Everything Roos and Kim herself and every other Newfy on the aircraft saw, heard, smelled, felt, and experienced since they'd landed the previous morning had been shaped by the character of Lieutenant Shattering's ingress, whatever that had been.

It was not a hellscape, Kim had thought. He must have entered joyfully.

The four enormous engines slung from the aircraft's mighty wings were spinning up to the right and left, each on their own schedule for the moment, filling every audible frequency with whine or groan.

``We could go tell him ourselves,'' she shouted to Roos next to her. He looked at her, his eyes narrowing ever so slightly.

Over an early breakfast at the air terminal, he had lamented the unreliable communications with Shattering and made clear he suspected the problem was on the N\&L side. ``We've asked Ted to help us with this,'' he'd said, ``but it's not the sort of thing he enjoys.'' Just as they'd finished their breakfast, Daniel had appeared, presumably to see them off. ``Nice to meet you, Kimberly,'' Daniel had said. He'd handed Roos a small brown envelope bearing the King's seal. ``Just in case,'' he'd said. ``Blood chits,'' Asa had explained to Kim.

Did Roos not trust everyone in their organisation? God, he was hard to read, this pale, sardonic operator. He was above trying to impress her, but Kim had detected in him an impish, if not impulsive, inclination to shake up the system, maybe to remind the system that he'd helped to establish it.

Roos turned his head to look at the airman, who was listening to the preflight brief on his headset. Roos leaned forward and tapped the airman on the knee. The airman looked up. Roos mimed passing the headset. The airman did. Kim could not hear what Roos, interrupting the brief, said to the pilot, but it was no more than ten words. Roos handed the headset back to the airman.

``Good idea,'' Roos shouted to her.

The engines roared, and the leviathan they sat atop, slowly, paradoxically, started its motion.











PART TWO



CHAPTER: Thomas \& Fury Picnic in the Forest

A Wood, Early Afternoon



``What do you call this tree.'' Thomas asked Fury.

In ankle-deep snow they'd walked west on the trail from Three Nations out to the high meadows and hills that overlooked the village. The Forest was dense here until it opened up onto a vast expanse of grass that described the boundaries of an ancient forest fire. The trail was wide, though, serving the farmers and traders of Three Nations. Fury had told him the nearest settlement of any size was in this direction, but it was two weeks by horse.

The tree in question looked like an ash, but Thomas wasn't sure. He had never mastered, as his mother had, identifying plants and flowers.

``Him? He's called Donald,'' came Fury's reply.

She was in an unusually good mood. He gave a perfunctory laugh.

``That's an ash. You call it ash.''

``We could eat here,'' he said to her. He was tired. Saturday night had been the Hoot, he'd spent Sunday walking back to the Chanticleer and recovering. Only the thought of seeing Fury had gotten him out this morning, despite the housemaid bringing bacon and eggs to his room, shaving him, and removing to the laundry his soiled and smokey weekend outfit. This afternoon, he'd again see his dark jumper and trousers hanging in the sunshine on the lines over the snow-covered south lawn, a lone, small bisected mortal floating amidst a battalion of enormous, cold, white linen angels.

That reminded him: he'd made another list. It had taken him weeks to read Christoffel's handwritten primer on archer history, not because of her handwriting, which was lovely and neat, but because he'd had to look up a reference or allusion in virtually every line. The only source available in the Forest was Ekkorbok. ``Ekkorbok contains every other book,'' Christoffel had reassured him. ``Even this one.'' he'd asked, holding up her notes. ``Yes,'' she'd replied without irony. ``Couldn't you have just lent me this volume, rather than copying it out by hand.'' he'd asked. ``I looked,'' she'd said, ``we don't have that one at the lodge.''

He'd made lists of questions for Fury, who sometimes looked askance at particular items. ``Toffy wrote that.'' Fury would say.

Now Fury said: ``Let's go into the woods a bit.''

He knew now she wasn't relaxed under the open sky. Also, he didn't think she relished Settler greetings. She was armed today, but for hunting, she said. No traders or travellers had yet passed them this morning, but typically one or two would on this road, and Thomas had become familiar with the settler expression unique to beholding an archer. It was the face schoolchildren wear in the presence of the headmaster.

He took his little list from his pocket as they walked into the woods.

``Angels,'' he said to her.

``Oh yes,'' Fury said with a chuckle. She looked at him. ``Is this going to offend you.''

They'd broached some topics in the past weeks that had made him uncomfortable as a Christian, but he'd been there before, in Arabia, in Asia.

``No, I'm fine,'' he said.

The snow was deeper here, with a thin glaze of ice over it owing to some local melting and refreezing in the night. They crunched through, sinking now to their calves.

``So she wrote about the Empyrean.''

``Yes. A bit.''

``Did she mention I wasn't there.''

``Oh? No.''

``No, I was...'' she chuckled again. ``I was at a music lesson. It was a scheduling error. Not Hobby's.''

``Oh, so the forces of Satan, dragons, et cetera, but three of you were adequate.''

``I think Hobby could have handled it on her own, to be honest.''

He looked at her. She was being honest.

``There's clearing up here,'' she said. Few miracles could impress him more than Fury's--than all the archers'--knowledge of Forest geography.

``I'm getting to know you all now, a bit,'' he said, aware of his own weakness, his tendency to reach out to her with petulant, needful overtures, begging her attention in a personal away. He'd been too tired this morning for it yet to have registered, but now he saw her anew, lifting her bare knees high to stomp her red fur boots through the snow, her bobbed hair swinging round her cheeks, the broken sunlight glinting off the glasses on her nose and the stars on her breast, and his stomach sank through the Earth and continued on to an opposite sky and space beyond. ``So,'' he continued, ``I can detect Christoffel's various modes of kindness. Her treatment of your divine allies in that battle is lousy with platitudes.''

``Um yes,'' said Fury. ``I mean, they, um...'' She stopped walking and considered. ``They suck, Thomas,'' she said finally. ``I mean, not all of them, but most of them. Hobby could give you an earful.''

He smiled, and she caught herself and smiled back. Hobby didn't talk to Thomas unless there was no way around it.

``Anyway, we had to train them.''

``Yeah, she said they came here.''

``Well not here,'' Fury said. ``Vedauwoo. Nice hotels, and the kind of company they prefer. Patrons of the arts. Tax fugitives. Yeah, we had a little clinic.''

Thomas looked at her questioningly.

``Oh, God, it was awful,'' she said, laughing humourlessly. ``They were useless. Luckily, as Hobby says, the other side was the same. In the Empyrean, Hobby and Christoffel helped lay the battle plan with, was it Michael.''

Thomas was shaking his head and blinking. ``Yeah, sure,'' he managed.

``Michael. He was halfway decent as I understand it. Anyway, Toffy carved a few up, I think, the enemy, but they were mostly cowards, and I think they wanted to yield. They went scurrying off behind their shield of humanity.'' She looked at him. ``Ha ha? Thomas.''

``No, I'm fine,'' he repeated.

She seemed chastened by his wonderment.

``Like I said,'' she said, reaching a hand slightly in his direction, ``I wasn't there.''

They reached the clearing, which was blinding in the sun, now at the apex of its low winter arc. Deer tracks crisscrossed the roughly circular snowfield, and swallows darted among the surrounding bushes, busy and picky with the abundant berries.

A trio of erratic boulders sat in the centre of the clearing. Fury hopped up and began kicking the snow off them while Thomas unpacked their lunch from his rucksack. They were calzones from da Fabio, the Neapolitan bistro in the Chanticleer. They were wrapped in copper foil and still quite hot.

``Oh, these are good,'' Fury said through a mouthful, closing her eyes with appreciation.

They sat facing each other from respective boulders, the rucksack taking its place on the third; it still held their salads.

``Yes,'' agreed Thomas, ``the buffalo that make these possible are out this way.''

``I've seen them,'' she said. ``I like their big, sweet faces.''

``I'm sorry,'' he blurted, ``how can you tell a regular animal from, you know....''

She thought. He hadn't asked her much about the animals, mostly because it wasn't part of his job. But something else had discouraged him, particularly when it came to Fury. She didn't exactly deflect conversation away from them, but there was a matter-of-factness that, unlike the uncanny ambivalence with which she and her comrades discussed the horrors of war, seemed a little bit forced, as if to hide that she was herself still coming to terms with the creatures' surreal advent.

``Well,'' she said at last, ``I suppose you can't really unless they're of unusual size, right? Or they're singing, but like human songs, not birdsong or something, or they're playing a guitar.'' She mimed awkward forelimbs attempting such a feat, which Thomas, no matter how many times he observed it up close and in person, could not quite fathom. He had sketched the animals, but so far only from memory. He wasn't sure sketching them from life would help him render the paradoxical physicality of their human motions.

He did hope to try one day.

He reached across to his rucksack and pulled out his sketchbook. Flipping through the pages he found his drawing of the big, sweet faces she'd mentioned and showed it to her.

``I love this, Thomas,'' Fury said, taking the book and admiring his portrait of one buffalo nuzzling another.

``You can have it,'' he said, reaching for the book, intending to tear out the drawing and give it to her.

``No,'' she said. ``Thank you, Thomas. I have nowhere to put it.''

He took the book and shrugged, a bit too deeply.

``Your drawings are lovely,'' she said.

He had waited six months.

``I could draw you,'' he said in as noncommittal a tone as he could manage.

He hadn't drawn any of them, even from memory. If he hadn't loved Fury, maybe he'd have dared. As it was, it had felt intrusive, inappropriate, indulgent...all the 'in's. No one had ever seen a drawing of an archer, much less a photograph. Even famous depictions of famous battles in which they'd reputedly played a major role excluded them, which was put down to the commissioning force's lack of candour about mercenary involvement in sometimes nation-defining victories. They'd never once been on the losing side.

``Is there a law against it.'' he asked her blank face.

``No,'' she said, and took a bite of her calzone.

Six months of almost daily walks and these awkward lunches. Weekends at the lodge; he had occasionally slept in the tack room. At least twenty-five Hoots. He'd watched Fury chop wood; swim in the frozen river; hunt, kill, and butcher deer; gallop Ontario through the woods faster than he could have imagined possible; sing and play her melodeon to the rising sun; dance with the animals; puke in the snow after drinking all night; collapse in a pile with Hemlock and Christoffel, all laughing, all high as kites.

Christoffel had taught him to ride. Cheops had been patient and accommodating. Fury had taught him archery. His naval training had made him an expert marksman with a pistol and rifle; it didn't translate. He'd made himself useful round the lodge on the weekends, helping with repairs, though the weakest among them, Christoffel, was stronger than he. Hobby hadn't warmed to him, but he had occasionally felt from her the tiniest helping of respect for his industry--and his drawings; she'd been unable to mask her admiration of these.

With Hemlock he smoked cigarettes and talked. From Christoffel's notebook he'd gotten the where and when and some of the how of a great many adventures they'd had, and from Fury he'd gotten some idea of the rules and religion under which they operated, but from Hemlock he'd gotten stories. Journeys by horseback across landscapes whose obvious wounds gave no clue as to the nature of the weapons that had so devastated it. Pranks they'd played on commanders nearing a victory they'd ensured. Fury being presented with a hand-wrought copper cat--a ``panthe.''--by Hannibal himself in Cormayeur, his self-satisfied Thomas-equivalent, along with a nude Nubian craftsman, a regiment, and two starving elephants in formation. ``They thought it was a sacred animal to us.'' Hemlock had told him. ``They almost got it right. Imagine being awarded a golden statue of the word 'fuck'. I was standing behind her, holding her hand. She dug her nails into me, look...'' Indeed, there were scars. Hemlock had looked up at him with those incandescent green eyes and grinned.

``Do better,'' she'd said.

Thomas had written his reports, replete with illustrations of everything except the archers. They sat piled up in his desk drawer at the Chanticleer. Awaiting a transfer on the windy deck of an icebreaker one of the King's agents had warned it might be some time before a line of communication was available. ``We don't have direct access to the carrier signal.'' she'd shouted at Asa. She'd glanced at Thomas. ``We were hoping your guy could help with that.'' Asa had shouted back at her: ``He's not a spy.''

What was there to spy on? These legendary warriors were the picture of idleness. Hobby had gone on a single ``lon.'' patrol, he didn't know where, but it hadn't seemed significant. Hemlock and Christoffel were out on a ``shor.'' patrol now, overdue in fact. They didn't drill. They didn't practice their war arts. Hobby still awaited word on a demonstration of Thomas' arrowheads; in the meantime he'd asked them to demonstrate their combat archery. It had been Autumn, before the snow. He'd been sitting at the picnic table outside the lodge with Hemlock and Fury. The two women had exchanged glances. Hemlock had had her bow handy. She'd plucked an acorn up off the ground and launched it sideways off her bowstring at the eel smoker thirty yards away. It had entered the small circular vent, scarcely wider than the acorn itself, cut into the lower part of the smoker's front door. They'd both stared at Thomas with exaggerated menace.

``We should try acorns in there,'' Fury had said, eye's still locked on Thomas'.

``Yeah, that sounds good,'' Hemlock had replied, also still staring at him.

Thomas knew the settlers were scared of the archers--more so in the village where Fury had killed a pet. He hadn't asked her about that.

He had asked Fabio and Enzo at the bistro about the archers. ``O, chelle cavallerizze,'' Fabio had said, making a Neapolitan hand gesture of great relish, ``che bbelle. Eh Enzo.''

``Si, bbellissime,'' the pizzaiolo had confirmed while turning a pizza in the oven with his long wooden pala.

Thomas had thanked them for their insight.

Fabio and Enzo were the among the few settlers Thomas had met that weren't, at least apparently, Icelandic. A freckled housemaid called Isabelle spoke French; he thought she might be Swiss. The archers were not census-takers, and if the settlers indeed ``pai.'' for every tree they felled, every river they dammed, every animal they hunted, and every gallon of His holy runoff they drank, Thomas had observed no real mechanism for the economy. No one seemed to know how many settlers or settlements there were.

He'd met Oca and Ape at the Hoot, and he'd admired both their skilled craftsmanship and their enormous fairy wings. They seemed to know the value in trade of various goods and services, but how those values were set was unclear. Hobby's horn had apparently been dear, for instance. Oca had fashioned Hemlock's intricate pipes for thanks alone. Deer meat, swan feathers, building repairs, metalwork, firewood, entertainment, raw copper, embroidered pillows, manure, whisky: all were currency, but Thomas had no clear sense of their mutual exchange rates.

Ilsa, the general manager of the Chanticleer, presented him with a bill every week, but she had made no attempt to collect any payment from him. He passed the bills to Fury, as she'd insisted, and she passed them on to Hobby. Hobby, who administrated from a small roll-top desk in the hall, opposite the bass and drums, had ledgers and files and stamps and seals and invited no inquiry into her administration. Thomas had noticed that the penmanship that flowed from Hobby's large, rough, axe-wielding, often cut and bleeding hands was even more beautiful and delicate than Christoffel's.

He'd wanted to draw those hands. He'd wanted to draw Christoffel singing and playing her balalaika. He'd wanted to draw Hemlock riding Puer, two blondes frolicking in Autumn leaves. Mostly he wanted to draw Fury's face, which possessed him.

Well, here he sat, notebook in hand, Fury sitting there on a rock, the snowy woods behind her, a half-eaten calzone in her hand. But she just chewed and stared at him like the buffalo had, and grateful as he was to be staring back at those bright blue eyes in their cage-like frame of copper spectacles, brown bangs, and high, full cheeks, she gave nothing like assent.

He put his notebook away and ate his calzone.



CHAPTER: Hemlock Meets Fury \& Thomas in the Forest

A Snowy Clearing in the Forest, Afternoon



God, do they just sit there every day and not talk to each other?

Hemlock saw Fury and Thomas in the clearing as she crested a down to their West. After a moment, she saw the brief shake of the long ears of Fury's headdress that indicated Fury saw her too. She spurred Puer and he reared, whinnied, and charged down the hill through the snow.

She pulled up to them and was immediately envious of their lunch. The food from the Chanticleer was delicious.

``You eat like this every weekday,'' she said to Fury. ``Tough duty. Hi Thomas.''

``Welcome back,'' Thomas said.

``Where's Toffy.'' asked Fury.

``Thank you, Thomas,'' said Hemlock, then looked at Fury. ``I left her at Oca and Ape's. She had a fever. She's fine now.''

Fury stared at her a moment and frowned. ``Hobby will ride up there,'' she said, shaking her head.

``No she won't,'' retorted Hemlock, dismounting, ``because she's fine now, and there's no point.''

She kicked out a small patch for Puer to graze and sat next to Thomas' rucksack on the third boulder. She took out her tobacco and started rolling a cigarette.

``What happened.'' Fury asked.

Hemlock glanced at Thomas.

``I'll tell you later,'' she said to Fury.

``I can leave,'' Thomas said, getting up.

Hemlock lifted her boot to block his thighs.

``Sit down, Lieutenant Shattering,'' she said, handing him the cigarette. He sat. She began to roll another for herself.

``Hemlock-.'' Fury started.

``She's fine, Fury.'' She locked eyes with her best friend and that was enough said for now.

She licked her cigarette to seal it. Thomas lit his, then hers. He always had matches.

Their shadows, never short this time of year, lengthened and swept across the meadow.

``He wants to draw us,'' Fury said and popped the last of her calzone into her mouth.

Hemlock turned to Thomas.

``You mean you haven't already.'' she said in mock surprise.

He blushed, but she knew he hadn't.

``I figured you'd already immortalised Fury puking on your boots.'' She looked at Fury, who was rolling her eyes. ``I'd be insulted, Fury.''

``I didn't puke on his boots,'' Fury said.

``No, you puked on mine,'' said Hemlock.

``I wanted to ask first,'' Thomas interjected. ``To draw you all.''

``Are you a spy, Thomas.'' asked Hemlock, narrowing her eyes at him.

``Maybe,'' he said.

He occasionally rose to banter, Thomas did, but he was not great at it. He smiled awkwardly. There were times Hemlock just wanted to pinch those Inuk cheeks of his.

``Iceland has spies in the Forest,'' Thomas said.

If it was an attempt at humour, it failed, and he wasn't cute to Hemlock anymore. She'd executed settlers. They all had. They'd burned entire villages to the ground. Their standing orders had red lines, and settlers crossed them from time to time.

``Maybe some are puppies,'' Thomas continued, looking down at his hands, his smile gone.

Hemlock coughed smoke.

Fury turned to ice.

Panthers! thought Hemlock, he just wanted to draw you, Fury. Now Thomas was lashing out--maybe more aggressively than he'd meant to--because he'd obviously asked her, and she'd probably just stared at him the way she does these days. Thomas was an idiot, but God on the Mountain, where was Fury's legendary grace?

Hemlock had actually thought Thomas had been good for Fury. She'd seemed more herself these past few months, her nightmares less frequent, conversations with her less odd. The staring, with eyes as empty as the Summer sky whose colour they shared, had continued, but that too was less frequent.

Fury looked at her briefly, and Hemlock nodded.

``Come on, Poo,'' Fury said, rising and walking over to Puer. She mounted him, which Hemlock knew pleased him, and spurred him, which Hemlock knew pleased him more. He reared and whinnied again, and they took off towards home.

``I-.'' Thomas started, standing. He looked at Hemlock. She shrugged. He sat and sulkily dragged his cigarette, staring after the place in the wood where Fury and Puer had disappeared.

``You ought to administer smaller doses of your notable charm, Thomas,'' Hemlock said to him. ``Tell me again how you came to be a diplomat.''





CHAPTER: Thomas Draws Hemlock, the Fox, and the Hare

A Snowy Clearing in the Forest, Afternoon



``Look who it is,'' said Hemlock.

Thomas looked up from his mope to see the fox and the hare walking toward them, emerging from the woods about thirty degrees North of where Fury and Puer had left the clearing. They had guitars tightly slung across their backs, and they alternated walking upright and trotting on all fours as it pleased them in the inscrutable manner of Forest creatures, responding now and then with frenetic energy to impulses and stimuli not evident to men.

Hemlock moved over to join Thomas on his boulder, scooching him with her hip. The archers were so lithe and graceful, it always struck Thomas how rock hard they felt, the few times incidental contact had occurred--he understood now their touch on human skin was basically fatal. It was strange to sit so close to one of them. Their headdresses were a thick, dark orange fur, with comically long pointed ears, themselves tufted with longer fur. Their polished hide chinstraps connected to the headdress in front of and behind the ear, supporting a stiff, moulded hide cup that covered much of the chin. Thomas looked at Hemlock's ear. It was a human ear, except for the long, bright white shocks of hair that grew from helix and tragus, stiff enough to suspend in arcs over the shoulders, soft enough to blow on the breeze. Hemlock's skin was a bit darker than Fury's; it was the skin of an outdoorsman, but looked healthy. The hair that spilled out from under her headdress was a thick golden blonde, the identical colour of Puer's main and tail. It fell in her face from time to time, but she didn't cut bangs or tie it up in back the way Hobby and Christoffel did. It just flowed like liquid straw onto her shoulders. Her eyebrows and the hair on her forearms was the same blonde. Thomas could see blonde hairs on her knees now as she sat crosslegged next to him.

The archers' white cotton shirts were a bit of a wonder to him. They rarely looked soiled. Hemlock would have ridden through the night, coming from Oca and Ape's workshop yesterday, but her collar was crisp and upright, the creases sharp and clean, the rolled sleeves likewise; they always wore their shirtsleeves rolled above the elbow. They never took off the uniform, he understood, and only ever bathed in rivers, lakes, and waterfalls, or in the rain. ``These are high quality shirts,'' had been Fury's explanation, running her fingers lovingly over the fabric of her rolled sleeve as she'd said it. They liked their shirts.

The tight black polished hide bodices didn't seem to need the straps over each shoulder, fixed with chased copper brooches. Embroidered copper crenelations ran along the suspender straps and the borders of the bodice, and glinted in the sunlight. Hemlock wore three copper squares suspended between her brooches. Everything was kept well polished.

An orange fur yoke topped the knee-length pleated tan skirt, a thick wool. Each archer had a buttoned slit up the right side of her skirt, from hem to yoke, to accommodate the hide straps that joined their quivers to their thighs. A few times now, Thomas had observed the strange procedure of attaching their quivers. The archer would wrap the long hide strap round her exposed thigh a specific number of times, fastening the copper buckles in a specific and practised way.

Hemlock's quiver was strapped to Puer, along with her bow, and was gone now. The way she sat now, the slit fell open, and Thomas could see stripes on her thigh, deep red impressions from the windings of the strap.

Thomas didn't know if they wore underwear.

The archer's knee-high boots were orange fur, their sharp, five-pointed copper spurs fixed with hide straps that joined in large copper rings on the outside and inside of each foot. Thomas looked down to see the embossed square pad on cross-legged Hemlock's soft left sole; each archer's symbol was also on their soles, leaving their mark in snow and mud.

Hemlock smelled like Fury. Maybe a bit horsier.

The fox and hare each climbed onto a boulder. They swung their guitars round to their breasts and began to tune them.

``They practice here sometimes,'' said Hemlock.

Thomas looked at the strange faces of the animals. Soon they would begin singing with human voices. It was diabolical. In six months Thomas had moved through moods of being transfixed by them to looking away, disturbed. He was watching with fascination as the fox repeatedly deployed his red leathery tongue to lick his own snout as he tuned the guitar, when Hemlock said: ``You can draw me.''

He turned his head to her.

``Sure,'' she said.

She sprang up, bumping him again, and hopped onto the fox's boulder, this time scooching the animal. The fox seemed untroubled by this, adjusting his own peculiar squat to give her room.

``Draw us, Thomas,'' Hemlock said resolutely, swinging into profile and leaning her back against the fox's side. ``They won't care.''

Thomas took out his notebook and pencils. He twisted round to look at the sun, enormous over the hills behind him, and judged a half hour remained of useful light. The three figures and two guitars in the bright clearing would make a nice picture. He'd leave out his own shadow and do his best not to imbue with any special harrowing significance that bit of the woods into which Fury had cantered off on Puer.

Why had he said that? Withstanding, as he imagined he had, each broadside blow of her rejection, crushing self-doubt nevertheless came in swells each time he came about before the fierce headwind her indifference ultimately, paradoxically, failed to provide. He had no line to tack amidst her polite deference, as calm and unconcerned with his denied ardour as are the Horse Latitudes with drowning horses. His passion was involuting into self-parody, into some kind of derangement that would invite only scorn or, of all becalmed states most wretched: pity.

He shook his head and set about outlining the forms of Hemlock and the two beastly guitarists.

The hare began a song in three quarter time, shanty-like. ``I am confident there never shall be a thing on this Earth as sublime as she,'' he sang. The fox joined him on guitar.

``We never know what he's on about,'' Christoffel had once told him. Thomas had joined the smallest archer a few times as she'd rehearsed with the Animals in the lodge on Sunday mornings. Hemlock and Fury were passed out or off getting sick. Hobby got her Sunday chores done early and then disappeared for the rest of the day.

``Sometimes his words seem to relate to us,'' Christoffel had continued, idly fingering the strings of her instrument. ``But not exactly, if you know what I mean. Other times it's just nonsense. As for the music-.'' she'd brushed her fingernails across the three strings in a brisk flamenco-like strum ``--oh, I get him completely. The right notes I reckon less as tones of particular lengths and pitches than as, for example, fish in a Forest brook, hovering in pools...'' her fingers arpeggiated some hovering fish ``...then darting about in some happiness only fish fathom...'' happy fish plucked across the strings ``...until fright overrules, then dispersing...'' a sustained low note followed by bright bell-tones skipping up the neck of the balalaika ``...now gathering in schools...'' a rich chord. She'd looked at Thomas, who'd been mesmerised by her virtuosity.

``Sometimes it's birds,'' she'd said.

Thomas smiled, thinking of daffy Christoffel. He watched his own hand dance across the emerging sketch, in a somewhat automatic obedience to his desired effect, the specific technique pure muscle memory. He'd put many hours into drawing. Still, he was always a bit surprised when one came out good.

This one was coming out pretty good.

``Nothing permanent,'' the hare sang, ``nothing transient, neither season nor reason.''

Yes, nonsense.

He knew Hemlock wouldn't speak while the animals sang next to her. She rolled another cigarette; he threw her a match, and she lit it.

``I don't understand how she makes me whole even as she tears apart my soul.''

Thomas posed the hare with his head thrown back in song.

``How she causes the dew-glazed leaves to shine, how she causes the streams to run with wine.''

He posed the fox mid-strum, regarding the viewer with the uncanny stare that even ordinary foxes possess.

``Oh, her play has a part for somebody's heart, and I'm confident it's not mine.''

He posed Hemlock as she sat, head cocked, looking at him a bit oddly, smoking, listening.

Thomas listened, too, as he drew.

``What estisi claims we can never requite, one of the roughs cries out 'If we don't we die!.''

Some mysterious allusions? Some Greek, too, maybe?

``We greet each morning with more foreboding, meanwhile, all around us, Spring is exploding. Oh, the swans are come, and the snows are gone, and the rapeseed hollers back up at the sun. Oh, bless this land, bless Her year after year, keep her skies and her horizons clear, bless the wind and the tides that brought us here and the rabbits out on the lawn.''

Thomas' hand stopped drawing. He looked up at the hare. The creature was singing about Newfoundland!

``As a boy I longed to bound with them cross the emerald hills of Newfoundland. Gave my heart to the sea when I found the Shore wasn't made for me, nor I for Her.''

He was singing about Thomas. He looked at Hemlock. She raised her eyebrows, aware. ``I don't know this one,'' she mouthed.

``No one wanted my opinion, yes, but again: I never asked for this. I am confident a mistake's been made: I'm partaking in a another's fate.

``Ariadne gave me a ball of twine, crossed sabres behind a ship-of-the-line, and sky-searching eyes, and sea-steady legs, and a longing heart, and buckets of faith. Oh, I found where I belonged, ere long, when I heard him speaking down in St John's on the Devil's strength, and the fight we are in, and how Death rides saddle by saddle with Sin. And however long the war rages on, I am confident we will win!

The fox sang a harmony for the refrain:

``As a man I pledged to be bound to him, our beloved King of Newfoundland. Gave my heart to the sea when I found the shore wasn't made for me, nor I for her. No one asked for my reaction, yes, but again I never asked for this. I am confident something's gone awry, and another's fate's been exchanged for mine.''

Now the fox sang alone:

``There's a voice in the wilderness, laughing and crying, a girl who will never, ever be mine, oh no, no matter what I do. To her, God is not just a word on a page, He stands her in placeand commands her by name, she is true, through and through. No, you can't love someone who's in love with a God, not even if that God is You.''

Now the hare sang alone again:

``Now I gather all my friends about, with his rabbit ears and his otter snout, and her kitten fangs and her sheepdog bangs, and her sadness and her madness. And the Fox fills the sky with the astral whine-.'' stunningly, the fox did just that ``--of a guitar hewn from pure moonshine, and the Fairy girls sing with one voice-.'' Hemlock shrugged, smiling at Thomas, and contributed a sustained harmonious ooh to the arrangement ``--irresistible to Animal boys! Oh, I choose to sing, but it's hardly a choice when you heart is filled with such joyful noise.''

The final chorus was rousing and full, all three musicians now connected to one another in their remarkable art, with which Thomas had become familiar but scarcely accustomed.

Thomas was transfixed.

``As a boy I heard this long before in the howling winds up in Labrador, saw a Fairy face in the blinding snow and three stars in an arc suspended below. As a man I swore I'd not come in, I meant even if asked, and I haven't been! I am confident something's out of place: my heart another's fortunes grace.''

The song ended.

``Well,'' said Hemlock, a bit breathless. ``How about that.''

Thomas' astonishment at the words of the song came as sparkles of reflected sun on the running brook of intimacy he felt running from Hemlock to himself. Her smile was intoxicatingly wide, her green eyes electrically bright in the setting sun. Needing to look away from her face, Thomas looked behind him and had to shield his eyes from the apocalyptic orange arbelos burning away atop two uneven hills to the West.

The animals, unaware of, or unconcerned by, or unimpressed with the human experience, proceeded into another tune, this one instrumental. The snowy meadow filled with the sound of their guitars.

Thomas turned back to Hemlock.

``What the Hell is going on.'' he asked her.

``I think it's my doing,'' she said, a bit sheepishly. ``I can find hidden doors.''

``What do you mean.''

She came to join him on his boulder again. The fox settled himself more comfortably as he played. Thomas and Hemlock watched the animals together, their own stretched shadows joining those of the animals to make a foursome on the field beyond.

``Look,'' Hemlock said, ``before I talk about that, have you considered it's chiefly aesthetic, your enchantment with her? That's what the World will suppose, you know.''

He'd known she'd known, this Fairy archer who maybe was becoming his friend, while Fury felt more remote every week.

Still, an at least perfunctory denial seemed appropriate.

``This is not a thing, Hemlock. I to her: flavour to Albion. I'm a naval officer-.''

She chuckled.

``--well, I am,'' he continued, but couldn't help chuckling himself. ``Such a thing, it's not...'' he trailed off. ``To me,'' he started again, ``it's sport. It's childish sport. It's subversion of duty.''

``One cannot but mis-measure flowers in dimensions of beauty,'' she said reflectively.

But he was lying. Nothing--not the King of Newfoundland, not singing animals, not the war, not Hemlock's grin--could put Fury out of his mind.

``I don't know what I'm doing here anyway,'' he said, putting his drawing away.

``Can I see.'' she asked.

``I'll finish it later,'' he said.

``None of us do, Thomas,'' she said. ``Know what we are doing here I mean.'' After a moment she said eagerly: ``I want to try those arrowheads.''

``What do you mean you can find secret doors.''

``Hidden doors, secret doors, yes. Um, there are two nearby. Do you want to see one.''





CHAPTER: Kim \& Asa Jump From an Airplane

A Military Aircraft, Early Evening



The special operations team was not happy about giving up three ``samaras,'' the winged fruits of some mountain-sized sycamore, presumably from some part of the DWF where such things grow.

``Each one of these costs a hundred thousand dollars.'' the team leader, a very muscular Chief Petty Officer, was shouting to Roos over the roar of the transport's engines. Roos and Kim and the team were assembled in the cargo hold with a crate stamped ``N\&LAFL.'' The crate was attached to its own samara.

``If you have another way of getting me down there, Chief,'' Roos shouted back, ``I'm all ears.''

``Ma'am, pay attention.'' the Second Class shouted at Kim, snapping her fingers in front of Kim's face. The young woman was not as muscular as her Chief, but just as salty. Her name patch read ``Comtois.''

``Yes, sorry.'' shouted Kim.

``Put these on.'' Comtois handed her a stiff hide helmet. Stuffed into it were a pair of hide gloves.

``That's it.'' Kim shouted, alarmed. She had expected some kind of full body protective gear over the flight suits and bomber jackets Roos had borrowed from the flight crew.

``That's it.'' Comtois shouted, smiling.

Other team members securing the lid of the crate, having stuffed into it Roos' and Kim's travel bags and rucksacks and anything Roos had been able to find onboard he thought might be useful for Lieutenant Shattering: some meals-ready-to-eat, blankets, a dry suit. ``I thought he was staying in a hotel,'' Kim had said. ``I need him to get out on the trail,'' Roos had said.

Kim hadn't even known the team was aboard. She'd been a little irritated by that. ``Is this like an extraction team or something, in case you and I were abducted? Were we in danger.'' Roos had looked at the team. ``It's pretty standard,'' he'd said.

Kim hadn't been able to appreciate the view of the Deep White Forest from the tiny window in the upper passenger area. When the rear door lowered, blasting her face with freezing wind, she was treated to a striking vista of the snowy Forest cast in orange by the low sun behind her, which the aircraft chased over the Western horizon. On the Eastern horizon, a pale blue crescent moon gently rocked.

``Chief, can you find this spot again.'' Roos shouted.

The Chief looked out at the terrain below, then up at the emerging stars, which were unfamiliar to all of them.

``Yes.'' he shouted back.

``I'm going to need you to make another drop here! I'll send you an inventory.''

``And a funding line.''

Roos gave the man a thumbs up.

``You'll be fine, Ma'am.'' Comtois shouted at Kim.

Two team members slid the crate off the ramp into the sky, its samara trailing. Kim gripped the stem of her own samara, wrapping one leg round its length as Comtois had instructed her.

``Don't grab above the swivel.'' Comtois reminded her.

Kim gave her a thumbs up.

She jumped.

She was in free fall for a few seconds before the giant leaves caught the air and began turning above her, slowing her to a gentle descent. They'd jumped from only three thousand feet, and the ground approached quickly. She saw the crate touch down near some trees at the edge of a farmer's field. Turning her head round, she saw Roos on his samara above and behind her, the aircraft climbing away aggressively behind him, turning back North. The sun had gone, and all was pale purple now. Stars were emerging.

``Land into the wind.'' Comtois had shouted at her. ``Unwrap your leg and slide down at thirty feet! Don't let go! When you touch down, walk forward! These are heavy.''

Kim remembered to do all that.

Roos, also uninjured, met her at the crate. They dragged it and the samaras under a large maple, opened the crate and retrieved their rucksacks.

``It's East,'' said Roos.

They started off through the snow.



CHAPTER: Hemlock Shows Thomas a Secret Door

A Snowy Wood, Evening



It had happened before, with Hobby, during a Hoot. The hare had sung about Hobby's time in Babylon. Hemlock and Fury had been stunned speechless. Toffy had wept openly and clung to Hobby in a desperate embrace. ``Poor Hobby,'' Toffy had cried, two words never before adjacent, at least not sincerely. They hadn't understood how the hare could have known such ghastly details about that harrowing experience without Hobby having told him, so they'd assumed she had. When she'd stared with her ice blue eyes at the hare, they'd assumed the look on her face was one of betrayal.

``But Fury quickly realised that Hobby was just as surprised by his knowledge as we were,'' Hemlock said.

She and Thomas walked on the trail back towards Three Nations. A number of farmers with donkeys and carts full of fencing materials had passed them, also a few hunters returning home. They'd all given them the subtle sidelong look Thomas now recognised.

They heard hooves, and two more hunters trotted by. One said a chilly ``Hello.''

Hemlock returned the woman's greeting.

``The hunters like us a little better,'' she whispered to Thomas.

``You were saying...'' Thomas prompted her.

``Right, so Hobby didn't kill him, the hare, obviously, which I thought was surprise enough. But then Fury further worked out the fusion with song--at least the hare's music--of my gift, my access, whatever you want to call it.''

She stopped, feeling like she needed to make this clear. Thomas stopped and turned to look at her.

``Thomas, right now I'm taking you to see a door,'' she said to him. ``An actual door. But-.'' she thought for a moment. How to put this? ``We know you call us 'fairies' sometimes,'' she said finally.

Thomas began to protest.

She held up her hand.

``No, Thomas, it's fine. And we know you call this place the Great In-Between.''

``I have never used that name! I-.'' he objected.

It took both hands this time to shut him up.

``I know, I know. No, Thomas, again, look, we are...oriented to frontiers, our race. I was made with a hungry mind that ever hunts contrivance, secret rooms, the backs of fronts. I feel along the edge of seem for the hidden catch that unlocks be. The articulated sconce, the bookshelf that swings wide. I see the mute gleam of recessed tracks upon which entire forests slide away, revealing other forests, other worlds.''

She felt she needed to explain this to gentle Thomas. The hare's intrusion into Thomas' life, into his boyhood--had unsettled the Newfy. It had unsettled Hemlock, too. What could the hare see about her own past, her own future--her own thoughts!--through the portals she herself opened?

``Whenever one of you makes an effort to make things clear,'' Thomas said, smiling, ``you obscure.''

She knew he meant it good-naturedly, and she was grateful: she preferred banter to all this earnestness.

``That's your limited aperture,'' she said. ``I think the retina of the human mind hosts one enormous diffraction pattern.''

He nodded.

``This way,'' she said, leading him on a small path that veered sharply off the trail and headed North. They were near Three Nations, but the rocky terrain here was unsuitable for homesteads.

``This is a deer path,'' she said over her shoulder to him. The path was too narrow to walk side-by-side as they had been doing. ``It climbs along a West-facing ridge, which a narrow draw cuts sharply. There's a stone bridge over the draw, have you seen it.''

``No,'' he said, now a bit breathless as they trudged uphill. ``Fury never took me this way. We are not far from the Chanticleer.''

``About a quarter mile,'' she said.

The path grew narrower, rockier, and more slippery. The well-travelled deer path was mostly clear of snow, but the mud would soon turn to mud ice, now the sun had set. Hemlock knew Thomas would have trouble seeing in the dark.

She heard as many as twelve or thirteen deer nearby. A fox. An ordinary one.

``We can build a fire under the bridge,'' she said to Thomas.

Before the path crested the ridge, she led him into the trees, going back downhill.

``Hemlock,'' he said, ``I can't really see anymore.''

She stopped and turned to him.

``Here,'' she said, ``give me one end of your scarf. Hold the other.''

He dropped the end of his wool scarf--knit for him by Toffy--into her hand. He was now careful to avoid physical contact with all of them. Hemlock found it amusing to alarm him with such incidental contact as he might be able to withstand. She had never laid a hand on a man other than to kill him, but she understood from Ekkorbok what the touch of an archer's bare palm on bare human skin, wherever placed, whatever its intent, could do to the human mind. She'd grappled with men in particularly thick melees--Puer kicking brains out of skulls nearby, sometimes within earshot of Hobby's axe splitting spines like firewood and Hobby's shouts rebuking the battlefield commander who'd ignored her instructions--but had overpowered and slain them too quickly to observe any psychological effect, apart from fear and grief, her touch may have enkindled prior to their death. The animals she touched all the time. They weren't people, and they were mad already, she figured.

She led Thomas down along the steep slope through narrow trees as the path rose above them. The Moon would not rise for another hour, and for Hemlock, colour was gone now from the land, except for a pale purple that lingered in the sky to the West. She knew Thomas now saw only blackness. He kept his mouth shut and kept up, though, heeding her warnings about slippery patches, nettles, low branches, and tight squeezes between trunks.

They reached level ground just as the slope turned to face North along the lower side of the draw. 

``What caused these ridges.'' asked Thomas.

``God,'' she said. She let his silent uncertainty linger a few seconds before saying: ``A glacier.''

He chuckled.

The trees gave way to rock as the draw narrowed, a brook running along its centre. She led Thomas by the scarf into a proper crevasse, spanned high above by an arched stone bridge supported by towering twin stone stanchions emerging vertically from the steep, rocky slopes on either side. She knew Thomas couldn't see any of this.

``Give me a minute to make a fire,'' she said to Thomas, throwing her end of his scarf over his shoulder.

``I'll stand alone here in the darkness,'' he said.

``Good,'' she said.

There were plenty of dead branches along the crevasse, some of them fairly dry. With Thomas' matches, she had a fire going in minutes. Thomas squatted by it and warmed himself.

``The Moon will be up soon,'' she told him. ``It should rise right along the crevasse. The door is there.'' She pointed at the wooden door with copper hardware at the base of the northern stanchion.

Thomas squinted at the door.

``What's in there.'' he asked.

``I don't know,'' she said. ``It's locked.''

Thomas looked disappointed.

``It doesn't seem very secret, Hemlock,'' he said. ``I mean, it's a funny place for a door. It's probably a storeroom for materials used to maintain the bridge.''

She walked over to the fire and returned with a burning branch.

``Do you see these letters.'' she said. She showed him the inscription on the door.

He looked closely.

``I don't recognise the symbols,'' he said.

``It's a very old writing system, used before the Forest existed, before He existed,'' she said.

He looked at her in surprise.

``Isn't it blasphemous to talk that way.'' he asked, concerned. ``Do you not consider God, your God, your Father, Lord Ekkor, always to have existed.''

``Yes,'' she said. ``This language is very old.''

``You sound like Christoffel,'' he said. ``What does it say.''

``No idea,'' she admitted. ``Can't read it.''

Hemlock heard uncertain, alien footsteps in the snow up on the ridge, approaching from the North. Two people in stiff boots who didn't know their way but had a destination in mind.

``Wait here,'' she commanded Thomas. ``I'll be right back.''

She trotted into the crevasse, knowing from the sound of their footfalls that these people would not hear or, if they did, recognise the sound of her spurs. She leapt onto the rocky northern slope and climbed nimbly to the top of the ridge just as the Moon rose. Through the trees she saw the two travellers, just now reaching the bridge, shining flashlights. She knew instantly they were Newfies.

She climbed back down into the crevasse and returned to Thomas.

``I think some friends of yours are here,'' she said.

``What-.'' Thomas started, but now the voices of the strangers on the bridge overhead could be heard clearly, reflecting down the stanchions, sounding uncannily close. The voices were wondering at the bridge's origin and engineering.

``My God, that's Asa.'' Thomas exclaimed in a hoarse whisper. He jogged out from under and looked up at the bridge, now prominent before the rising Moon.

``Asa.'' he shouted.

After a moment came the reply: ``Tom.''

Thomas looked at Hemlock with his big Inuk smile, his eyes glistening, his face bright in the Moon and the campfire. Hemlock saw for the first time how lonesome he was.

CHAPTER: Kimberly \& Asa Meet Hemlock

The Woods, Night



``Do they have the capacity to care for someone.'' Kim said to Roos, who walked a few paces behind her. ``Since they cannot die.''

``One wonders,'' he replied.

The sun had set, but the trail through the woods was reasonably wide and clear. The eastern star they followed, selected by Roos after consulting his little notebook filled with mysteries, now came into view, now hid behind the bare trees as the trail wound.

Now the trail narrowed and rose sharply. On the airplane, itself a diplomatic territory, they had tried to rid themselves of any metals that weren't copper. But there was nothing to be done about the steel in the toes of their boots, and so they'd made some other allowances, among them flashlights, which they now used. As the trail topped the ridge, the Moon peeked up over the horizon. Kim had picked out where she thought the Moon would rise and was pleased to be vindicated. Roos had more years in the Navy, but she had more years at sea, the older Commander having moved into the diplomatic branch early in his career.

They followed the ridge round a gentle southerly curve and found themselves before an arched stone bridge, stark in the moonlight.

``Who built this.'' wondered Kim.

``It's old,'' replied Roos.

Breeze had kept snow from gathering on the stones of the bridge itself. Kim stepped onto the walkway and peered over wall on the moonlit eastern side. The stone supports below descended into a deep crevasse.

There was a light down there, under the bridge, as from a small fire.

``It's a strange design,'' said Asa, walking toward her.

``Sir...'' Kim said.

``Asa.'' a voice cried from below.

Asa looked at Kim, his mouth an O, his eyes wide in mock alarm; the hair stood up on the back of her neck.

``Shattering,'' Asa announced to Kim. He then leaned over the wall and called out: ``Tom.''

``Wait there, we'll come up.'' the voice from below called up.

Kim heard the ``we'll,'' and her body tingled with excitement. She was, she hoped, about to meet a Daughter of Artemis.

``Steady,'' Asa said to her, but he took off his watch cap and tidied his hair.

Kim took off her own cap. They stood together on the bridge in the moonlight, their shadows strokes of ink across the frosted stones.

Over the bridge, a little ways down the path ahead, two figures emerged from the trees. They approached the bridge, and Kim saw a lanky, aristocratic, gentle-faced, half-Inuk officer of her Navy accompanied by a lankier, head-dressed, blonde, broad-shouldered woman in the uniform of Lord Ekkor's Mounted archers. She was as tall as he, her headdress making her seem a great deal taller. The red fur she wore was muted in the moonlight, but her eyes shone with their own light, a transfixing lime green, almost electrical. Plumes of soft white hair arced from her ears over her shoulders, lofting like wings as she walked. She was beautiful.

Kim swallowed nervously. She looked at Asa, whose lips had all but vanished leaving just a straight line where his mouth had been.

Lieutenant Shattering was covered, and he saluted Roos before the two men shook hands. Not an embracing sort of friendship, Kim thought.

``Hi Asa,'' said Tom. ``May I present Hemlock of King Ekkor's Royal Mounted archers. They don't salute, and you can't shake her hand.''

``Lieutenant Commander Asa Roos,'' Asa said. ``This is Lieutenant Junior Grade Kimberly Jack.''

The beautiful archer, whose feral, blonde eyebrows were very expressive, regarded them.

``Hello,'' the archer said to Kim. She looked at Asa. ``Are you supposed to be here.'' she asked him, smiling. Kim picked up the Brabant accent.

Asa produced the small brown envelope Daniel had given him at the Vedauwoo air terminal and handed it to Hemlock. She looked down at the seal then back up at Roos. ``Ah,'' she said. She tucked the envelope into the waistband of her skirt.



Kim walked beside Hemlock as they made their way to Shattering's hotel. The two men followed a few paces behind, engaged in their own conversation, which Kim had overheard commencing with Shattering's whispered ``What the Hell are you doing here.'' The gibbous Moon, now well above the hills, cast shadows of bare branches, segmenting the snowy trail into irregular white patches and black borders.

``It's beautiful here,'' she said to Hemlock, tears in her eyes. To be able to talk to this creature was overwhelming.

``Are you alright.'' Hemlock asked her.

``Yes,'' Kim said. ``I'm crying, ha ha,'' she wiped her eyes, ``because I wasn't sure I'd ever meet someone from...'' she spread her arms ``...here.'' She turned her head to look up at Hemlock, who was a good six inches taller. ``You are the most extraordinary thing--uh, person--I have ever seen.''

``I doubt that,'' said Hemlock. ``You were in Vedauwoo.''

Kim remembered Bickle and Pupkin.

``Loveliest, I should say,'' Kim corrected herself, then turned her head and sniffled away her embarrassment at her own gushing.

``Thank you, Kimberly,'' said Hemlock.

``Please will you call me Kim.''

``Kim.''

``I've read everything about you,'' Kim offered, the floodgates now open. ``About your legion, I mean. Everything that's written in Newfoundland and Labrador, which is not very much. But none of you were in Vedauwoo. I had thought to see vast regiments on the parade grounds.''

Hemlock laughed. ``No, not in Vedauwoo,'' she said. ``They should have taken you North.'' She patted her headdress. ``Oceans of red hats.''

``It's magnificent,'' Kim said of the headdress. She looked down at the rest of the uniform, the bared knees and rolled up sleeves in particular. ``You don't get cold.''

``No,'' Hemlock said, ``we know you find it strange. Our bodies are hotter than yours. A few degrees. Summers are Hell.''

Kim laughed.

The walk to Three Nations took about thirty minutes. In that time Kim learned the following from Hemlock: there were only four archers here, hundreds of days by horse from any other; the four had not been to war in some time, maybe five or six years; meanwhile, they performed patrols throughout the Southern region of the Forest, sometimes ranging as far North as the dense woodlands between Waccabuc and Vedauwoo, and very occasionally circling His Mountain at a constant and distant range to venture into the East; rarer still, a very long patrol might take them into the North; they had in the past suppressed small rebellions amongst the Settlers, who were billed by Vedauwoo for every tree felled, every animal slain, and every gallon of water consumed; the mining or use of any metal other than copper was illegal; also, the four archers made music in their barracks lodge with a troupe of woodland creatures.

``What.'' asked Kim.

``I don't think we prepared gentle Thomas for that,'' said Hemlock, ``so I thought I'd let you know. In case you come to the lodge. I hope you will.''

Bored and lonesome is not how Kim had expected to find Ratatoskr's famous mounted archers, but the eagerness in Hemlock's voice was unmistakable.

The woods were thinning as they approached Three Nations. Lights could be seen in cottages. There was a smell of roasting meat on the air. Distant music, maybe? A donkey brayed.

Kim leaned toward Hemlock and whispered: ``Gentle Thomas? Is that what you call him.''

``It's not an insult,'' Hemlock said. ``Is it offensive.''

``No,'' said Kim. ``I mean it might be to him.'' She glanced back over her shoulder at Shattering who talked earnestly with Roos as they walked. ``I don't know him.''



CHAPTER: Thomas \& Asa Discuss Thomas' Mission

The Woods, Night



``What the Hell are you doing here.''

Thomas hadn't expected to see anyone from Newfoundland \& Labrador until Spring, if that soon, and not here in the Deep White Forest. And not Asa, who was comfortable and masterful in meeting rooms and cocktail parties, but was even less of a field operative than Thomas. The young Lieutenant, Kim, looked tougher, though as she walked next to Hemlock in front of them, Thomas was struck by the side-by-side comparison of Newfy and archer. Hemlock's height, broad shoulders, and impossibly slender frame in a bodice and skirt next to this shorter, curvier human woman in a flight suit and bomber jacket gave the impression of a couple cross-dressed.

It was a strange feeling, having them here. He acknowledged within himself an odd pride of association with the archers and suddenly a selfishness.

``How did you get in.'' he asked Asa.

``How did you get in, Thomas.'' Asa replied in his typically sardonic tone. ``This is what everyone is wondering. Was it Haystack, here.''

``Hemlock.''

``Whatever. She met you in the meadow.''

``No it wasn't her.''

``So you've met others.''

``There are four of them.''

``There are billions of them, the Two reckons,'' suggested Asa, using the shorthand for the N2, Naval Intelligence.

``They're a unit,'' Thomas said. ``A squad. They call it a Square. I have reports, Asa. I have no way of sending them out.''

``Well, we're going to fix that.''

They walked in silence for a bit, listening to the murmur of Hemlock up ahead as she spoke to Lieutenant Junior Grade Jack.

``Jack, as in....'' Thomas said.

Roos nodded. ``His daughter.''

``Jesus,'' said Thomas. ``Asa, what's going on? Why her.''

``She's at the University.'' Asa nodded towards Hemlock. ``She's doing a thesis on them. She's beside herself right now. Are they all that tall.''

``Taller. The one called Hobby, the squad leader, is towering. Only one is shorter than I. Christoffel.''

``I have news about your father,'' Asa said. ``He's doing well. He's recovering from surgery. He's back home. Your mother-.'' he looked at Thomas with a guilty smile, ``--wishes you would write.''

Thomas stopped. Asa stopped a few paces later.

``Asa,'' said Thomas, ``why are you here.''

Asa walked back to him and produced another envelope, this one with their own King's seal.

``I have orders for you, To.'' he said.

Thomas was struck with dread: Jack was here to replace him. Fury's face filled his mind with such vividness he had to shake his head and blink the vision away. He knew Asa could read him and was never slow to understand things, so it didn't surprise Thomas when his friend said:

``No, you're not getting fired. You're taking them to Germany.'' He thrust the envelope into Thomas' hand. ``Walpurgisnacht.''

Thomas looked down again at the envelope. ``You're kidding,'' he said. ``I'm taking them, to whom all metal but copper is  sacrilege, to a weapons fair.'' He levelled his gaze at Asa. ``Your idea.''

Asa got irritated, which pleased Thomas at the moment.

``Oh, it gets better, buddy,'' Asa said sharply. ``We're handling the movements. So however the God King spirits them off to Syracuse or Thessaly or wherever--how do they do that, Tom.''

``I have no idea,'' Thomas blared back, turning his palms up to the sky.

``However they do it, it's not available to you, so you are going to shepherd them through our system. Them and their horses.''

``Are you serious.'' Thomas cried.

Hemlock and Jack had left them behind, but Thomas was suddenly past caring if their raised voices were overheard. He knew there were many things Asa was cleared to know that Thomas himself was not. It had been that way for a couple years. Nor did he mind taking orders from his friend. Asa seemed to always know what was going on in the Navy--in the country--while Thomas had to admit to himself that he really hadn't a clue. Nor did he really care. He had just liked going to sea, and now he liked going to front office parties. But Asa showing up here with the daughter of the Chief of Navy meant Thomas had been kept more in the dark than usual.

``And what do you mean, you've no idea.'' Asa said. ``What have you been doing here with your friend Haystack-.''

``Hemlock.''

``And Bobby and Christabel-.''

``Hobby and Christoffel.''

``Right, what did I say? Have you learned any--wait, you said there are four.''

Thomas could feel his heart pounding.

``Who's the fourth.'' Asa asked suspiciously.

``Do you mean her name.'' Thomas asked, his voice wavering, as he'd known it would.

Asa peered at him askance. ``Yeah, Tom, what's she called.''

``Fury,'' Thomas said, straightening his spine. ``She's called Fury.''

After a moment Asa's hard look cracked into a mocking laugh.

``Oh no. Oh, you're kidding me, Tom.''

``What.'' Thomas asked in useless denial.

``Do you know how hard I had to push to get you this assignment, you jackass? And now I find you beguiled by and soppy over some fairy archer lass. Are they even lasses, Tom? My God, I can see it in your eyes, buddy, you don't care what they are. You're in love.''

Thomas stood firm and kept silent, but he realised his eyes had filled with tears.

Asa shook his head.

``I mean, wow,'' Asa said, ``that one-.'' he pointed down the trail where Hemlock and Jack had disappeared round a bend ``--is pretty hot. This Fury must be...'' he trailed off.

Asa leaned in and saw Thomas' tears.

``Oh Jesus Christ,'' Asa said. ``Go ahead Thomas, tell me about lovely Fury.''

Thomas exploded.

``Do I say she is lovely.'' he shouted. ``No! 'Tis heresy.'' He walked off down the trail, then turned round dramatically. ``You know, for all her gentleness of form as taken in from such distance as courtesy compels, up close she is a beast. And warm, unaccountably warm she is, though storm of wind and ice this wretched sky doth thrice excite fortnightly, does she burn.'' He paced to and fro cross the trail as he ranted, tears flowing freely now. ``And swarm with ticks, Asa, did you know? She has lice and the slick of musk oil on her hide. Mice dorm in her headdress, I'll warrant, and plagues by vermin borne infect her ears and eyes and I'm sure her blood.'' He stopped pacing and looked up at the waxing Moon, where the hare with his guitar stood waist-deep in the lunar night. ``And she seldom bathes.''

Thomas looked down from the heavens to find his Scandinavian supervisor staring at him with authentic pity. Asa put his hand on Thomas' shoulder.

``She is the exact cancellation of beauty,'' Asa said.

``Aye,'' Thomas said. ``In faith, she is abominable to me.''

For a moment they stood in the moonlight not speaking.

Finally, Asa said: ``We should catch up.''CHAPTER: Kimberly \& Asa \& Hemlock \& Thomas Have a Drink

Three Nations, Evening



Kim figured Roos had been briefing Shattering or Shattering had been briefing Roos. And they were old friends. The two men jogged up to join her and Hemlock just as the woods gave way to the small farms surrounding the village of Three Nations. The village sat in a shallow valley, and Kim could see the village square had been taken over by a Christmas market, with hundreds of Settlers milling about stalls selling crafts and meals. They could hear the Settler band clearly now, playing a reel.

``Christmas,'' said Hemlock, smiling at Kimberly, evidently thinking this would please her. It did, but not as much as Hemlock's smiling face: Kimberly was enchanted with her. ``I would dance.'' Kimberly had told her mentor, drunk in the Hourglass one Christmas ago, ``I would drink or smoke whatever they put in front of me! And I would climb above the canopy, and I would shout My name is Kimberly.'' She wanted this lanky elf for a sister, and she would happily dance with her. She'd embrace her right now if the archer's hands on her skin wouldn't stop her heart.

Their entrance into the village proper was heralded by a folksong whose lyrics Kim quickly recognised as a fusion of Eddic and Christian mythologies. She looked round at the mutely cheerful, simply dressed Settlers. These are all Icelanders, Kim thought, though she knew their point of departure from the destiny of the modern maritime republic she and Thomas knew as rival and occasional enemy was located hundreds of generations in the past. They glanced at her, attempting, she assumed, to assess her connection to the tall archer she accompanied, and they kept their distance as the foursome approached the Chanticleer.

At the reception desk, Hemlock and Shattering spoke to a woman called Ilsa who seemed to be in charge, and Roos and Kim were given room keys.

The bar was decorated for Christmas. A barmaid led them to a table against the wall.

The men averted their gazes, but Kim sat and watched in wonder as Hemlock parted her skirt and unwrapped the windings of her quiver strap. Stripes of red skin and missing hairs on her thigh attested to its tightness. ``I know, it's weird,'' Hemlock said to her, smiling. She sat on the cushioned bench next to Kimberly, leaning her quiver and bow between them. Roos and Shattering took the chairs opposite.

Ilsa brought their drinks over herself, glühwein for everyone except Hemlock, who'd ordered a tall, icicle-chilled cocktail made from vodka and banana liqueur.

``I don't come to town often,'' she said to Kim, grinning as she sipped the drink. ``Fury deals with the hotel.''

``She's your squad leader.'' Kim asked. She was trying to keep the archers straight in her mind, but she'd already detected Fury was important to Hemlock.

``No, that's Hobby,'' said the archer.

Kim could not help her eagerness. ``Could they all join us.'' she asked, glancing at Roos, whose ambivalence about the idea was obvious. Thomas looked away. If Hemlock's demurral owed to the men's reactions, the sweet-faced archer didn't make it obvious.

``Hobby and Christoffel won't be back yet, and Fury will be getting the lodge ready for the, um...''

Hemlock's eyes now fixed on Roos, who was idly looking round the bar at the other customers.

Kimberly turned her head and stared for a moment at the archer's pupils, bright as Christmas, an impossible green. Those eyes, the cheerful grin, the blonde hair spilling out round her cheeks, the headdress with its comically tall tufted ears, and the four arcing plumes of bright white hair from Hemlock's own ears, surrounded and lit by candles and Christmas decorations, with a sparkly summer cocktail set before her, it all gave the impression of an explosion frozen in time. When those green eyes fixed suddenly on Kimberly's own and subtly widened she was unprepared.

``Oh, excuse my eagerness,'' Kimberly managed. ``In general I am behaving like a tourist.''

She looked at Shattering, who slouched a bit and was generally unimpressive, though he had a handsome Eskimo face. Hemlock sipped her drink through a straw, still grinning. When in silence Kimberly, Asa, and Thomas all raised their glasses to their lips in awkward accidental unison, Hemlock's grin widened. Roos, so elegant at high levels, was useless among the troops, thought Kimberly. And Thomas Shattering? His drawings had better be good.

``Kukuleku.''

Kimberly jumped.

A Settler boy in overalls with a syndrome-y face had snuck over and leaned to within inches of her ear and crowed like a rooster. Asa and Thomas had also been startled, but Kimberly registered and was immediately comforted by the only slight, and entirely unconcerned, dimming of Hemlock's grin. The archer's eyes told a story of thousands of years of quickly assessing threat; here they'd found none.

A red haired, bearded man in a tattered brown suit with a banjo slung over his back hurriedly approached and put his hands on the boy's shoulders. ``He thinks he's a rooster.'' The man was rather handsome, of humble means, a farmer by his hands, and evidently in his best clothes for the Christmas market. Like most Settlers, he had that odd Icelandic accent, evolved over millennia in isolation. Kimberly found it pleasant, though not as charming as the tinkling-chimes-over-bass-flute of Hemlock's Flemish inflection.

``Come,'' the man in the suit said, gently but firmly steering the boy away from the table.

``No, it's okay,'' said Kimberly. ``He just startled me.'' She looked at the boy, and said: ``Hello.''

``Kukuleku.''

``Is he your son.'' Kimberly asked the man.

The man looked embarrassed. ``No, no,'' he said, looking down at the boy with pity. ``He has no parents.''

Ilsa appeared with an anxious look on her face. ``They're musicians,'' she said to Hemlock in the tone of an excuse. ``From up North.'' She nodded toward the other side of the room. Kimberly now saw that across the crowded room a pair of stools sat beside a double bass and a small drum kit.

``When do you start.'' Hemlock asked the red-haired man.

``Soon,'' he said. ``Now.'' He looked at Ilsa. ``Now.''

Ilsa nodded.

The man looked back at Hemlock.

``Now,'' he said with a smile.

Another round of drinks arrived as the little band settled in. The red-haired banjo player and the boy in overalls were joined by an old Chinese man on the double bass and another farmer--also in overalls, and wearing a straw hat--on the drums. ``From up North,'' Ilsa had said. Kimberly associated the presence of the Chinese bassist with an impression she was forming of Vedauwoo, galactic spa and tax-haven, leaking the occasional non-Icelandic immigrant into the greater Forest.

``He took the rotundity of the Moon,'' the red-haired man sang, at first a cappella, then with the band joining on ``Moo.'' for a lightly swung ballad, the drummer and bassist harmonising with ``oohs.'' Kimberly leaned her elbows on the table, cupping her hands round the fresh glass of whisky. ``And the curves of creepers,'' the song continued, ``and the clinging of tendrils...'' It was beautiful. Rooster boy didn't appear to have a musical role in the band. He sat on the stool beside the red haired man and swayed, a vacant look on his face. ``...and the trembling of gras.'' -- ``aah.'' now from the rhythm section -- ``and the slenderness of the reed, and the bloom of flowers, and the lightness of leaves, and the tapering of the elephant's trunk...''

``This is not a Christmas song,'' Asa said, causing Hemlock to snort banana cocktail out her nose. Kimberly laughed and handed her a napkin, crying ``Oh my God, here.''

``Sorry,'' said Hemlock, wiping the table then her face. ``That's pretty gross,'' she giggled.

Asa didn't exactly smile, but his eyes sparkled.

Kimberly looked across the table at the sulky Thomas Shattering. What was wrong with this guy?

``Shattering, you alright there.'' she asked him in the challenging tone of a shipmate. He was slightly senior to her, but he didn't strike Kimberly as the type to assert anything but his own talent and experience, such as it was. Which is to say she got an ungrudging good feeling about his character, despite his moping. Also he was friends, apparently, with Roos, which struck her as a privilege in their Navy.

``He lives here,'' said Hemlock, still sniffling banana, her eyes tearing, ``I'm embarrassing him.''

``Has he been a good guest.'' asked Roos.

``We are very fond of Thomas,'' she replied.

``So he's not a lot of work for you.'' Roos pressed.

``Well,'' said Hemlock, ``I'm not his minder. Fury...''

``...and the fickleness of the winds,'' came the song across the quiet murmurings of the bar's cheerful holiday patrons, ``and the timidity of the hare...''

Hemlock had paused and glanced at Shattering. Roos' non-smile had taken a sardonic turn. Shattering had focused more intently on his drink, his own lips tightening.

Kimberly figured it out. Thomas Shattering had ``danced with the fairies,'' or at least he wanted to.

She looked at Hemlock, who met her gaze but held a steady expression, despite another sniffle.

So here we are, Kimberly thought, all four now knowing a thing, knowing all the others know, and no one wishing to speak it aloud. It was oddly bonding.

As Roos treated an attentive Hemlock to a brief history of Newfoundland \& Labrador's rise to global maritime dominance, starting with the tale of Jenny Uqaliq, the housemaid of Signal Hill, Kimberly considered the woman beside her. A person could desire this creature, she supposed--people could desire anything. Kimberly herself had never been in love nor particularly lustful, and the two men who'd presumed to call her ``girlfrien.'' were now lost to space and time, belonging, whatever their virtues, to the set of things obscure and remote to her more certainly than she had ever belonged to either of them.

She'd reserve judgment until she met the other archers, but there was nothing soft about Hemlock. As she sat now, a bit hunched over the bar table, she arced in long, rigid segments, the tight hide bodice just supple enough to reveal how rock-hard was the slender body beneath it. Hemlock's square face was very pretty, but Kimberly thought its mischievous, friendly character more capable of flirtation than actual seduction.

``They are virgins,'' her mentor had told her. ``Think of them as nuns. Warrior nuns.''

Light but enthusiastic applause attended the finale of the little band's first song.

``Thank you,'' said the red-haired singer, removing his jacket and rolling up his sleeves. ``Here's one from over the sea.''

``Qin de ha, qin de ha, qin de ha,'' the Chinese bassist began singing in a monotone, to which Rooster boy, after a few measures and in his debut that evening, added ``dicky-dicky-doi-doi, dicky-dicky-doi-doi.''

What followed was a hallucinatory biography of a hapless Newfoundland man who had for his own pleasure imported from the Deep White Forest copper ore, a Fairy bride, and an animal band. It seemed to amuse Roos, unsettle Shattering, and make Hemlock ashamed.

``Thomas,'' Hemlock said, ``I'm sorry about this.''

Confused, Kimberly asked her: ``What's going on.''

``Never mind,'' said Shattering.

``It's hard to explain,'' said Hemlock.

``Qin de ha, qin de ha, qin de ha, dicky-dicky-doi-doi, dicky-dicky-doi-doi.''

As the red-haired man plucked away at the extended coda of the sprawling number, Kimberly observed a sizeable globule of his flesh drip off one bare elbow and plop onto the wood floor at his feet. The globule immediately began to writhe and develop rolling eyes and a gaping mouth, which puled miserably.

Roos and Shattering were struck simultaneously by the edge of the tabletop as it slammed into their chests. They fell to the floor, winded, the overturned table atop them. Kimberly's drink landed in her lap. Hemlock stood where the table had been. The traces of her arms having wielded her bow, pulled an arrow, and knocked and loosed it seemed to linger in Kimberly's vision. The arrow now lodged in a framed landscape of a hunt behind the red-haired man, upper lip and teeth were now gone. The snap of the bowstring, the crack of the copper broadhead separating the man's spine from the base of his skull, and the thwack of the arrow's impact into the canvas had all merged in Kimberly's ear, scarcely to be isolated. The man's bright blue irises had been consumed by his pupils. He dropped to the ground in a heap beside the wretched globule, still lamenting its own hideous parthenogenesis and growing in size.

Rooster boy's expression snapped into a hateful consciousness and intelligence the idiot face hadn't possessed before. Meeting Hemlock's gaze, he gave a wry smile and cocked his head back. Her arrow entered his throat, separated his brainstem from his spine, and lodged in the drummer's upper arm. Rooster boy spilled off his stool onto the floor beside the red-haired man.

In the exodus of the other patrons from the bar, Kimberly observed the muted panic of a habitually repressed people. She felt the whisky soaking into her lap, stinging. She looked up at Hemlock, who stood in a pose from an urn, and with an expression she'd have to describe as divine.

The face on the sickly pink blob was now fully formed. Its dull eyes looked round the room, its mouth gaped moronically. With revulsion Hemlock concluded that Rooster boy shared its loathsome pedigree.

Shattering righted the table in his own rising and helped Roos to his feet. Both men regarded the inert musicians and the blob.

Roos looked at Hemlock, who came out of her trance and explained: ``Devils.''

Kimberly met Roos' gaze.

Ilsa appeared with a sack. Hemlock took it from her and poured what looked to be salt over the blob. It perished in agony.

``Can you get my arrow.'' she asked Ilsa.

``Yes,'' Ilsa replied, ``we put him in a guest room. He's not a Devil. Neither is the Asian fellow.''

``Thomas, would you mind.'' Hemlock said to Shattering.

Thomas nodded and followed Ilsa out of the bar.

``What does this mean.'' Kimberly asked Hemlock.

The magnificent archer wrinkled her brow, then shook her head. ``It happens,'' she said. ``I mean, they're around.'' She looked at Roos. ``Not usually here, though. I don't know.'' She looked round the room. ``Hobby and Fury will have to sort things out with Ilsa and the Settlers. They'll probably want to have some kind of meeting.''

``What did they want.'' Roos asked.

Hemlock shrugged. ``Mischief,'' she said. ``Let's go to the Lodge.''

Kimberly looked at the bodies and the black puddle where the blob had been.

``Don't worry,'' Hemlock said to her. ``Ilsa knows what to do with them.''



CHAPTER: Hobby Considers the Situation

The Barracks Lodge, Night



``Accountin.'' was the final section of her monthly report, but apart from her executive summary, Hobby imagined it was the only one read by HCF. The summary hadn't changed in sixty months: no major developments nor threats in her area of operational responsibility. The shape of that area, with its tendrils of long patrols, some absurdly convoluted, many omitted for secrecy, was the feature of the page facing the summary, and it bore no red symbols, month after month.

``Accountin.'' was unremarkable, the four archers having brought the barracks lodge to self-sustainability within weeks of taking it over. Coin-boxes arrived at Oca and Ape's every month. They were stacked in the lodge cellar. The archers hadn't opened a single one. Fish, firewood, and fresh water were their currency with local Settlers, and the occasional deer, and elimination of pest bears or big cats. For fifty-seven months Hobby had included her recommendation that their water ration be reduced by three quarters: they were four in a station built and budgeted for sixty. Meanwhile, they traded the surplus and hoarded the coins, which the Settlers valued but were made insane by possessing.

Hobby heard Puer cross the bridge. Not Hemlock astride him, Fury rather, and with a burden. Hobby's gut tightened. She looked over the report once more, initialed each page, and signed and chopped the summary. She was affixing her seal when Fury came in with a breeze that disturbed the candles.

``Where's Hemlock and Toffy.'' Hobby asked.

``Hemlock's with Thomas.''

Hobby heard the edge in Fury's voice. Fury was moody. Hobby didn't know how to handle it.

``Toffy's at Oca and Ape's. She's got a fever.''

Hobby stared at Fury, whose expression softened.

``It's fine, Hobby. It's nothing.'' Fury glanced at the papers in front of Hobby. ``Doing the books.''

``Done.'' Hobby blew out the candles and closed up the desk.

Fury put a log on the fire and flopped onto the sofa.

``Hoot tonight.'' she asked, putting her feet on the coffee table.

``I suppose so,'' said Hobby. She looked out the window. The sun was already down.

She sat next to Fury and matched her pose, ankles crossed, soles to the fireplace.

Fury looked about them, then sat up a little, craning her neck to look round the hall.

``Did you clean.'' she asked. ``I was going to clean.''

``Yeah,'' said Hobby. ``Felt like it.''

She felt Fury looking at her.

``She's fine, Hobby.''

``I know.''

They watched the fire in the dusk. A painting of a red mask with tufted ears hung over the fireplace. It represented their Father. It hung in every house in the Forest, or was meant to. Around the chimney breast: shelves and shelves of Ekkorbok in red hide bindings.

``Do you want to read a bit.'' Fury asked.

``No thank you,'' said Hobby.

They chuckled together.

Fury took her hand. Hobby felt the warm, rough palm and felt peace filling her heart. Fury's hands were as big as Hobby's, and just as capable. More capable with a bow.

Hobby was worried about Christoffel, but she was more worried about Fury, whose knees were torn bloody, and who's face bore the signs--signs Hobby knew--of hiding something.

``We're lucky, Hobby,'' said Fury.

Hobby was struck by an unexpected wave of hope.

``For the Animals. Don't you think? To sing and play with them.''

``You know I agree, Fury. If I seem reticent,'' with her free hand, Hobby pointed at her own chin, ``it's just my face.''

Fury smiled. ``I took a deer on the way back,'' she said.

``I thought so.''

``I took him on the run, east of the trail.''

``Dense wood there.''

``Aye, and Puer can pour it on. But he sees, like the hart does, paths between the trees I can scarce anticipate. Look at my knees.''

``Yeah.'' Hobby considered Fury's kneecaps, whose flesh now decorated the barks describing the path of her hunt. The tops of her boots were soaked in blood. ``Gross.''

``Aye. But with Puer steering the chase, my thoughts were liberated to the volume of curves, rectified undulations twining round each other and the shaft's unswerving secant as our destinies--the hart and mine--drew together to meet at the leading edge of the broadhead.'' Fury leaned her head forward and tapped the back of her neck. ``At the kill.''

Hobby was nonplussed.

``Fury, are you alright.''

Fury's face showed disappointment.

``I'm sorry,'' Hobby said.

``Hobby...''

``I know, I know, I'm sorry. I know the figure you mean. One-five-one-five-eight-.''

Fury smiled. ``Whatever.''

Hobby had momentarily betrayed a compact she and Fury had made years ago: that their private discussions of Ekkorbok be devoid of sentiment. Each of the archers, Hobby knew, had their own way of finding meaning in the monstrous text. For Christoffel it was a frenetic and ecstatic celebration of its poetics. For Hobby herself, it was an encyclopaedia she'd memorised. For Fury it was a perpetual rediscovery of her own nervous system, teased apart by their Father's surgeons, filigreed and pressed between the innumerable pages. Hobby's knowledge of those charts made her a singular pilot upon the oceans of Fury's humours, except where there were dragons.

Hobby squeezed Fury's hand hard.

``Ow.'' Fury cried. She stared at Hobby, her eyebrows in a vee.

Hobby stared right back.

``I know the figure you mean,'' Hobby said.

They heard the party on the bridge. Hemlock and Thomas, both tense, and two strangers on foot.

In moments, Hobby and Fury were armed.



Outside, Hemlock appeared from the darkness, followed by Thomas and two blonde Newfies. Asa Roos, Hobby figured from Thomas' descriptions, and a woman, both in flight suits.

``A Devil, I'm guessing,'' Fury whispered.

They stood in the snow as Thomas presented Commander Asa Roos and Lieutenant Junior Grade Kimberly Jack. Hemlock recounted the incident at the Chanticleer.



CHAPTER: Kimberly Attends the Hoot

The Barracks Lodge, Evening



The ones called Hobby and Fury were very tall and broad-shouldered, and the image of the two standing with their bows at the ready before the lodge, combined with that of Hemlock's ruthless shot in the hotel bar, convinced Kimberly of the might of Ekkor's forces. If there were millions--some said billions--of these archers, then who could oppose the Forest King's will? A permanent alliance with either St Johns or Reykjavik was doom for the one forsaken.

``His daughters are His only native force,'' Asa had said. ``Everyone else you see, even the top brass, even the COS, are leased from abroad.'' Mr Bradfield had confirmed: ``If it doesn't ride a horse and shoot arrows, it's fighting for a pay check.'' To that end, each archer was herself also precious barter. How many were fighting abroad? And where? And for what cause?

``Will the hotel clean up the mess.'' Hobby was asking Hemlock. Kimberly picked up Hobby's critical tone, as well as Hemlock's indignation.

``I brought them here,'' Hemlock said, indicating Roos and Kimberly herself, ``to get them out of Ilsa's way for a few hours.''

``It's been a while, eh.'' Fury remarked to Hobby, who nodded grimly.

Fury then approached Kimberly, bow lowered, her other hand on the stars that hung between her brooches.

``I'm Fury,'' said the bespectacled elf, whose pupils were an unworldly blue. ``It's nice to meet Thomas' friends.''

Kimberly shot a look at Shattering, whose eyes met hers and betrayed everything.

``Oh, yes,'' she said to Fury, ``I mean, I only met him today.''

``You're a sailor.'' Fury asked.

``A naval officer, yes.''

Fury looked over Kimberly's head at Asa, then at Hobby, then back at Kimberly.

``We're making music tonight,'' Fury said. ``Will you join us.''

``I fiddle,'' Kimberly told her. ``A bit.''



The first time she'd seen an elephant walking down the street, in port somewhere in South Asia, Kimberly had thought how natural it had seemed. The devils in the hotel had struck her similarly. So the monstrous woodland creatures as they'd silently entered the barracks lodge, which itself seemed to be a kind of library.

``Don't be put off by their expressions,'' Fury told her, staring at the fireplace. ``You cannot know their happiness.''

Kimberly, between Fury and Hemlock, on her knees backward on the hide couch, holding a hot chocolate with rum in it, turned to look at the Fury's broad face in the firelight. It was a rather furry face, up close. Kimberly resumed watching the Animals set up their instruments. She'd been transfixed by the handsome head of the Hare, his black ears and limbs, and the impossibly soft-looking white soles of his feet.

``Now you've seen devils, so this must not be too strange for you,'' Hemlock said to her.

The blonde archer was writing up the events at the Chanticleer.

``I don't know,'' Kimberly said dreamily. ``It's pretty weird.''

Hobby was at a desk at the far corner of the hall, opposite the band, talking with Roos and Shattering, mostly with Roos. Kimberly had picked up Hobby's disdain for Shattering.

She turned round and joined Fury watching the fire, a gentle landscape of yellow flames in a large granite frame.

``You are Lieutenant Shattering's minder.'' Kimberly asked Fury.

``Yes,'' Fury said.

``Hobby doesn't seem to like him much.''

``That's just her face. It takes a long time to know her.''

``Like the Animals.''

``Hobby is more inscrutable,'' said Hemlock. ``Fury, does the bar at the Chanticleer have its own name.''

``I don't think so. Just put 'hotel bar'.''

Kimberly shuddered at the memory of the globule puling on the floor.

``Can you please explain what happened.'' she asked, either Hemlock or Fury, she wasn't sure. ``What they are--were.''

It was Fury who answered.

``There was a country that, under the weight of its own optimism, sank into the ocean.''

``Was lowered, deliberately,'' said Hemlock. ``Cranked down by hand.''

``Either way,'' continued Fury, ``its people became flat and red and spiky.''

``I've seen them.'' said Kimberly. ``In Vedauwoo.''

``Yes,'' said Fury, ``they can't disguise themselves there.''

``What does it mean.'' Kimberly asked.

Fury thought.

``Well,'' she said, ``they're devils. They do mischief.''

``They have a lot of money,'' said Hemlock. She looked up from her notebook and met Kimberly's eyes. ``It makes some people angry, like Hobby maybe, that you--that Newfoundland \& Labrador does business with them through Ekkor.''

``I don't think such a creature could exist in Newfoundland and Labrador.''

``Well, maybe there's a clue,'' said Hemlock.

``Iceland does the same thing,'' said Fury. ``And Germany, and China, and Arabia.''

``But you killed them,'' Kimberly said to Hemlock.

Hemlock shrugged. ``Those are our orders.''

Kimberly looked at Fury, who nodded.

``It's policy,'' said Fury.

Both archers sat up suddenly, and Kimberly heard Hobby hush Shattering mid-sentence.

A smile came to Fury's face.

``Toffy.'' she said.

``With Oca and Ape,'' affirmed Hemlock.



The fourth archer, the bee- and goose-winged fairies, more rum, a joint, and the first song of the evening all conspired to heft Kimberly's mind entirely out of its skull. Christoffel, as she was called, per Hemlock, was subdued that evening, having been ill, but she had begun her welcome home by excitedly recounting visions she'd had in some kind of curative cave where the fairies had nursed her back to her full strength. She had spoken with a dizzying energy. ``Ask her about Italy,'' Hemlock had said to Kimberly, and Fury had snorted laughter.

``Cheops let you hitch a wago.'' Fury had wondered, shaking her head. ``He must have pitied you. You must have been very ill, Toffy.''

The way the archers had laughed, and the way they'd held onto Christoffel, Hobby's palms on the littlest archer's cheeks in relieved affection, one could have mistaken them for ordinary women.

Roos and Shattering had replaced Kimberly and the archers on the couch, and they'd tended the fire and foregone smoking pot, but Kimberly had joined the band circle.

``I'm Ape,'' the bee fairy with the Asian face had said with a shy smile as she'd handed Kimberly a fiddle.

Oca, with her enormous afro and skin black as onyx, played an organ that Roos and Shattering had insisted on carrying in from the wagon as the orders-of-magnitude stronger archers had looked on.

The opening number, at Christoffel's request, had been a kind of rondeau, with each archer contributing a verse in response to the sung challenge ``Are you ardent.''

``Are you arden.'' Christoffel had sung in a lilting alto, ``in the Madness of war, guarding his life with your Death, His Song on your breath, your Love for Him filling your heart? Are you still wild? Can you take command? Will you join the attack, firing true from horseback? Let us ride all you Red Hats and fill afternoon with our arrows, high and aloft, fighting forever for Ekkor our God! Are you ardent.'' She'd looked at Hemlock and sung: ``Let us hear a tale of Song from Hemlock now.''

``Centuries ago,'' Hemlock had responded in a voice like a bell, ``on the shores of the world, travellers tossed by a fault, 'neath an ocean of salt, washed up without bearings nor hope,'' she'd sung. ``And the Holy Forest throng, the uncanny birdsong, called to them more than the reach. They abandoned the beach, wandered into the trees, where they joined in the chorus forever, drifting in time. Castaways wed to the Wood, speech and destinies all but forsaken for music and rhyme, artistic extremes and dreams leporine. Are you ardent.'' She'd turned to Fury. ``Let us hear a tale of Death from Fury now.''

``I recall my first,'' Fury had sung, in a voice lower and breathier than Hemlock's, and achingly beautiful, ``far from my worst, a man from the bigoted hordes, a Captain of sorts, at the Battle of Dáktylir. Fire had snapped my bow, so I rode him down, drove him into a red oak, as he slashed at my throat, I crushed him into the trunk with Ontario's shoulder, 'till his breastbone exploded, and a hundred branch-fuls of snow shook down like confectioners' sugar, his blood on my face, his dying eyes marking who'd furnished his fate. Are you ardent.'' Fury had passed the torch back to Christoffel. ``Let us hear a tale of Madness from Christoffel now.''

The brown-haired, copper-eyed, sweet-seeming archer, who was only a bit taller than Kimberly herself, had responded in Italian. ``Ah, quei giorni utopici giù in Toscana! La poesia! La musica senza finale galleggiando sul maestrale, e tanti amici demenziale! Feci caprioli su Cheope in la piazza. Tutt'applaudirono, e por un solo momento, io sapevo cosa significa essere veramente singolare, la bella del ballo, La Eterodossa! 'Na sopra, non 'na tra, bilione cast'e doverosa ragazze scout in le gonne marrone. Sei appassionata.'' Hemlock had grinned at Kimberly, who'd had just barely enough time and Italian to work out that Christoffel had been recounting a mad visit to Tuscany. Christoffel had then sung: ``Let us hear a tale of Love from Hobby now.''

More grins, and Kimberly surmised that assigning the topic to Hobby was mockery.

But music and rum had loosened the squad leader.

``Oh, you think me proud,'' Hobby had sung in a powerful voice, deeper than all the others', ``but I know a tale round which these others will pale, all that Song on your breath, all your Madness and Death. Very well, I will tell of a love so pure, yet so insecure, nothing could come of it but rivers of blood. A testament cut in the breast of the Mountain forever. A carving away. A breathlessly penitent hush in the Song of the Forest forever. A pining away. A beautiful \& terrible rush to the depths of Creation forever. A falling away. A hopelessness manifest justin the drape of an arm round a shoulder, and a heart that would break but that it meant never seeing her face again.'' To her stunned and delighted companions Hobby had concluded the song: ``Are you ardent.''

Love, Madness, Death, and Song, they'd covered. It seemed to be an archer thing, and Kimberly was relieved not to have been challenged with a topic, though she'd caught on to the melody and accompanied on fiddle with some ease.

``You play well,'' Fury had said, and the room had brightened, and Kimberly's flesh had tingled at the compliment. Christoffel and Ape had nodded agreement. Kimberly had shaken her head. The archers were virtuosos. The Animals were the best musicians she'd had ever heard. And the Animals' voices! When the next song had begun, and the Otter had begun to sing longingly about a love he'd left behind in ``Otter-town,'' Kimberly, overwhelmed and overjoyed, had put her fiddle on her lap and wept. Ape had put her hand on Kimberly's shoulder, something the archers couldn't do but looked as if they wished they could. Hemlock had passed her a joint.

Kimberly had overheard Christoffel whispering to Fury as the song had continued: ``I forget sometimes, it can be a lot for them to take in.''



``How are the Settlers not in awe of them.'' Kimberly asked Ape as together they peed in the woods.

``The Settlers are,'' Ape had said, standing and straightening her simple brown skirt, ``for the most part, bigots and litterbugs.''

Ape's voice was gentle and soft, and her transparent coppery bee wings, though enormous as Oca's brown goose wings, floated light on the air.

She was barefoot.

``Aren't your feet cold.'' Kimberly asked.

``No. It's too hot in there,'' Ape said, nodding at the lodge. ``The workshop is always hot, from the forge.''

Kimberly stared at Ape's Asian features.

``Where are you from, Ape.'' Kimberly asked.

Ape looked at her with a sad smile, then shrugged.

``I don't know,'' she said.



``I was sure,'' Christoffel was saying when Kimberly and Ape came back in to the lodge, ``that we each had a role to play.''

The Badger, Hedgehog, Hobby, and the Hare were improvising on their instruments on the other side of the room. Meanwhile, Christoffel held court by the fire, sitting on the sofa between Oca and Fury. Hemlock sat cross-legged on the intricate red and brown rug, the Fox's head in her lap. The Otter, tall as an archer, stood behind them by the spiral staircase, polite and serene, his webbed paws clasped before his long, soft belly. Roos and Shattering, both with tea, both of whom seemed to prefer to keep their distance from the Animals, sat opposite Hemlock in chairs borrowed from the kitchen.

Ape proceeded directly to squeeze in between Fury and Christoffel, leaving Kimberly to stand awkwardly behind her two seated shipmates.

``All the places I saw,'' Christoffel continued with wonderment, ``the Hollow Planet, the Seahorse Valley, the Five Islands. I knew that it was for me to see them, for Hemlock to find the way to them, for Fury to understand them.'' She paused and twisted round to look over the back of the sofa at Hobby intoning on her copper horn a delicate avant-garde solo over the Badger's wistful brushings. ``But only for Hobby to visit them all.''

``Ha.'' exclaimed Hemlock, stirring the Fox. She clutched the fur of his neck to settle him. ``Homebody Hobby. What could make her go to the edge of everything.''

``Orders,'' Fury said flatly.

``Yeah,'' said a chastened Hemlock. ``Besides that, I mean.''

Hemlock appeared to look around for something to throw at Fury. Kimberly smiled at the two friends' love for each other, a bond she'd picked up on right away.

Fury looked at Kimberly and said: ``Toffy has been describing a vision she had in a cave near Oca and Ape's workshop. It's a sort of healing place.''

``A hot spring,'' Ape added.

``I'm glad you are feeling better,'' Kimberly said to Christoffel.

``I didn't know you could get sick,'' said Roos, whose tea had followed many whiskeys.

``She wasn't sick,'' Oca said coldly.

``I had a fever,'' Christoffel said, placing her pale hand on Oca's black arm. Oca's goose wings draped over the back of the sofa, the soft leading edge of the right one resting on Christoffel's neck.

``It's not sick like you get sick,'' Fury said to Roos. ``It's a kind of--Thomas.'' She looked at Shattering, seeking a translator.

``A fever dream,'' Thomas said, looking at Kimberly. She grimaced and leaned toward him, trying to hold his gaze for more than the one second at a time he'd up to now granted. They hadn't expected to see him--well, maybe Asa had; Kimberly wondered if coming here from Vedauwoo had really been her own idea--in any case, there hadn't been a chance for a proper debrief. As they'd walked to Three Nations from the bridge, in pauses in her excited discussion with Hemlock, she'd heard smatterings of the conversation behind her. It had been informal. The two men had fallen behind at one point, and surely Thomas had passed any word of caution at that point, but Asa had not hinted at anything urgent.

Looking into Thomas' dark Inuk eyes, Kimberly could see that something had happened to him here. He'd fallen in love with one of the archers, Fury. That seemed to be an open secret. But there was something else. Kimberly was curious, but didn't necessarily relish speaking with Thomas alone. He was a bit depressing.

She became aware of Hemlock looking at her, and as if reading Kimberly's thoughts, the cheerful blonde archer said: ``This is reserved, professional Thomas.''

Thomas looked at Hemlock, then down at his shoes.

``We haven't seen him in a while,'' Hemlock continued. There were chuckles from the others, and a wan, pitying smile from Fury that mercifully went unobserved by Thomas.

Asa gripped Thomas' shoulder affectionately, a rare gesture from the Scandinavian. Kimberly assessed it was a function mostly of his inebriation, with another smaller term that credited Thomas' evident assimilation into the archers' world, which was, after all, his fucking mission.

``Have you seen his drawings.'' Christoffel asked Kimberly.

Kimberly shook her head.

``They're good,'' said Christoffel.

Hemlock, Fury, Oca, and Ape all nodded in unison.

``Maybe he could draw your vision,'' Kimberly suggested to Christoffel.

Asa shot her a look and hid it quickly with a sip of his tea.

``That's a good idea.'' said Hemlock, grinning.

Thomas looked up.

``What.'' he said. ``Now.''

``No,'' said Hemlock. ``Not now.''

``I'd like that.'' said Christoffel. ``We can go for a ride tomorrow, I'll tell you everything, Thomas. There are more details.''

Kimberly caught Fury's and Hemlock's smile at this. Evidently, Christoffel's powerful imagination, comely face, bright and cheerful disposition, musical talent, prodigious war-fighting capability, her viciousness in combat, and her remarkable horsemanship all conspired to keep the talkative archer just this side of being somewhat tiresome in conversation.

In the firelight, goose-winged Oca and bee-winged Ape hugged Christoffel from either side, a splendid thing to behold.

CHAPTER: Thomas is Debriefed by Asa \& Kimberly

A Stables, Early Morning



``Can you take notes.'' Asa said to Jack, who nodded.

Thomas sat on the edge of his cot in the stables watching his friend arrange two chairs and a candle-bearing stool on the bare wooden floor, so that the tack room might serve as an interrogation room. The archers' four saddles hung on the walls round them, polished black hide contours mutely described in the pre-dawn gloom. Just beyond the sphere of candlelight, they hovered like the scooped out and scarred over faces of ancient judges, committed by mutilation to implacability.

``We have to do this,'' Asa said to Thomas. ``Are you high.''

``No,'' Thomas said. ``Not really.''

Asa and Jack took their seats. Jack opened a notebook and began her dutiful transcription.

``Put the names and date, all that stuff later,'' Asa said to Jack. ``The location.'' He looked round the tack room and chuckled.

Thomas drew his legs up under himself to sit cross-legged upon the cot.

``You could just read my reports,'' Thomas said to Asa.

Asa shrugged and said: ``Let's do this anyway.''



``She showed up about an hour after you left me in the meadow. I think she'd been watching me for a while.''

``Did she bring you directly here.'' Asa asked.

``We camped one night. Well, half the night. We rested a couple hours.''

``How long was the journey.''

``Maybe eight, nine hours total.''

Jack scribbled.

``What do you remember about the route.'' Asa asked.

``There was a footbridge over a waterfall. She identified it as the boundary of the Forest proper.''

Thomas was grateful to Asa for their conversation on the trek to Three Nations, for the ridicule and reproach. It inured Thomas to the exposure he felt now recounting that evening. Lieutenant Jack was sharp, but Thomas trusted Asa would not allow into the record anything not strictly necessary to the mission.

``What was your impression of her, of Fury.'' Asa asked, not looking at Thomas.

``Well she's impressive. They all are. I'd learned enough from Ted Bradfield, just enough, to know that walking over the bridge was something significant. Unprecedented, even. Nevertheless I crossed an ordinary footbridge, under ordinary moonlight, if in extraordinary company. Before long we were on proper trails, and there was nothing unusual about them. We passed houses, like the ones you've seen, some with lights in the windows. At some point I noticed the constellations were unfamiliar.''

Thomas watched Kimberly scribble as he talked.

``I heard the music from the lodge before I saw the monstrous animals singing and playing their instruments. When I entered, when I saw them, I collapsed. When I woke, the archers were tending to me. I stayed in here that first night.'' He looked at Asa, who still did not meet his gaze. ``I was drunk. Stoned.''

``When did you show them the bodkins.'' Asa asked.

When Thomas didn't immediately answer, his friend finally looked at him.

``I showed them to Fury by the footbridge,'' Thomas said. ``Right after we crossed.''

``What did she think of them.''

``She was impressed.''

Asa looked at Kimberly.

``Have any of them touched you.'' she asked.

Thomas stared at her. She was young, and junior. But she'd been read in, probably more than he. He looked back at Asa.

``Is she a tourist.'' Thomas said, pointing at Jack.

``Subject matter expert,'' Asa said.

``Well then she knows they haven't touched me, because I'm breathing, right.''

``I'm just doing my job, Shipmate,'' Kimberly said as she transcribed his response.

``You're a valuable specimen, Tom,'' Asa said, smiling.

Thomas looked into Asa's steel blue eyes and felt the years of their friendship transact across their mutual regard. It occurred to him that intimacy had never really been achieved. Finally, he shook his head.

``Just read my reports, Asa,'' he said. ``If I had anything to tell you, I'd tell you.''

CHAPTER: Fury's Dream

Barracks Lodge, Early Morning



``Consider,'' Toffy said, ``a cylindrical eel.''

She dangled the limp, shiny, black creature before her and touched the point of her dagger to its neck.

``This--Fury, look.''

Fury had been momentarily distracted by Toffy's copper eyes, which looked more sober and focused than she'd ever seen them. Hemlock's face and hair was most like their Mother's, but only Toffy had Diana's copper eyes.

``Yes, sorry, go ahead,'' said Fury, looking back to the eel and the spherical reflection in his dead eye of herself and her sister leaning in intently.

``You make a slit here along the spine,'' Toffy said, doing so. ``That's zero. Then a quarter.'' She turned the eel ninety degrees and made another slit. ``Then half.'' She turned the eel another ninety degree and slit below its chin. Clear fluid issued from the incision. ``Then three quarters.'' She made a fourth slit. She held the eel higher. ``Then you do the same thing a quarter down his length, round where the dorsal ribbon starts.'' She did, dextrously turning and slitting. ``Then half, then three quarters. Then, you join zero at the top to a quarter at the quarter, do you know what I mean.'' She dragged the dagger's tip in a curve from the zero slit near the head to the quarter-turn slit below, the smooth skin easily parted by the polished copper blade. She repeated the motion from each of the top slits, twisting the eel as she carved. She continued the procedure down the eel's length, her cuts sure and smooth.

Toffy laid the helically flayed eel on the dining table. ``There,'' she said. ``That's how She likes them.''

``It's not the best way,'' said Fury. ``How do you get his guts out.''

``They just dissolve in the smoker,'' said Toffy. She licked eel juice from her fingers and smiled affectionately at Fury.

Fury looked into her sister's eyes again.

``Why don't you talk like this anymore.'' Fury said.

Toffy's brow furrowed.

``What do you mean.''

``You're sort of...distracted. For years, Christoffel.''

``Am I.''

``Did you go mad.''

Toffy laughed. She mimed a loony expression, then her calm, sober smile returned. Fury longed to embrace her.

``Toffy, I love you so much,'' Fury said, tears coming to her eyes.

``I love you, too, Fury,'' Toffy said gently, taking Fury's hand.

A breeze blew through the screened-in porch, flickering the candles on the dining table.

``You set the table,'' said Toffy, ``I'll put this guy in the smoker.''



They walked through the park to meet their Mother's train. Swans and geese floated on the lake. Passersby smiled shyly at them, admiring their shiny uniforms and the tall ears of their headdresses. A sports team from the high school approached them at a jog, and one of their security detail in his black suit and black sunglasses trotted up to meet them with outstretched arms, channeling them cattle-like off the path. A handsome blonde boy smiled at Fury as he jogged by. ``Sorry,'' she mouthed. He doffed an imaginary cap to her.

``Mom would like Thomas,'' Toffy said.

``Do you think.''

Fury didn't credit that. Their Mother had little use for men in general, certainly not one who showed an interest in one of her daughters.

``I think she'd like the Hare, too,'' said Toffy. ``But Thomas might fit better.''

``I can't get used to you as the voice of reason, Toffy.''

Across the lake, a train left the raised station, heading West for the city. The breeze carried bagpipes from the police station.

``I wish it could always be Autumn,'' said Toffy, closing her eyes.

Of course Thomas would fit. He wasn't royalty, but he was a naval officer, and from a line of naval officers. He would know how to behave.

Was she honestly going to bring the Hare home to dinner?

``He plays his guitar well enough,'' Fury said in a pouty voice. ``He can probably eat with a fork.''

Toffy took her hand. She was so much shorter than Fury, so looking up to her new commanding personality was especially awkward, like Fury would spend her life ducking, trying to meet Toffy's low, copper gaze.

``He's on that island.''

Fury snapped her head round to look at the small island in the middle of the lake. She knew it as a swan graveyard. She heard his guitar. She looked back at Toffy, who smiled indulgently and nodded, letting go her hand. ``I'll meet Mom.''

Fury bolted to the edge of the lake and launched herself in a soaring dive. She kicked her legs powerfully and surfaced a few meters from the shore. Already she heard the detail on their radios. ``Clipper Two on the run.''

Why was she ``tw.''? Hobby was older.

That's right, Toffy was younger. Hemlock the youngest. It was just that Toffy seemed older with her new personality. That's right. ``I'm Clipper Two,'' Fury thought.

The water was ice cold. She swam as fast as she could. Over her shoulder she saw one of the detail jump in the lake. Toffy waved as she continued walking through the park to the train station. Some passersby had stopped to watch the commotion.

When she reached the island, Fury clambered out among the swan skeletons. The Hare was there, strumming his guitar, and her eyes rested on his face and felt, finally, at home. As usual, she couldn't tell if he was looking at her.

``Why can't you just talk to me.'' she implored.

She heard the chop of helicopter blades, then felt them as the machine sped over the lake and pulled up into a hover above the island. In the lower atmosphere, she saw two satellites arc silently with uncanny speed and steadiness to take positions above the park, forming a triangle with the helicopter. They glinted in the sun. The radio chatter continued. ``Space command has Clipper Two at...'' then a long string of coordinates.

There were so many tuples! Across how many dimensions were she and her sisters tracked?

The Hare stopped playing and swung his guitar onto his back.

``Please,'' Fury begged. ``Please don't leave me.''

There was a spyglass on a tripod facing the train station. ``Thomas','' she thought.

``Please.'' she screamed at the Hare, who showed no reaction, but didn't leave yet. Could he swim with his guitar?

She composed herself, then shivered in the helicopter's downwash. Lake water filled her boots and streamed from her headdress down her face. She walked to the telescope, crunching swan ribs, and looked through. It was aimed at the train station. She saw her Mother in her business suit disembark, her detail behind her. Toffy took her briefcase.

``Where's your sister.'' Artemis asked.

Fury looked at the Hare in shock.

``I can hear them through this.'' she shouted over the thunderously loud helicopter.

The Hare stared blankly, not necessarily at Fury. His ears flew wildly in the wind. 

``I mean that's pretty cool,'' she shouted awkwardly. She looked back into the eyepiece.

``She wanted to help with dinner,'' Toffy told their Mother.

Artemis looked directly at Fury, who recoiled from the eyepiece.

``What's going on over there.'' Artemis asked.

``Mom, it's okay,'' Toffy said.

``Hemlock has tantrums, not Fury,'' said Artemis, lighting a cigarette. ``What, are we walking.''

``It'll be nice,'' said Toffy.

``She knows my name,'' Fury whispered, tears stinging her eyes.



``I think,'' Artemis said, a forkful of eel perched near her mouth, ``you've switched.'' She turned the fork toward them and wagged it back and forth.

Their Mother sat at the head of the table. Toffy sat directly to her right, Fury beside Toffy. Across the table settings had been laid for the two absent sisters. A fan turned slowly on the ceiling of the screened-in porch. Artemis liked to eat out here in Spring and Autumn. The sky was purple. Fireflies danced on the lawn.

``That makes sense,'' Fury thought. ``Toffy is me, now, and I'm Toffy. So why do I still love him.''

``It doesn't work like that, Mom,'' Toffy said. ``I could rotate into Fury, but she would rotate into Hobby. We can't just switch.''

That didn't sound right.

``There would need to be more...'' Fury mumbled.

``Don't mumble, Fury,'' Artemis said.

``I was saying there would need to be more than four of us,'' Fury said to her Mother. ``For symmetry.''

Artemis smiled. ``Or fewer,'' she said.

Fury would have thought of that if it weren't unthinkable. A God could think the unthinkable.

CHAPTER: Fury Wakes from a Dream

Barracks Lodge, Early Morning



The pulse of the organ.

The throb of the double bass.

Even in the pre-dawn gloom, Hemlock's broad face was sunny. The fire was embers, but it was enough to glint in her green eyes and in the loving smile that was the only thing Fury would enshrine were the Forest and its epoch hers to chronicle. Hemlock's palm was on her cheek, warm and rough and nourishing. They were on the couch, Fury's head in her friend's lap.

``Was I dreaming.''

Hemlock's smile darkened. She nodded.

``Did I say anything.''

Fury realised she was drenched in sweat. She tugged at the sleeve on her upper arm, feeling it peel from her skin. ``Oh gross,'' she said.

She sat up and turned, frowning to see the dark patch on Hemlock's skirt. She looked at Hemlock and laughed.

``I'm sorry,'' Fury said. ``That's gross.''

She flopped to sit beside to her friend.

Before them, Toffy was passed out on the rug, her arms round the Fox, whose hind legs splayed heavenward in a uniquely canine sleep pose.

``That's gross,'' said Hemlock, nodding towards him.

``Oh my God,'' said Fury, pushing her thumb and forefinger up under her glasses to rub her eyes. ``Have you just been staring.''

``I can't look away,'' said Hemlock, widening her eyes comically.

Fury snorted. ``Give me that,'' she said, pointing at the small grey blanket, embroidered by Ape with borders of black acorns, folded on the arm of the couch under Hemlock's elbow.

Fury leaned forward and draped it, nappy-like, over the Fox.

Toffy stirred, clutching the beast tighter and uttering a sleepy, unintelligible articulation.

Fury and Hemlock giggled.

``Hobby up.'' Fury asked.

``No. Look.'' Hemlock indicated behind them.

Fury twisted round to see Hobby across the hall, asleep on the floor, her head on the reclining Otter's shoulder. The Hedgehog was bowing a soft melody over Oca's all but stopped lower register. Oca seemed in a trance. Back to back, Ape and the Badger shared a drink and the stool behind the drum kit.

Ape smiled dreamily at Fury and made a little wave. Fury smiled at the bee fairy.

``I wouldn't have credited such a sight a couple years ago,'' Fury mused, looking back at Hobby, whose horn rested in her lap, her big hands folded over it. The Otter's eyes were bright and alert, but he was keeping still apparently to accommodate the sleeping archer.

``You heard what she sang,'' said Hemlock, her voice uncharacteristically low and candid. ``A breathlessly penitent hush in the Song of the Forest forever.''

Fury crossed her arms under her chin and settled on her knees to stare at Hobby over the back of the couch.

``I know,'' she said. Then she shot Hemlock a perplexed look. ``I know, right.''

Hemlock's face hid many complications. Fury caught the tremble in the green pupils, betraying ratcheting behind them.

``She's been blowing that horn a long time,'' said Hemlock, looking back at the dying embers. ``It means more to her than she lets on.''

Hemlock became philosophical only when sad, and Fury knew herself to be, at the moment, the source of that sadness. She spun back round and took Hemlock's hand.

``I'm fine, you know,'' Fury said, and Hemlock nodded. ``What did I say in my sleep.''

``'Please don't leave..''

Fury chuckled. ``Who was I talking to.''

Hemlock looked at her sharply, as reproachful as she ever had, and Fury felt her stomach drop. Hemlock knew. Of course she knew. Shame rushed to accompany horror as Fury understood at once the inevitability of Hemlock's understanding, and the betrayal of not having confided in her. She gripped Hemlock's hand tightly, almost violently.

``Not now,'' Fury said. ``Please.''

A tear ran down Hemlock's cheek. ``It doesn't matter when, Fury,'' she said. ``It can be never. I stand with you.''

The door was open to the night.

They heard the Newfy woman walking across the slushy forecourt from the stables. Kimberly peeped round the doorjamb and Fury beckoned her inside. Kimberly knocked her heels together to clear her boots and tiptoed over to sit in the armchair. She looked over at the tableaux round the organ, whence the pulsing drone of the duet.

``That's beautiful,'' the visitor said.

Fury nodded. Kimberly looked as if she hadn't slept. Fury considered her. She was very pale and blonde, this Newfy.

``You're not an Eskimo,'' Fury observed. She still held Hemlock's hand. Hemlock still stared into the embers.

Kimberly shook her head. ``No. I'm what they call 'Qallunaat'. 'Off the boat'.''

``You seem more at home here than Thomas,'' Fury said. ``And he's been here a year. I'm not criticising him. We're all fond of him.''

``I grew up in Labrador,'' Kimberly said. ``Thomas is from St John's.''

``Well, he knows how to fish and hunt and ride now.''

``That's good for him.''

``He's not great,'' said Fury. Hemlock snorted. The three chuckled together.

Fury watched as Kimberly's eyes scanned Toffy and the Fox.

``We're not what you expected,'' Fury said.

The Newfy shrugged. ``I confess I considered you en masse. I thought of you as legion, not individuals I would ever meet. I mean we don't have much to go on. No photographs. No drawings even. No interviews. I'm sorry, am I being insensitive.''

Fury shook her head. ``No,'' she said. ``We know how it seems. Our traditions. Our rules.''

``But Thomas draws the four of you.''

Fury shrugged. She jabbed a thumb over her shoulder towards Hobby. ``Her call,'' she said.

Kimberly looked over at Hobby and covered an amused smile, her brows arching with tenderness. It was a lovely sight, Hobby sleeping on the Otter's shoulder.

``She doesn't seem to like him much,'' Kimberly said. ``Thomas I mean.''

``You can't really know what Hobby is thinking,'' Fury said. ``But yeah, she finds him pretty useless.''

Kimberly looked at Toffy and the Fox again.

``You guys are off the beaten track,'' she said.

Fury and Hemlock laughed. ``Oh yes,'' said Fury.

``My father is the Commander of our navy,'' said Kimberly.

``Yes,'' Fury said. ``Thomas said.''

``Do you have any sisters.'' asked Hemlock.

Fury watched Kimberly's eyes closely to see how she'd react to the rebuff. What she saw was genuine humility.

``We had a dog,'' Kimberly said.

Hemlock laughed.

They listened to the music, and after a few minutes Kimberly asked: ``Where's the Rabbit.''

Fury felt her heart skip a beat and Hemlock's hand clench her own.

``He's probably in the woods,'' said Hemlock. ``Writing a song.''

Fury felt Kimberly's eyes on her and didn't dare meet them with her own. She suddenly felt irritated. She stood up, yanking her hand out of Hemlock's too abruptly, realising the tantrum gave her away more than anything in her eyes might have.

Fury marched past Kimberly, out the door, and into the forecourt, her fire-dry boot-fur eagerly wicking up the slushy melt.

Yeah: where was he?

She quickly found his unmistakable tracks, imbalanced by the guitar strapped to his back. The Moon was full and high, its resident Hare strumming away on his own guitar. She followed the tracks into the woods south of the river.

Before long she heard his soft strumming.

She followed the music.

She saw him in a clearing.

He was singing to the Moon.



\end{document}